### 2012-10-28 icse2013demo-testevol/paper.tex
Initial commit

\documentclass[conference]{IEEEtran}
\synctex=1

\usepackage[linesnumbered,boxed,ruled,nofillcomment]{algorithm2e} % add vlined,
\usepackage{amsmath}
%\usepackage{amsthm}
\usepackage[usenames]{color}
\usepackage[light,first]{draftcopy}
% \usepackage{draftwatermark}
% \usepackage[firstpage]{draftwatermark}
\usepackage{epsfig}
%\usepackage{fullpage}
%\usepackage[pdftex]{graphicx}
\usepackage{graphicx}
%\usepackage{latex8}
\usepackage{listings}
\lstloadlanguages{Java}
\usepackage{multirow}
%\usepackage{palatino}
\usepackage{alltt}
\usepackage{times}
% \usepackage{url}
\usepackage{hyperref}
\usepackage{cite}
\usepackage{xspace}
\usepackage[linesnumbered,boxed,ruled,nofillcomment]{algorithm2e} % add vlined,
% \usepackage[small,compact]{titlesec}

\newcommand{\subparagraph}{}
%\usepackage[compact]{titlesec}
%\titlespacing{\section}{0pt}{1ex}{1ex}
%\titlespacing{\subsection}{0pt}{1ex}{0ex}
%\titlespacing{\subsubsection}{0pt}{0.5ex}{0ex}

% Use the following to make modification
% \SetWatermarkAngle{45}
% \SetWatermarkLightness{0.8}
% \SetWatermarkFontSize{5cm}
% \SetWatermarkScale{1}
% \SetWatermarkText{DRAFT -- Do not redistribute}

%\renewcommand{\topfraction}{0.85}
%\renewcommand{\textfraction}{0.1}
%\renewcommand{\floatpagefraction}{0.75}
%\addtolength{\textfloatsep}{-0.3in}

\input{mymacros}
\newcommand{\tool}{\textsc{TestEvol}\xspace}

%\linespread{0.97}
%\columnsep 0.11in
\clubpenalty = 10000
\widowpenalty = 10000
\displaywidowpenalty = 10000

\let\oldthebibliography=\thebibliography
\let\endoldthebibliography=\endthebibliography
\renewenvironment{thebibliography}[1]{%
  \begin{oldthebibliography}{#1}%
    \setlength{\parskip}{0ex}%
    \setlength{\itemsep}{0ex}%
  }%
  {%
  \end{oldthebibliography}%
}

%\toappear{}

\begin{document}

\title{TestEvol: A Tool for Analyzing\\Test-Suite Evolution}

\author{\IEEEauthorblockN{XXX}
\IEEEauthorblockA{
College of Computing\\
Georgia Institute of Technology\\
Atlanta, USA\\
\{orso\}@cc.gatech.edu}
}

\maketitle

\pagestyle{empty}

\begin{abstract}
  Test suites, once created, rarely remain static. Just like the
  application they are testing, they evolve throughout their lifetime.
  Test obsolescence is probably the most known reason for test-suite
  evolution---test cases cease to work because of changes in the code
  and must be suitably repaired. Repairing existing test cases
  manually, however, can be extremely time consuming, especially for
  large test suites, which has motivated the recent development of
  automated test-repair techniques. We believe that, for developing
  effective repair techniques that are applicable in real-world
  scenarios, a fundamental prerequisite is a thorough understanding of
  how test cases evolve in practice. Without such knowledge, we risk
  to develop techniques that may work well for only a small number of
  tests or, worse, that may not work at all in most realistic cases.
  Unfortunately, to date there are no studies in the literature that
  investigate how test suites evolve. To tackle this problem, in this
  paper we present a technique for studying test-suite evolution, a
  tool that implements the technique, and an extensive empirical study
  in which we used our technique to study many versions of six
  real-world programs and their unit test suites. This is the first
  study of this kind, and our results reveal several interesting
  aspects of test-suite evolution. In particular, our findings show
  that test repair is just one possible reason for test-suite
  evolution, whereas most changes involve refactorings, deletions, and
  additions of test cases.  Our results also show that test
  modifications tend to involve complex, and hard-to-automate, changes
  to test cases, and that existing test-repair techniques that focus
  exclusively on assertions may have limited practical applicability.
  More generally, our findings provide initial insight on how test
  cases are added, removed, and modified in practice, and can guide
  future research efforts in the area of test-suite evolution.
\end{abstract}

% A category with the (minimum) three required fields
%\category{H.4}{Information Systems Applications}{Miscellaneous}
%A category including the fourth, optional field follows...
%\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]

%\terms{Theory}

%\keywords{ACM proceedings, \LaTeX, text tagging}

\section{Introduction}

\vspace{4pt}
The rest of the paper is organized as follows.

\section{Conclusion and future work}
\label{sec:concl-future-work}

\section*{Acknowledgments}

This work was supported in part by NSF awards CCF-0916605 and
CCF-0964647 to Georgia Tech, and by funding from IBM Research and
Microsoft Research.

\bibliographystyle{abbrv}
\bibliography{paper}

\end{document}

### 2012-10-29 tool/src/main/java/org/testevol/controller/IndexController.java
summary report, new left menu and added config files

@@ -3,16 +3,13 @@ package org.testevol.controller;
 import org.springframework.stereotype.Controller;
 import org.springframework.web.bind.annotation.RequestMapping;
 import org.springframework.web.bind.annotation.RequestMethod;
-import org.springframework.web.servlet.ModelAndView;
 
 @Controller
 @RequestMapping("/index")
 public class IndexController {
 
 	@RequestMapping(method = RequestMethod.GET)
-	public ModelAndView init() {
-		ModelAndView mav = new ModelAndView();
-		mav.setViewName("index");
-		return mav;
+	public String  init() {
+		return "redirect:/projects/list";
 	}
 }

### 2012-10-29 tool/src/main/java/org/testevol/controller/ProjectController.java

@@ -1,5 +1,6 @@
 package org.testevol.controller;
 
+import java.io.File;
 import java.io.PrintWriter;
 import java.io.StringWriter;
 import java.util.ArrayList;
@@ -8,6 +9,7 @@ import java.util.HashMap;
 import java.util.List;
 import java.util.Map;
 
+import org.apache.commons.io.FileUtils;
 import org.springframework.beans.factory.annotation.Autowired;
 import org.springframework.beans.factory.annotation.Value;
 import org.springframework.stereotype.Controller;
@@ -51,6 +53,11 @@ public class ProjectController {
 		mav.addObject("projects", projects);
 		mav.setViewName("projectList");
 		return mav;
+	}
+
+	@RequestMapping(value="names",method = RequestMethod.GET, produces="application/json")
+	public @ResponseBody List<String> getProjectNames() throws Exception {
+		return projectRepo.getProjectsNames();
 	}
 
 	
@@ -203,10 +210,14 @@ public class ProjectController {
 		return executionMap;
 	}
 	
-	@RequestMapping(value="version/script",method = RequestMethod.GET)
-	public @ResponseBody String getSummReportScript() throws Exception {
-		return "alert('loaded dude');";
-
+	@RequestMapping(value = "{project}/execution/{id}/report/script/{name}", method = RequestMethod.GET, produces="application/javascript")
+	public @ResponseBody
+	String getReportScript(@PathVariable("project") String projectName,
+			@PathVariable("id") String id,
+			@PathVariable("name") String scriptName) throws Exception {
+		
+		Execution execution = projectRepo.getExecution(projectName, id);
+		return FileUtils.readFileToString(new File(execution.getExecutionDir(),scriptName+".js"));
 	}
 
 	@RequestMapping(method = RequestMethod.POST)
@@ -218,7 +229,7 @@ public class ProjectController {
 	@RequestMapping(value = "getBranches", method = RequestMethod.GET, produces = "application/json")
 	public @ResponseBody
 	Map getBranches(@RequestParam("vcs") String versionControlSystem,
-			@RequestParam("url") String url) {
+					@RequestParam("url") String url) {
 
 		VersionControlSystem versionControlSystemInstance = VersionControlSystem
 				.getInstance(versionControlSystem, url);

### 2012-10-29 tool/src/main/java/org/testevol/domain/ProjectRepository.java

@@ -13,6 +13,7 @@ public interface ProjectRepository {
 	public boolean exists(String projectName);
 	public Project getProject(String projectName) throws Exception;
 	public List<Project> getProjects();
+	public List<String> getProjectsNames();
 	public void deleteProject(String projectName) throws IOException;
 	public void deleteVersion(String projectName, String version) throws Exception;
 	public UpdateResult updateRepo(String projectName, String version) throws Exception;

### 2012-10-29 tool/src/main/java/org/testevol/infra/ProjectRepoFileSystem.java

@@ -4,6 +4,7 @@ import java.io.File;
 import java.io.FileInputStream;
 import java.io.IOException;
 import java.util.ArrayList;
+import java.util.Arrays;
 import java.util.Calendar;
 import java.util.Collections;
 import java.util.Comparator;
@@ -228,6 +229,12 @@ public class ProjectRepoFileSystem implements ProjectRepository {
 		File executionDir = new File(executionsDir,id);
 		
 		FileUtils.deleteDirectory(executionDir);		
+	}
+
+	@Override
+	public List<String> getProjectsNames() {
+		return Arrays.asList(projectsDir.list());
+	
 	}
 	
 	

### 2012-10-29 tool/src/main/webapp/js/testevol.js

@@ -1,0 +1,272 @@
+var NUMBER_OF_CATEGORIES = 8;
+var versionsSummary = {};
+
+function getCategoryLabel(index) {
+	switch(index) {
+		case 0:
+			return 'TESTREP';
+		case 1:
+			return 'TESTMODNOTREP';
+		case 2:
+			return 'TESTDEL (AE|RE)';
+		case 3:
+			return 'TESTDEL (CE)';
+		case 4:
+			return 'TESTDEL (P)';
+		case 5:
+			return 'TESTADD (AE|RE)';
+		case 6:
+			return 'TESTADD (CE)';
+		case 7:
+			return 'TESTADD (P)';
+	}
+}
+
+function isRepairCategory(category) {
+	return category == 'TESTREP' || category == 'TESTMODNOTREP';
+}
+
+function isCoverageAwareCategory(category) {
+	return category == 'TESTDEL (P)' || category == 'TESTADD (P)';
+
+}
+
+function createSummaryTable(summaryTable, versions, summary_data) {
+	//add header
+	var firstLine = document.createElement("tr");
+
+	var line = document.createElement("tr");
+	var leftMostColumn = document.createElement("td");
+	leftMostColumn.innerHTML = "All Versions";
+	leftMostColumn.className = "allValues";
+	line.appendChild(leftMostColumn);
+	appendValuesToLine(line, 0, summary_data, "total", "numbers allValues");
+	summaryTable.append(line);
+
+	var tbody = document.createElement("tbody");
+	var previousVersion = versions[0];
+	for(var i = 1; i < versions.length; i++) {
+		var version = versions[i];
+		line = document.createElement("tr");
+		var versionsColumn = document.createElement("td");
+		var link = document.createElement("a");
+		link.href = version + "/report.html";
+		link.innerText = previousVersion + ' - ' + version;
+		versionsColumn.appendChild(link);
+		line.appendChild(versionsColumn);
+		appendValuesToLine(line, i, summary_data, version, "numbers");
+		tbody.appendChild(line);
+		previousVersion = version;
+	}
+	summaryTable.append(tbody);
+}
+
+function appendValuesToLine(line, rowNum, summary_data, version, css_classes) {
+	var sum = summary_data[version][NUMBER_OF_CATEGORIES];
+	for(var j = 0; j < NUMBER_OF_CATEGORIES; j++) {
+		var categoryColumn = document.createElement("td");
+		var value = summary_data[version][j];
[…]

### 2012-10-30 tool/src/main/java/org/testevol/controller/LoginController.java
new version almost finished

@@ -1,0 +1,16 @@
+package org.testevol.controller;
+
+import org.springframework.stereotype.Controller;
+import org.springframework.web.bind.annotation.RequestMapping;
+import org.springframework.web.bind.annotation.RequestMethod;
+
+@Controller
+@RequestMapping("/login")
+public class LoginController {
+
+	@RequestMapping(method = RequestMethod.POST)
+	public String login() {
+		return "redirect:/projects/list";
+	}
+	
+}

### 2012-10-30 tool/src/main/java/org/testevol/controller/ProjectController.java

@@ -72,7 +72,7 @@ public class ProjectController {
 	}
 	
 	@RequestMapping(value="{project}/execute",method = RequestMethod.POST)
-	public String execute(@PathVariable("project") final String projectName, @ModelAttribute Project projectModel) throws Exception {
+	public String execute(@PathVariable("project") final String projectName, final @ModelAttribute Project projectModel) throws Exception {
 
 		final Execution execution = projectRepo.createExecution(projectName, projectModel.getVersionsToExecute());
 		final Project project = execution.getProject();
@@ -84,12 +84,11 @@ public class ProjectController {
 				versionsToExecute.add(version);
 			}
 		}
-		Collections.reverse(versionsToExecute);		
-
+		Collections.reverse(versionsToExecute);
 		new Thread(){
 			@Override
 			public synchronized void run() {
-				DataAnalysis dataAnalysis = new DataAnalysis(configDir, project, versionsToExecute, execution.getExecutionDir());
+				DataAnalysis dataAnalysis = new DataAnalysis(configDir, project, versionsToExecute, execution.getExecutionDir(), !projectModel.isIncludeCoverageAnalysis());
 				try {
 					projectRepo.saveExecution(projectName, execution.getId(), execution.getName(), ExecutionStatus.RUNNING);
 					dataAnalysis.start();
@@ -158,7 +157,17 @@ public class ProjectController {
 		return mav;
 	}
 	
-	
+	@RequestMapping(value="{project}/execution/{id}/report/version",method = RequestMethod.GET)
+	public ModelAndView getDetailedExecutionReport(@PathVariable("project") String projectName, 
+													@PathVariable("id") String id,
+													@RequestParam("name") String version) throws Exception {
+		Execution execution = projectRepo.getExecution(projectName, id);
+		ModelAndView mav = new ModelAndView();
+		mav.addObject("execution", execution);
+		mav.addObject("version", version);
+		mav.setViewName("detailed_report");
+		return mav;
+	}	
 	
 	@RequestMapping(value="{project}/execution/{id}/delete",method = RequestMethod.GET)
 	public String deleteExecution(@PathVariable("project") String projectName, @PathVariable("id") String id) throws Exception {

### 2012-10-30 tool/src/main/java/org/testevol/domain/Project.java

@@ -14,9 +14,17 @@ public class Project {
 	private List<Version> versionsList;
 	private List<String> versionsToExecute;
 	private List<String> branchesToCheckout;
+	private boolean includeCoverageAnalysis;
 	
+	public boolean isIncludeCoverageAnalysis() {
+		return includeCoverageAnalysis;
+	}
+
+	public void setIncludeCoverageAnalysis(boolean includeCoverageAnalysis) {
+		this.includeCoverageAnalysis = includeCoverageAnalysis;
+	}
+
 	public Project() {
-		// TODO Auto-generated constructor stub
 	}
 	
 	public Project(String name) {

### 2012-10-30 tool/src/main/java/org/testevol/engine/Classifier.java

@@ -28,7 +28,6 @@ import org.testevol.engine.domain.Results;
 import org.testevol.engine.domain.TestEvolLog;
 import org.testevol.engine.domain.VersionPair;
 import org.testevol.engine.driver.CopyAndPasteDetectorDriver;
-import org.testevol.engine.util.Utils;
 
 import com.ibm.wala.classLoader.IClass;
 import com.ibm.wala.classLoader.IMethod;
@@ -178,6 +177,8 @@ public class Classifier extends Task {
 	}
 
     private void searchClones(Version oldVersion, Version version, Results results) throws ParseException, IOException{
+    	
+    	log.log("Running clone detection for pair "+oldVersion.getName()+ " - "+version.getName());
         List<Category> categoriesToSearch = new ArrayList<Category>();
         
         categoriesToSearch.add(results.getCategoryC1());
@@ -206,6 +207,16 @@ public class Classifier extends Task {
         List<String> clonesOnCategory7 = performaCloneAnalysisCategory(version, oldVersion, results.getCategoryC7(), categoriesToSearch);            
         List<String> clonesOnCategory8 = performaCloneAnalysisCategory(version, oldVersion, results.getCategoryC8(), categoriesToSearch);
 
+        int totalNumberOfClonesFound = 	clonesOnCategory1.size()+clonesOnCategory2.size()+clonesOnCategory3.size()+
+        								clonesOnCategory4.size()+clonesOnCategory5.size()+clonesOnCategory6.size()+
+        								clonesOnCategory7.size()+clonesOnCategory8.size();
+        		
+        if(totalNumberOfClonesFound == 0){
+        	log.log("No clones found");
+        }
+        else{
+        	log.log(totalNumberOfClonesFound+ " clones found");
+        }
         
         results.getCategoryC1().removeTestsFromThisCategory(clonesOnCategory1);
         results.getCategoryC2().removeTestsFromThisCategory(clonesOnCategory2);

### 2012-10-30 tool/src/main/java/org/testevol/engine/DataAnalysis.java

@@ -21,14 +21,17 @@ public class DataAnalysis {
 	private Project project;
 	private List<Version> versions;
 	private File executionFolder;
+	private boolean skipCoverageAnalysis;
 
 	public DataAnalysis(String testevolConfigRoot, Project project,
-			List<Version> versions, File executionFolder) {
+			List<Version> versions, File executionFolder,
+			boolean skipCoverageAnalysis) {
 		super();
 		this.testevolConfigRoot = testevolConfigRoot;
 		this.project = project;
 		this.versions = versions;
 		this.executionFolder = executionFolder;
+		this.skipCoverageAnalysis = skipCoverageAnalysis;
 	}
 
 	/**
@@ -59,14 +62,17 @@ public class DataAnalysis {
 			log.logStrong("Starting Execution...");			
 			for (Version version : versions) {
 				log.log("Setting up version " + version.getName());
-				version.setUp(new File(testevolConfigRoot));
+				if(!version.setUp(new File(testevolConfigRoot))){
+					log.logError("Error while setting up version "+version.getName());
+					throw new RuntimeException();
+				}
 			}
 			Compiler compiler = new Compiler(versions, log);
 			Runner runner = new Runner(versions, log);
 			Differ differ = new Differ(versions, testevolConfigRoot, log);
 			Classifier classifier = new Classifier(versions, differ, log);
 			ReportGenerator reportGenerator = new ReportGenerator(versions,
-					classifier, project.getName(), executionFolder, log);
+					classifier, project.getName(), executionFolder, log, skipCoverageAnalysis);
 
 			compiler.go();
 			runner.go();
@@ -74,9 +80,7 @@ public class DataAnalysis {
 			classifier.go();
 			reportGenerator.go();
 
-		} catch (Exception e) {
-			e.printStackTrace();
-		} finally {
+		}finally {
 			long end = System.currentTimeMillis();
 			if(log != null){
 				log.addLine();

### 2012-10-30 tool/src/main/java/org/testevol/engine/ReportGenerator.java

@@ -1,7 +1,6 @@
 package org.testevol.engine;
 
 import java.io.File;
-import java.io.FileOutputStream;
 import java.util.ArrayList;
 import java.util.List;
 import java.util.Map;
@@ -15,19 +14,22 @@ import org.testevol.engine.domain.TestEvolLog;
 import org.testevol.engine.domain.VersionPair;
 import org.testevol.engine.report.CSVReport;
 import org.testevol.engine.report.HtmlReport;
-import org.testevol.engine.util.Utils;
 
 public class ReportGenerator extends Task {
 
 	private Classifier classifier;
 	private String projectName;
 	private File reportsFolder;
+	private boolean skipCoverageAnalysis;
 	
-	public ReportGenerator(List<Version> versions, Classifier classifier, String projectName, File reportsFolder, TestEvolLog log) {
+	public ReportGenerator(List<Version> versions, Classifier classifier,
+			String projectName, File reportsFolder, TestEvolLog log,
+			boolean skipCoverageAnalysis) {
 		super(versions, log);
 		this.classifier = classifier;
 		this.projectName = projectName;
 		this.reportsFolder = reportsFolder;
+		this.skipCoverageAnalysis = skipCoverageAnalysis;
 	}
 
 
@@ -37,56 +39,61 @@ public class ReportGenerator extends Task {
 
 		Map<VersionPair, Results> resultsMap = classifier.getResults();
         List<VersionPair> versionPairs = new ArrayList<VersionPair>();
-
-        log.logStrong("Generating report...");
+        
+        if(skipCoverageAnalysis){
+        	log.logStrong("Skipping coverage analysis...");
+        }
+        else{
+        	log.logStrong("Starting coverage analysis...");
+        }
+        
         
 		for (Version version:versions) {
 			
 			if (oldVersion == null) {
 				oldVersion = version;
-				Utils.println("\nReport: Skipping first version: " + version.getName());
 				continue;
 			}
 
-			log.log("Generation report for pair " + oldVersion.getName() + " - " + version.getName());
-			
 			VersionPair versionPair = new VersionPair(oldVersion, version);
 			versionPairs.add(versionPair);
 			Results results = resultsMap.get(versionPair);
 			
-			log.log("Analysing coverage");
-			CategoryC5 categoryC5 = results.getCategoryC5();
-			categoryC5.analyseCoverage();
-			
-			CategoryC8 categoryC8 = results.getCategoryC8();
+			if(!skipCoverageAnalysis){
[…]

### 2012-10-30 tool/src/main/java/org/testevol/engine/Runner.java

@@ -52,7 +52,7 @@ public class Runner extends Task {
             // first version
             if (oldVersion != null) {
                 // T0P1
-                classpath = Utils.getClassPathInDir(version.getDirectory());
+                classpath = version.getClassPath();
                 classpath += File.pathSeparator + oldVersion.getBinTestDir();
                 classpath += File.pathSeparator + version.getBinDir();
                 versionToClasspathMap.put("T0P1", classpath);
@@ -60,7 +60,7 @@ public class Runner extends Task {
                 // alternateClasspath = this.buildAlternateClasspath(classpath,
                 // verDir, oldDir);
                 // T1P0
-                classpath = Utils.getClassPathInDir(oldVersion.getDirectory());
+                classpath = oldVersion.getClassPath();
                 classpath += File.pathSeparator + version.getBinTestDir();
                 classpath += File.pathSeparator + oldVersion.getBinDir();
                 versionToClasspathMap.put("T1P0", classpath);

### 2012-10-30 tool/src/main/java/org/testevol/engine/TestRunner.java

@@ -5,7 +5,6 @@ import java.lang.reflect.Constructor;
 import java.lang.reflect.InvocationTargetException;
 import java.lang.reflect.Method;
 import java.lang.reflect.Modifier;
-import java.net.URL;
 import java.util.ArrayList;
 import java.util.Collection;
 import java.util.HashMap;
@@ -35,6 +34,17 @@ public class TestRunner {
 	
 	private static final String SET_UP_METHOD = "setUp";
 	private static final String TEAR_DOWN_METHOD = "tearDown";
+	
+	public static final String IgnoreAnnotation = "org.junit.Ignore";
+	public static final String BeforeAnnotation = "org.junit.Before";
+	public static final String BeforeClassAnnotation = "org.junit.BeforeClass";
+	public static final String AfterAnnotation = "org.junit.After";
+	public static final String AfterClassAnnotation = "org.junit.AfterClass";
+	public static final String TestAnnotation = "org.junit.Test";
+	public static final String TestNoneAnnotation = "org.junit.Test$None";
+	public static final String RunWith = "org.junit.runner.RunWith";
+	public static final String Parameterized = "org.junit.runners.Parameterized";
+	public static final String Parameters = "org.junit.runners.Parameterized$Parameters";
 
 	private TrexClassLoader trexClsLoader;
 
@@ -109,14 +119,13 @@ public class TestRunner {
 
 		Method beforeClassMethod = null;
 		Method afterClassMethod = null;
-		//HERE444
-//		for (Method m : klass.getMethods()) {
-//			if (m.isAnnotationPresent(AfterClass.class)) {
-//				afterClassMethod = m;
-//			} else if (m.isAnnotationPresent(BeforeClass.class)) {
-//				beforeClassMethod = m;
-//			}
-//		}
+		for (Method m : klass.getMethods()) {
+			if(trexClsLoader.isAnnotationPresent(m, AfterClassAnnotation)){
+				afterClassMethod = m;
+			} else if (trexClsLoader.isAnnotationPresent(m, AfterClassAnnotation)){
+				beforeClassMethod = m;
+			}
+		}
 
 		try {
 			// invoke the setup method
@@ -318,21 +327,21 @@ public class TestRunner {
 
 		Object testObj = null;
 		try {
-			//HERE444
-//			if(cls.isAnnotationPresent(RunWith.class)){
-//				RunWith runWith = cls.getAnnotation(RunWith.class);
[…]

### 2012-10-30 tool/src/main/java/org/testevol/engine/domain/CategoryC5.java

@@ -132,7 +132,6 @@ public class CategoryC5 extends Category {
 	public List<String> hasDecreasedCoverage(Coverage testSuiteCoverage,
 			Coverage testCoverage) {
 		Set<String> linesCoveredByTestSuite = testSuiteCoverage.getCoveredLines();
-		boolean hasDecreasedCoverage = false;
 		List<String> notCoveredLines = new ArrayList<String>();
 		for (String coveredLine : testCoverage.getCoveredLines()) {
 			if (!linesCoveredByTestSuite.contains(coveredLine)) {

### 2012-10-30 tool/src/main/java/org/testevol/engine/domain/CategoryC8.java

@@ -22,10 +22,12 @@ import org.testevol.engine.util.Utils;
 public class CategoryC8 extends Category {
 
 	public Map<String, Boolean> coverageHasImproved;
+	private HashMap<String, List<String>> newCoveredLines;
 	
 	public CategoryC8(Version oldVersion, Version version) {
 		super(CategoryClassification.TESTADD_P, oldVersion, version);
 		coverageHasImproved = new HashMap<String, Boolean>();
+		newCoveredLines = new HashMap<String, List<String>>();
 	}
 
 	public void init() {
@@ -96,7 +98,18 @@ public class CategoryC8 extends Category {
 			if(testCoverage == null){
 				throw new RuntimeException("Did you executed coverage analysis for added test methods?");
 			}
-			coverageHasImproved.put(test, hasImprovedCoverage(testSuiteCoverage, testCoverage));
+			
+			List<String> coveredLines = hasImprovedCoverage(testSuiteCoverage, testCoverage);
+			coverageHasImproved.put(test, !coveredLines.isEmpty());
+			this.newCoveredLines.put(test,coveredLines);
+			
+			//	coverageHasImproved.put(test, hasImprovedCoverage(testSuiteCoverage, testCoverage));
+
+//			List<String> notCoveredLines = hasDecreasedCoverage(testSuiteCoverage, testCoverage);
+//			coverageHasDecreased.put(test, 	notCoveredLines.isEmpty());
+//			this.notCoveredLines.put(test, notCoveredLines);
+
+			
 			
 			System.out.println("Coverage:"+testCoverage.toString());
 						
@@ -114,20 +127,23 @@ public class CategoryC8 extends Category {
 		return testsSameCoverage;
 	}
 	
-	public boolean hasImprovedCoverage(Coverage testSuiteCoverage, Coverage testCoverage) {
+	public List<String> hasImprovedCoverage(Coverage testSuiteCoverage, Coverage testCoverage) {
 		Set<String> linesCoveredByTestSuite = testSuiteCoverage.getCoveredLines();
-		boolean hasImprovedCoverage = false;
+		List<String> newCoveredLines = new ArrayList<String>();
 		for (String coveredLine : testCoverage.getCoveredLines()) {
 			if (!linesCoveredByTestSuite.contains(coveredLine)) {
-				hasImprovedCoverage = true;
+				newCoveredLines.add(coveredLine);
 				break;
 			}
 		}
-
[…]

### 2012-10-30 tool/src/main/java/org/testevol/engine/report/HtmlReport.java

@@ -74,6 +74,10 @@ public class HtmlReport {
 		objectMapper.writeValue(coverageLoss, results.getCategoryC5().getNotCoveredLines());
 		
 		resultJS.append(createJSFunction("getCoverageLost", "return " + coverageLoss+ ";"));
+		
+		StringWriter coverageImprovement = new StringWriter();
+		objectMapper.writeValue(coverageImprovement, results.getCategoryC8().getNewCoveredLines());
+		resultJS.append(createJSFunction("getCoverageImprovement", "return " + coverageImprovement+ ";"));
 
 
 //		fileWriter.write(resultJS.toString());

### 2012-10-30 tool/src/main/java/org/testevol/engine/util/TrexClassLoader.java

@@ -17,11 +17,9 @@ import java.util.Set;
 import java.util.jar.JarEntry;
 import java.util.jar.JarFile;
 
-public class TrexClassLoader extends URLClassLoader {
+import org.testevol.engine.TestRunner;
 
-	public static final String IgnoreAnnotation = "org.junit.Ignore";
-	public static final String TestAnnotation = "org.junit.Test";
-	public static final String TestNoneAnnotation = "org.junit.Test.None";
+public class TrexClassLoader extends URLClassLoader {
 	
 	private HashMap<String, Class<?>> loadedClasses;
 	
@@ -106,7 +104,7 @@ public class TrexClassLoader extends URLClassLoader {
 	}
 	
 	public boolean isIgnoredClass(Class<?> cls) throws ClassNotFoundException {
-		return isAnnotationPresent(cls,IgnoreAnnotation);
+		return isAnnotationPresent(cls, TestRunner.IgnoreAnnotation);
 	}
 	
 	
@@ -120,6 +118,11 @@ public class TrexClassLoader extends URLClassLoader {
 		}
 		if(isTestClass("org.junit.internal.runners.JUnit38ClassRunner", className)){
 			return true;
+		}
+		for(Method m:cls.getMethods()){
+			if(isTestMethod(m)){
+				return true;
+			}
 		}
 		return false;
 	}
@@ -141,12 +144,22 @@ public class TrexClassLoader extends URLClassLoader {
 
 	public boolean isTestMethod(Method method) {
 		return (method.getName().startsWith("test") || isAnnotationPresent(
-				method, TestAnnotation))
-				&& !isAnnotationPresent(method, IgnoreAnnotation);
+				method, TestRunner.TestAnnotation))
+				&& !isAnnotationPresent(method, TestRunner.IgnoreAnnotation);
 	}
 
 	public Annotation getAnnotation(Method method, String annotationName) {
-		for(Annotation annotation:method.getAnnotations()){
+		
+		return getAnnotation(method.getAnnotations(), annotationName);
+	}
+	
+	public Annotation getAnnotation(Class clazz, String annotationName) {
+		
+		return getAnnotation(clazz.getAnnotations(), annotationName);
+	}
+	
+	public Annotation getAnnotation(Annotation[] annotations, String annotationName){
+		for(Annotation annotation:annotations){
 			if(annotation.annotationType().getName().equals(annotationName)){
 				return annotation;
 			}

### 2012-10-30 tool/src/main/java/org/testevol/engine/util/Utils.java

@@ -25,6 +25,8 @@ import java.util.jar.JarOutputStream;
 import java.util.zip.ZipEntry;
 import java.util.zip.ZipInputStream;
 
+import org.testevol.engine.TestRunner;
+
 public class Utils {
 	private static boolean diagnosticOn = true;
 
@@ -227,27 +229,7 @@ public class Utils {
 	}
 
 	public static boolean isIgnoredMethod(Method method, TrexClassLoader classLoader) {
-		return classLoader.isAnnotationPresent(method, TrexClassLoader.IgnoreAnnotation);
-	}
-
-	public static String getClassPathInDir(File verDir) {
-		String classpath = ".";
-		File cpfile = new File(verDir, "classpath.txt");
-		File libDir = new File(verDir, "lib");
-
-		if (!cpfile.exists()) {
-			// No classpath.txt file in verDir
-			// Using all jar files under "lib"
-			for (File jar : Utils.getMatchingFiles(libDir, ".*jar$")) {
-				classpath = classpath + File.pathSeparator
-						+ jar.getAbsolutePath();
-			}
-		} else {
-			classpath = Utils.makePathsAbsolute(
-					Utils.getFileContentAsString(cpfile),
-					verDir.getAbsolutePath());
-		}
-		return classpath;
+		return classLoader.isAnnotationPresent(method, TestRunner.IgnoreAnnotation);
 	}
 
 	public static HashSet<URL> getClassPathFromString(String classpath) {

### 2012-10-30 tool/src/main/java/org/testevol/versioncontrol/GitImpl.java

@@ -2,10 +2,14 @@ package org.testevol.versioncontrol;
 
 import java.io.File;
 import java.util.ArrayList;
+import java.util.Collections;
+import java.util.HashSet;
 import java.util.List;
+import java.util.Set;
 
 import org.apache.commons.io.FileUtils;
 import org.eclipse.jgit.api.Git;
+import org.eclipse.jgit.api.ListBranchCommand.ListMode;
 import org.eclipse.jgit.api.PullResult;
 import org.eclipse.jgit.lib.Ref;
 import org.testevol.domain.Version;
@@ -29,14 +33,36 @@ public class GitImpl extends VersionControlSystem {
 
 		File dir = Utils.getTempDir();
 		List<String> branches = new ArrayList<String>();
-
 		try {
 			Git git = Git.cloneRepository().setURI(url).setDirectory(dir)
 					.setNoCheckout(true).call();
 
+			Set<String> availableRefs = new HashSet<String>();
 			for (Ref ref : git.lsRemote().setHeads(true).call()) {
-				branches.add(ref.getName());
+				availableRefs.add(ref.getName());
 			}
+			
+			boolean hasMaster = false;
+			for(Ref ref : git.branchList().setListMode(ListMode.REMOTE).call()){
+				//System.out.println(ref.getName());
+				String name = ref.getName();
+				if(name.contains("/")){
+					name = name.substring(name.lastIndexOf("/")+1);
+				}
+				String headRef = "refs/heads/"+name;
+				if(availableRefs.contains(headRef)){
+					if(!hasMaster && "master".equals(name)){
+						hasMaster = true;
+					}
+					else{
+						branches.add(headRef);						
+					}					
+				}
+			}
+			if(hasMaster){
+				branches.add("refs/heads/master");
+			}
+			Collections.reverse(branches);
 		} finally {
 			if (dir != null) {
 				FileUtils.deleteDirectory(dir);

### 2012-10-30 tool/src/main/webapp/js/diff_match_patch.js

@@ -1,0 +1,49 @@
+(function(){function diff_match_patch(){this.Diff_Timeout=1;this.Diff_EditCost=4;this.Match_Threshold=0.5;this.Match_Distance=1E3;this.Patch_DeleteThreshold=0.5;this.Patch_Margin=4;this.Match_MaxBits=32}
+diff_match_patch.prototype.diff_main=function(a,b,c,d){"undefined"==typeof d&&(d=0>=this.Diff_Timeout?Number.MAX_VALUE:(new Date).getTime()+1E3*this.Diff_Timeout);if(null==a||null==b)throw Error("Null input. (diff_main)");if(a==b)return a?[[0,a]]:[];"undefined"==typeof c&&(c=!0);var e=c,f=this.diff_commonPrefix(a,b),c=a.substring(0,f),a=a.substring(f),b=b.substring(f),f=this.diff_commonSuffix(a,b),g=a.substring(a.length-f),a=a.substring(0,a.length-f),b=b.substring(0,b.length-f),a=this.diff_compute_(a,
+b,e,d);c&&a.unshift([0,c]);g&&a.push([0,g]);this.diff_cleanupMerge(a);return a};
+diff_match_patch.prototype.diff_compute_=function(a,b,c,d){if(!a)return[[1,b]];if(!b)return[[-1,a]];var e=a.length>b.length?a:b,f=a.length>b.length?b:a,g=e.indexOf(f);if(-1!=g)return c=[[1,e.substring(0,g)],[0,f],[1,e.substring(g+f.length)]],a.length>b.length&&(c[0][0]=c[2][0]=-1),c;if(1==f.length)return[[-1,a],[1,b]];return(e=this.diff_halfMatch_(a,b))?(f=e[0],a=e[1],g=e[2],b=e[3],e=e[4],f=this.diff_main(f,g,c,d),c=this.diff_main(a,b,c,d),f.concat([[0,e]],c)):c&&100<a.length&&100<b.length?this.diff_lineMode_(a,
+b,d):this.diff_bisect_(a,b,d)};
[…]

### 2012-10-30 tool/src/main/webapp/js/testevol.js

@@ -1,23 +1,41 @@
 var NUMBER_OF_CATEGORIES = 8;
 var versionsSummary = {};
 
-function getCategoryLabel(index) {
+function getCategoryLabel(index, escape) {
 	switch(index) {
 		case 0:
 			return 'TESTREP';
 		case 1:
 			return 'TESTMODNOTREP';
 		case 2:
+			if(escape){
+				return 'TESTDEL_AE_RE';
+			}
 			return 'TESTDEL (AE|RE)';
 		case 3:
+			if(escape){
+				return 'TESTDEL_CE';
+			}
 			return 'TESTDEL (CE)';
 		case 4:
+			if(escape){
+				return 'TESTDEL_P';
+			}
 			return 'TESTDEL (P)';
 		case 5:
+			if(escape){
+				return 'TESTADD_AE_RE_';
+			}
 			return 'TESTADD (AE|RE)';
 		case 6:
+			if(escape){
+				return 'TESTADD_CE';
+			}
 			return 'TESTADD (CE)';
 		case 7:
+			if(escape){
+				return 'TESTADD_P';
+			}
 			return 'TESTADD (P)';
 	}
 }
@@ -31,10 +49,8 @@ function isCoverageAwareCategory(category) {
 
 }
 
-function createSummaryTable(summaryTable, versions, summary_data) {
+function createSummaryTable(summaryTable, versions, summary_data, url) {
 	//add header
-	var firstLine = document.createElement("tr");
-
 	var line = document.createElement("tr");
 	var leftMostColumn = document.createElement("td");
 	leftMostColumn.innerHTML = "All Versions";
@@ -50,7 +66,7 @@ function createSummaryTable(summaryTable, versions, summary_data) {
 		line = document.createElement("tr");
 		var versionsColumn = document.createElement("td");
 		var link = document.createElement("a");
-		link.href = version + "/report.html";
+		link.href = url+'?name='+version;
 		link.innerText = previousVersion + ' - ' + version;
 		versionsColumn.appendChild(link);
 		line.appendChild(versionsColumn);
@@ -127,10 +143,10 @@ function toggleLeftBar(op) {
 
 function createTable(category) {
 	$("#dataTable").empty();
-	$("#headerAccordion").html("Tests on category " + category);
+	$("#headerCateogry").html("Tests on category " + category);
 	var packages = getCategories()[category];
 	if(packages.length == 0) {
-		$("#dataTable").html("<tr><td>No tests found in this category.</td></tr>")
[…]

### 2012-10-30 tool/src/test/java/org/testevol/versioncontrol/GitImplTest.java

@@ -3,15 +3,26 @@ package org.testevol.versioncontrol;
 import java.io.File;
 import java.util.Arrays;
 
-import org.junit.Test;
+import junit.framework.Assert;
 
+import org.junit.Test;
 
 public class GitImplTest {
 
-	@Test
+	//@Test
 	public void checkouTest() throws Exception {
 		GitImpl git = new GitImpl("git://github.com/leandroshp/math.git");
-		git.checkout(new File("/home/leandro/Documents/Atlanta/tmp/Versions/math"), Arrays.asList("refs/heads/v1","refs/heads/master"));
+		git.checkout(new File(
+				"/home/leandro/Documents/Atlanta/tmp/Versions/math"), Arrays
+				.asList("refs/heads/v1", "refs/heads/master"));
 	}
-	
+
+	@Test
+	public void getBranches() throws Exception {
+		GitImpl git = new GitImpl("git://github.com/testevol/google-gson.git");
+		Assert.assertEquals(Arrays.asList("refs/heads/master",
+				"refs/heads/v.1.1.1", "refs/heads/v.1.1", "refs/heads/v.1.0"),
+				git.getBranches());
+	}
+
 }

### 2012-11-01 tool/src/main/java/org/testevol/controller/ProjectController.java
Bug fixes and new Features

@@ -1,6 +1,9 @@
 package org.testevol.controller;
 
 import java.io.File;
+import java.io.FileInputStream;
+import java.io.IOException;
+import java.io.InputStream;
 import java.io.PrintWriter;
 import java.io.StringWriter;
 import java.util.ArrayList;
@@ -9,7 +12,11 @@ import java.util.HashMap;
 import java.util.List;
 import java.util.Map;
 
+import javax.servlet.http.HttpServletResponse;
+
 import org.apache.commons.io.FileUtils;
+import org.apache.commons.io.IOUtils;
+import org.eclipse.jgit.api.errors.TransportException;
 import org.springframework.beans.factory.annotation.Autowired;
 import org.springframework.beans.factory.annotation.Value;
 import org.springframework.stereotype.Controller;
@@ -22,7 +29,9 @@ import org.springframework.web.bind.annotation.ResponseBody;
 import org.springframework.web.servlet.ModelAndView;
 import org.testevol.domain.Project;
 import org.testevol.domain.ProjectRepository;
+import org.testevol.domain.RepositoryInfo;
 import org.testevol.domain.Version;
+import org.testevol.domain.VersionSettings;
 import org.testevol.engine.DataAnalysis;
 import org.testevol.engine.domain.Execution;
 import org.testevol.engine.report.ExecutionStatus;
@@ -157,6 +166,25 @@ public class ProjectController {
 		return mav;
 	}
 	
+	@RequestMapping(value = "{project}/execution/{id}/report/csv", method = RequestMethod.GET)
+	public void getFile( @PathVariable("project") String projectName, 
+						  @PathVariable("id") String id,
+						  HttpServletResponse response) throws Exception {
+		Execution execution = projectRepo.getExecution(projectName, id);
+	    try {
+	      // get your file as InputStream
+	      InputStream is = new FileInputStream(execution.getCSVReport());
+	      // copy it to response's OutputStream
+	      IOUtils.copy(is, response.getOutputStream());
+	      response.setContentType("text/plain");
+	      response.setHeader("Content-Disposition", "attachment; filename="+execution.getName()+".txt");
+	      response.flushBuffer();
+	    } catch (IOException ex) {
+	      throw new RuntimeException("Error while generating Report!");
+	    }
+
+	}
+	
 	@RequestMapping(value="{project}/execution/{id}/report/version",method = RequestMethod.GET)
[…]

### 2012-11-01 tool/src/main/java/org/testevol/domain/Project.java

@@ -4,13 +4,10 @@ import java.util.List;
 
 import org.testevol.versioncontrol.VersionControlSystem;
 
-import static org.testevol.versioncontrol.VersionControlSystem.GIT;
-
 public class Project {
 
 	private String name;
-	private String vcs;
-	private String gitUrl;
+	private RepositoryInfo repositoryInfo;
 	private List<Version> versionsList;
 	private List<String> versionsToExecute;
 	private List<String> branchesToCheckout;
@@ -39,30 +36,11 @@ public class Project {
 	public void setName(String name) {
 		this.name = name;
 	}
-
-	public String getVcs() {
-		return vcs;
-	}
-
-	public void setVcs(String vcs) {
-		this.vcs = vcs;
-	}
-
-	public String getGitUrl() {
-		return gitUrl;
-	}
 	
 	public String getUrl() {
-		if(GIT.equals(vcs)){
-			return getGitUrl();	
-		}
-		return null;
+		return repositoryInfo.getUrl();
 	}
-
-	public void setGitUrl(String gitUrl) {
-		this.gitUrl = gitUrl;
-	}
-
+	
 	public List<Version> getVersionsList() {
 		return versionsList;
 	}
@@ -80,7 +58,15 @@ public class Project {
 	}
 
 	public VersionControlSystem getVersionControlSystem(){
-		return VersionControlSystem.getInstance(getVcs(), getUrl());
+		return VersionControlSystem.getInstance(repositoryInfo);
+	}
+	
+	public void setRepositoryInfo(RepositoryInfo repositoryInfo) {
+		this.repositoryInfo = repositoryInfo;
+	}
+	
+	public RepositoryInfo getRepositoryInfo() {
+		return repositoryInfo;
 	}
 	
 	public void setVersionsToExecute(List<String> versionsToExecute) {
@@ -95,15 +81,16 @@ public class Project {
 		if(getName() == null || getName().trim().isEmpty()){
 			return false;
 		}
-		String vcs = getVcs();
+		if(getRepositoryInfo() == null){
+			return false;
+		}
+		String vcs = getRepositoryInfo().getType();
 		if(vcs == null || vcs.trim().isEmpty()){
 			return false;
 		}
-		if(GIT.equals(vcs)){
-			if(getGitUrl() == null || getGitUrl().trim().isEmpty()){
-				return false;
-			}	
-		}
+		if(getUrl() == null || getUrl().trim().isEmpty()){
+			return false;
+		}	
[…]

### 2012-11-01 tool/src/main/java/org/testevol/domain/ProjectRepository.java

@@ -22,5 +22,6 @@ public interface ProjectRepository {
 	public void saveExecution(String projectName, String id, String name, ExecutionStatus status) throws Exception;
 	public List<Execution> getExecutions(Project project) throws Exception;
 	public void deleteExecution(String projectName, String id) throws IOException;
+	public void updateVersionSettings(VersionSettings versionSettings) throws Exception;
 	
 }

### 2012-11-01 tool/src/main/java/org/testevol/domain/RepositoryInfo.java

@@ -1,0 +1,36 @@
+package org.testevol.domain;
+
+public class RepositoryInfo {
+
+	private String type;
+	private String url;
+	private String username;
+	private String password;
+	
+	public RepositoryInfo() { }
+		
+	public String getType() {
+		return type;
+	}
+	public void setType(String type) {
+		this.type = type;
+	}
+	public String getUrl() {
+		return url;
+	}
+	public void setUrl(String url) {
+		this.url = url;
+	}
+	public String getUsername() {
+		return username;
+	}
+	public void setUsername(String username) {
+		this.username = username;
+	}
+	public String getPassword() {
+		return password;
+	}
+	public void setPassword(String password) {
+		this.password = password;
+	}
+}

### 2012-11-01 tool/src/main/java/org/testevol/domain/Version.java

@@ -26,6 +26,13 @@ import org.testevol.versioncontrol.VersionControlSystem;
 
 public class Version {
 
+	public static final String LIB_DIR = "lib.dir";
+	public static final String TESTS_SRC = "tests.src";
+	public static final String TESTS_RESOURCES = "tests.resources";
+	public static final String JAVA_RESOURCES = "java.resources";
+	public static final String JAVA_SRC = "java.src";
+	public static final String JAVA_VERSION = "java.version";
+
 	private File versionDir;
 	private File baseBuildDir;
 	private String name;
@@ -34,10 +41,11 @@ public class Version {
 	// Used in case of a maven project
 	private Model mavenModel;
 	private Properties testEvolProperties;
+	private VersionSettings versionSettings;
 
 	public Version(File versionDir) throws Exception {
 		super();
-		this.versionDir = versionDir;		
+		this.versionDir = versionDir;
 		name = versionDir.getName();
 		properties = new Properties();
 		if (getPropertiesFile().exists()) {
@@ -46,29 +54,28 @@ public class Version {
 		loadConfiguration();
 	}
 
-	private void deleteClassesFromResources(File dir) throws IOException{
-		
-		
-		for(Object fileObj : FileUtils.listFiles(dir, new String[]{"class"}, true)){
-			if(fileObj instanceof File){
+	private void deleteClassesFromResources(File dir) throws IOException {
+
+		for (Object fileObj : FileUtils.listFiles(dir,
+				new String[] { "class" }, true)) {
+			if (fileObj instanceof File) {
 				((File) fileObj).delete();
 			}
 		}
 		deleteEmptyDirectories(dir);
-		
+
 	}
 
-	private boolean deleteEmptyDirectories(File dir){
+	private boolean deleteEmptyDirectories(File dir) {
 		boolean empty = true;
-		for(File file:dir.listFiles()){
-			if(file.isDirectory()){
+		for (File file : dir.listFiles()) {
+			if (file.isDirectory()) {
 				empty = deleteEmptyDirectories(file) && empty;
-			}
-			else{
+			} else {
 				empty = false;
 			}
 		}
-		if(empty){
+		if (empty) {
 			dir.delete();
 		}
 		return empty;
@@ -90,50 +97,72 @@ public class Version {
 		return new File(getBuildDir(), "bintmp");
 	}
 
[…]

### 2012-11-01 tool/src/main/java/org/testevol/domain/VersionSettings.java

@@ -1,0 +1,126 @@
+package org.testevol.domain;
+
+import java.io.IOException;
+import java.io.StringWriter;
+
+import org.codehaus.jackson.JsonGenerationException;
+import org.codehaus.jackson.annotate.JsonIgnore;
+import org.codehaus.jackson.map.JsonMappingException;
+import org.codehaus.jackson.map.ObjectMapper;
+import org.codehaus.jackson.map.annotate.JsonSerialize;
+import org.codehaus.jackson.map.annotate.JsonSerialize.Inclusion;
+
+@JsonSerialize(include = Inclusion.NON_NULL)
+public class VersionSettings {
+
+	public VersionSettings() {
+		// TODO Auto-generated constructor stub
+	}
+
+	public VersionSettings(String source, String resource, String testSources,
+			String testResource, String lib, String javaversion) {
+		super();
+		
+		this.source = correct(source);
+		this.resource = correct(resource);
+		this.testSources = correct(testSources);
+		this.testResource = correct(testResource);
+		this.lib = correct(lib);
+		this.javaversion = correct(javaversion);
+	}
+
+	private String correct(String value){
+		if(value != null && !value.trim().isEmpty()){
+			return value.trim();
+		}
+		return null;
+	}
+	
+	public String getProject() {
+		return project;
+	}
+
+	public void setProject(String project) {
+		this.project = project;
+	}
+
+	public String getVersion() {
+		return version;
+	}
+
+	public void setVersion(String version) {
+		this.version = version;
+	}
+
+	private String project;
+	private String version;
+	private String source;
+	private String resource;
+	private String testSources;
+	private String testResource;
+	private String lib;
+	private String javaversion;
+
+	public String getSource() {
+		return source;
+	}
+
+	public void setSource(String source) {
+		this.source = source;
+	}
+
+	public String getResource() {
+		return resource;
+	}
+
+	public void setResource(String resource) {
+		this.resource = resource;
+	}
+
+	public String getTestSources() {
+		return testSources;
+	}
+
+	public void setTestSources(String testSources) {
+		this.testSources = testSources;
+	}
+
+	public String getTestResource() {
+		return testResource;
+	}
+
+	public void setTestResource(String testResource) {
+		this.testResource = testResource;
+	}
+
+	public String getLib() {
+		return lib;
+	}
+
+	public void setLib(String lib) {
+		this.lib = lib;
+	}
+
[…]

### 2012-11-01 tool/src/main/java/org/testevol/engine/ReportGenerator.java

@@ -95,7 +95,7 @@ public class ReportGenerator extends Task {
         	Version version = versionPair.getVersion();
         	log.log("Generating report for pair " + oldVersion.getName() + " - " + version.getName());
         	Results results = resultsMap.get(versionPair);
-            CSVReport.generateReport(oldVersion, version, results, reportsFolder);
+            CSVReport.generateReport(oldVersion, version, results, reportsFolder, !skipCoverageAnalysis);
     		new HtmlReport().generateReport(oldVersion, version, results, reportsFolder);
         }
 	

### 2012-11-01 tool/src/main/java/org/testevol/engine/domain/Execution.java

@@ -101,4 +101,8 @@ public class Execution {
 
 		
 	}
+
+	public File getCSVReport() {
+		return new File(executionDir,"results.txt");
+	}
 }

### 2012-11-01 tool/src/main/java/org/testevol/engine/report/CSVReport.java

@@ -13,7 +13,7 @@ import org.testevol.engine.domain.Results;
 public class CSVReport {
 
 	public static void generateReport(Version oldVersion,  Version version,
-			Results results, File reportsDir) throws IOException {
+			Results results, File reportsDir, boolean coverageEnabled) throws IOException {
 		
 		File csvResults = new File(reportsDir, "results.txt");
 		
@@ -23,17 +23,41 @@ public class CSVReport {
 		if (!fileAlreadyExists) {
 			csvResults.createNewFile();
 		}
-//		if (!c1Results.exists()) {
-//			c1Results.createNewFile();
-//		}
+		
+		
 		FileWriter fileWriter = new FileWriter(csvResults, true);
-		//FileWriter fileWriterC1 = new FileWriter(c1Results, true);
-
 		String lineSeparator = System.getProperty("line.separator");
-		if (fileAlreadyExists) {
-			fileWriter.append(lineSeparator);
+		if (!fileAlreadyExists) {
+			//write header
+			fileWriter.append("#");
+			fileWriter.append(results.getCategoryC1().getClassification().getLabel());
+			fileWriter.append(",");
+			fileWriter.append(results.getCategoryC2().getClassification().getLabel());
+			fileWriter.append(",");
+			fileWriter.append(results.getCategoryC3().getClassification().getLabel());
+			fileWriter.append(",");
+			fileWriter.append(results.getCategoryC4().getClassification().getLabel());
+			fileWriter.append(",");
+			fileWriter.append(results.getCategoryC5().getClassification().getLabel()+" - SAME COVERAGE ");
+			fileWriter.append(",");
+			fileWriter.append(results.getCategoryC5().getClassification().getLabel()+" - COVERAGE LOSS");
+			fileWriter.append(",");
+			fileWriter.append(results.getCategoryC6().getClassification().getLabel());
+			fileWriter.append(",");
+			fileWriter.append(results.getCategoryC7().getClassification().getLabel());
+			fileWriter.append(",");
+			fileWriter.append(results.getCategoryC6().getClassification().getLabel());
+			fileWriter.append(",");
+			fileWriter.append(results.getCategoryC8().getClassification().getLabel()+" - SAME COVERAGE ");
+			fileWriter.append(",");
+			fileWriter.append(results.getCategoryC8().getClassification().getLabel()+" - COVERAGE IMPROVED");
+			
+			if(!coverageEnabled){
[…]

### 2012-11-01 tool/src/main/java/org/testevol/infra/ProjectRepoFileSystem.java

@@ -2,6 +2,7 @@ package org.testevol.infra;
 
 import java.io.File;
 import java.io.FileInputStream;
+import java.io.FileOutputStream;
 import java.io.IOException;
 import java.util.ArrayList;
 import java.util.Arrays;
@@ -18,6 +19,7 @@ import org.springframework.stereotype.Repository;
 import org.testevol.domain.Project;
 import org.testevol.domain.ProjectRepository;
 import org.testevol.domain.Version;
+import org.testevol.domain.VersionSettings;
 import org.testevol.engine.domain.Execution;
 import org.testevol.engine.report.ExecutionStatus;
 import org.testevol.engine.util.Utils;
@@ -49,11 +51,19 @@ public class ProjectRepoFileSystem implements ProjectRepository {
 			throw new RuntimeException("Project already exists");
 		}
 
+		
+		
 		//TODO: implement this inside version object
 		VersionControlSystem versionControlSystem = project
 				.getVersionControlSystem();
 		File projectDir = new File(projectsDir, project.getName());
-		versionControlSystem.checkout(projectDir, project.getBranchesToCheckout());
+		projectDir.mkdirs();		
+		try {
+			versionControlSystem.checkout(projectDir, project.getBranchesToCheckout());
+		} catch (Exception e) {
+			FileUtils.deleteDirectory(projectDir);
+			throw e;
+		}
 	}
 
 	public boolean exists(String projectName) {
@@ -243,6 +253,29 @@ public class ProjectRepoFileSystem implements ProjectRepository {
 	public List<String> getProjectsNames() {
 		return Arrays.asList(projectsDir.list());
 	
+	}
+
+	@Override
+	public void updateVersionSettings(VersionSettings versionSettings) throws Exception {
+		File projectDir = new File(projectsDir, versionSettings.getProject());
+		File versionDir = new File(projectDir, versionSettings.getVersion());
+		
+		Properties properties = new Properties();
+		properties.setProperty(Version.JAVA_SRC, versionSettings.getSource());
+		properties.setProperty(Version.JAVA_RESOURCES, versionSettings.getResource());
+		properties.setProperty(Version.TESTS_SRC, versionSettings.getTestSources());
+		properties.setProperty(Version.TESTS_RESOURCES, versionSettings.getTestResource());
+		properties.setProperty(Version.LIB_DIR, versionSettings.getLib());
[…]

### 2012-11-01 tool/src/main/java/org/testevol/versioncontrol/GitImpl.java

@@ -1,17 +1,19 @@
 package org.testevol.versioncontrol;
 
 import java.io.File;
+import java.io.IOException;
 import java.util.ArrayList;
 import java.util.Collections;
-import java.util.HashSet;
 import java.util.List;
-import java.util.Set;
 
 import org.apache.commons.io.FileUtils;
+import org.eclipse.jgit.api.CloneCommand;
 import org.eclipse.jgit.api.Git;
-import org.eclipse.jgit.api.ListBranchCommand.ListMode;
 import org.eclipse.jgit.api.PullResult;
 import org.eclipse.jgit.lib.Ref;
+import org.eclipse.jgit.transport.CredentialsProvider;
+import org.eclipse.jgit.transport.UsernamePasswordCredentialsProvider;
+import org.testevol.domain.RepositoryInfo;
 import org.testevol.domain.Version;
 import org.testevol.engine.util.Utils;
 
@@ -19,9 +21,13 @@ public class GitImpl extends VersionControlSystem {
 
 	private String url;
 	private File workingCopy;
+	private String username;
+	private String password;
 
-	public GitImpl(String url) {
-		this.url = url;
+	public GitImpl(RepositoryInfo repositoryInfo) {
+		this.url = repositoryInfo.getUrl();
+		this.username = repositoryInfo.getUsername();
+		this.password = repositoryInfo.getPassword();
 	}
 	
 	public GitImpl(File workingCopy) {
@@ -32,64 +38,65 @@ public class GitImpl extends VersionControlSystem {
 	public List<String> getBranches() throws Exception {
 
 		File dir = Utils.getTempDir();
-		List<String> branches = new ArrayList<String>();
+		List<String> tags = new ArrayList<String>();
 		try {
-			Git git = Git.cloneRepository().setURI(url).setDirectory(dir)
-					.setNoCheckout(true).call();
-
-			Set<String> availableRefs = new HashSet<String>();
-			for (Ref ref : git.lsRemote().setHeads(true).call()) {
-				availableRefs.add(ref.getName());
+			CloneCommand cloneCommand = Git.cloneRepository().setURI(url).setDirectory(dir).setNoCheckout(true);
+			
+			if(username != null && !username.trim().isEmpty() &&
+			   password != null){
+				cloneCommand.setCredentialsProvider(new UsernamePasswordCredentialsProvider(username, password));
 			}
 			
-			boolean hasMaster = false;
[…]

### 2012-11-01 tool/src/main/java/org/testevol/versioncontrol/VersionControlSystem.java

@@ -2,15 +2,16 @@ package org.testevol.versioncontrol;
 
 import java.io.File;
 import java.util.List;
-import java.util.UUID;
+
+import org.testevol.domain.RepositoryInfo;
 
 public abstract class VersionControlSystem {
 	
 	public static String GIT = "git";
-
-	public static VersionControlSystem getInstance(String type, String repoUrl){
-		if(GIT.equals(type)){
-			return new GitImpl(repoUrl);
+	
+	public static VersionControlSystem getInstance(RepositoryInfo repositoryInfo){
+		if(GIT.equals(repositoryInfo.getType())){
+			return new GitImpl(repositoryInfo);
 		}
 		
 		return null;

### 2012-11-01 tool/src/main/webapp/js/help-projects.js

@@ -1,0 +1,10 @@
+var help_project = {
+		"project_name":"Insert the project name.",
+		"project_repository":"Project Repository help",
+		"project_versions":"Select the version that you want to analyse using TestEvol",
+		"project_git_url":"The URL used to retrieve information of your Git repository. Supported only HTTP(s) and Git Read-Only urls."
+};
+
+function show_help_project(message_id){
+	$('#help_message').html(help_project[message_id]);
+}

### 2012-11-01 tool/src/main/webapp/js/tooltips_report.js

@@ -1,0 +1,18 @@
+var tooltips = {
+		"toolTipCatTestRep":"Repaired Tests",
+		"toolTipCatTestModNotRep":"Modified Tests",
+		"toolTipCatTestDel":"All deleted tests",
+		"toolTipCatTestDelAeRe":"Tests deleted because throw an AssertionError or RuntimeException",
+		"toolTipCatTestDelCe":"Tests deleted because they the methods the API they test has become obsolete. Throw a Compilation Error when executed in the new version",
+		"toolTipCatTestP":"Tests deleted that still pass in the new version. Probably redundant tests.",
+		"toolTipTestAdd":"All added tests",
+		"toolTipCatTestAddAeRe":"Tests added to test bug Fixes. Throw an AssertionError or RuntimeException when executed in the old version" ,
+		"toolTipCatTestAddCe":"Tests added to test modifications on the API of the program.  Throw a Compilation Error when executed in the old version",
+		"toolTipCatTestAddP":"Tests added that pass in the old version. Probably to improve the test suite coverage."
+};
+
+function setTooltips(){
+	for (var key in tooltips) {
+		$("#"+key).attr('data-original-title', tooltips[key]);
+	}
+}

### 2012-11-01 tool/src/test/java/org/testevol/versioncontrol/GitImplTest.java

@@ -5,23 +5,31 @@ import java.util.Arrays;
 
 import junit.framework.Assert;
 
+import org.junit.Ignore;
 import org.junit.Test;
+import org.testevol.domain.RepositoryInfo;
 
 public class GitImplTest {
 
-	//@Test
+	@Test
+	@Ignore
 	public void checkouTest() throws Exception {
-		GitImpl git = new GitImpl("git://github.com/leandroshp/math.git");
+		RepositoryInfo repositoryInfo = new RepositoryInfo();
+		repositoryInfo.setUrl("git://github.com/testevol/google-gson.git");
+		
+		GitImpl git = new GitImpl(repositoryInfo);
 		git.checkout(new File(
-				"/home/leandro/Documents/Atlanta/tmp/Versions/math"), Arrays
-				.asList("refs/heads/v1", "refs/heads/master"));
+				"/tmp/gson"), Arrays
+				.asList("v.1.1", "v.1.0"));
 	}
 
 	@Test
 	public void getBranches() throws Exception {
-		GitImpl git = new GitImpl("git://github.com/testevol/google-gson.git");
-		Assert.assertEquals(Arrays.asList("refs/heads/master",
-				"refs/heads/v.1.1.1", "refs/heads/v.1.1", "refs/heads/v.1.0"),
+		RepositoryInfo repositoryInfo = new RepositoryInfo();
+		repositoryInfo.setUrl("git://github.com/testevol/google-gson.git");
+		
+		GitImpl git = new GitImpl(repositoryInfo);
+		Assert.assertEquals(Arrays.asList("v.1.2","v.1.1","v.1.0"),
 				git.getBranches());
 	}
 

### 2012-11-01 tool/src/test/java/org/testevol/domain/VersionTest.java
changes on tomcat config

@@ -1,34 +1,0 @@
-package org.testevol.domain;
-
-import java.io.ByteArrayOutputStream;
-import java.io.File;
-import java.io.PrintStream;
-
-import junit.framework.Assert;
-
-import org.apache.maven.cli.MavenCli;
-import org.junit.Test;
-
-public class VersionTest {
-	
-	@Test
-	public void checkConfiguration() throws Exception{
-		Version version = new Version(new File("/home/leandro/Documents/Atlanta/tmp/Versions/math/v1"));
-		version.setUp(null);
-		Assert.assertEquals("1.6", version.getJavaVersion());
-	}
-	
-	//@Test
-	public void test() {
-		MavenCli maven = new MavenCli();
-		ByteArrayOutputStream baos = new ByteArrayOutputStream();
-		PrintStream ps = new PrintStream(baos);
-		maven.doMain(new String[]{"clean","dependency:copy-dependencies"}, "/home/leandro/Documents/Atlanta/tmp/Versions/math/v1", ps, ps);
-		maven.doMain(new String[]{"clean"}, "/home/leandro/Documents/Atlanta/tmp/Versions/math/v1", System.out, System.out);
-		
-		System.out.println(baos);
-		System.out.println(baos.toString().contains("BUILD SUCCESS"));
-		
-	}
-
-}

### 2012-11-01 tool/src/test/java/org/testevol/versioncontrol/GitImplTest.java
ignore GItTest

@@ -24,6 +24,7 @@ public class GitImplTest {
 	}
 
 	@Test
+	@Ignore
 	public void getBranches() throws Exception {
 		RepositoryInfo repositoryInfo = new RepositoryInfo();
 		repositoryInfo.setUrl("git://github.com/testevol/google-gson.git");

### 2012-11-01 tool/src/test/java/org/testevol/versioncontrol/GitImplTest.java
GItTest

@@ -24,7 +24,6 @@ public class GitImplTest {
 	}
 
 	@Test
-	@Ignore
 	public void getBranches() throws Exception {
 		RepositoryInfo repositoryInfo = new RepositoryInfo();
 		repositoryInfo.setUrl("git://github.com/testevol/google-gson.git");

### 2012-11-01 tool/src/test/java/Test.java
Test class

@@ -1,0 +1,21 @@
+import java.io.File;
+
+import org.testevol.domain.Version;
+
+
+
+public class Test {
+
+	@org.junit.Test
+	public void test() {
+		try {
+			Version version = new Version(new File("/home/leandro/Documents/Atlanta/workspace/testevol-web/testevol-web/tool/tmp/projects/Gson/v.1.0"));
+			version.setUp(new File("/home/leandro/Documents/Atlanta/workspace/testevol-web/testevol-web/tool/config"));
+		} catch (Exception e) {
+			// TODO Auto-generated catch block
+			e.printStackTrace();
+		}
+	}
+	
+	
+}

### 2012-11-01 tool/src/test/java/Test.java
Test class

@@ -6,7 +6,7 @@ import org.testevol.domain.Version;
 
 public class Test {
 
-	@org.junit.Test
+	//@org.junit.Test
 	public void test() {
 		try {
 			Version version = new Version(new File("/home/leandro/Documents/Atlanta/workspace/testevol-web/testevol-web/tool/tmp/projects/Gson/v.1.0"));

### 2012-11-01 tool/src/main/java/org/testevol/controller/ProjectController.java
new cli for maven

@@ -177,7 +177,7 @@ public class ProjectController {
 	      // copy it to response's OutputStream
 	      IOUtils.copy(is, response.getOutputStream());
 	      response.setContentType("text/plain");
-	      response.setHeader("Content-Disposition", "attachment; filename="+execution.getName()+".txt");
+	      response.setHeader("Content-Disposition", "attachment; filename="+execution.getName()+".csv");
 	      response.flushBuffer();
 	    } catch (IOException ex) {
 	      throw new RuntimeException("Error while generating Report!");

### 2012-11-01 tool/src/main/java/org/testevol/domain/Version.java

@@ -1,25 +1,23 @@
 package org.testevol.domain;
 
 import java.io.BufferedReader;
-import java.io.ByteArrayOutputStream;
 import java.io.File;
 import java.io.FileInputStream;
 import java.io.FileNotFoundException;
 import java.io.FileOutputStream;
 import java.io.FileReader;
 import java.io.IOException;
-import java.io.PrintStream;
 import java.util.HashSet;
 import java.util.Properties;
 import java.util.Set;
 
 import org.apache.commons.io.FileUtils;
-import org.apache.maven.cli.MavenCli;
 import org.apache.maven.model.Model;
 import org.apache.maven.model.Plugin;
 import org.apache.maven.model.io.xpp3.MavenXpp3Reader;
 import org.codehaus.plexus.util.xml.Xpp3Dom;
 import org.testevol.engine.driver.TestCoverageDriver;
+import org.testevol.engine.util.TestevolMavenCli;
 import org.testevol.engine.util.Utils;
 import org.testevol.versioncontrol.UpdateResult;
 import org.testevol.versioncontrol.VersionControlSystem;
@@ -341,15 +339,16 @@ public class Version {
 	}
 
 	public String getConfigurationType() {
+		if (!getSourceDir().exists() || !getLibrariesDir().exists()) {
+			return "Invalid";
+		}
 		if (hasTestEvolConfig()) {
 			return "TestEvol";
 		}
 		if (isMavenProject()) {
 			return "Maven";
 		}
-		if (!getSourceDir().exists() || !getLibrariesDir().exists()) {
-			return "Invalid";
-		}
+		System.out.println(getLibrariesDir().getAbsolutePath());
 
 		return null;
 	}
@@ -423,14 +422,16 @@ public class Version {
 		File srcResources = getSrcResourcesDir();
 		File testResources = getTestResourcesDir();
 
-		MavenCli maven = new MavenCli();
-		ByteArrayOutputStream baos = new ByteArrayOutputStream();
-		PrintStream ps = new PrintStream(baos);
-		maven.doMain(new String[] { "clean", "compile", "test",
-				"dependency:copy-dependencies" }, versionDir.getAbsolutePath(),
-				ps, ps);
-
-		boolean result = baos.toString().contains("BUILD SUCCESS");
+		
+		String output;
+		try {
+			output = TestevolMavenCli.execMavenProcess(new String[] { "clean", "compile", "test",
[…]

### 2012-11-01 tool/src/main/java/org/testevol/engine/Compiler.java

@@ -238,7 +238,6 @@ public class Compiler extends Task {
             	log.log(line);
             }
         }
-
     }
     
     private String getClassName(String relativePath) throws IOException{

### 2012-11-01 tool/src/main/java/org/testevol/engine/util/TestevolMavenCli.java
new cli for maven

@@ -1,0 +1,62 @@
+package org.testevol.engine.util;
+
+import java.io.BufferedReader;
+import java.io.ByteArrayOutputStream;
+import java.io.File;
+import java.io.IOException;
+import java.io.InputStream;
+import java.io.InputStreamReader;
+import java.io.PrintStream;
+import java.io.StringWriter;
+import java.util.ArrayList;
+import java.util.HashSet;
+import java.util.List;
+
+import org.apache.commons.io.IOUtils;
+import org.apache.maven.cli.MavenCli;
+import org.testevol.domain.Version;
+
+public class TestevolMavenCli {
+
+	public static String exec(String[] goals, File workingDir) {
+		MavenCli maven = new MavenCli();
+		ByteArrayOutputStream baos = new ByteArrayOutputStream();
+		PrintStream ps = new PrintStream(baos);
+		maven.doMain(goals, workingDir.getAbsolutePath(), ps, ps);
+		return baos.toString();
+	}
+
+	public static String execMavenProcess(String[] goals, File workingDir) throws Exception {
+		List<String> args = new ArrayList<String>();
+		args.add("mvn");
+		for (String goal : goals) {
+			args.add(goal);
+		}
+
+		Process process = new ProcessBuilder(args).start();
+		process.waitFor();
+
+		String line;
+		ByteArrayOutputStream baos = new ByteArrayOutputStream();
+		if (process.exitValue() != 0) {
+			InputStreamReader isr2 = new InputStreamReader(
+					process.getErrorStream());
+			BufferedReader br2 = new BufferedReader(isr2);
+
+			while ((line = br2.readLine()) != null) {
+				IOUtils.write(line+"\n", baos);
+				
+			}
+		} else {
+			InputStream is = process.getInputStream();
+			InputStreamReader isr = new InputStreamReader(is);
+			BufferedReader br = new BufferedReader(isr);
+			while ((line = br.readLine()) != null) {
+				IOUtils.write(line+"\n", baos);
+			}
+		}
+		System.out.println(baos.toString());
+		return baos.toString();
+	}
+
+}

### 2012-11-01 tool/src/main/java/org/testevol/engine/util/TestevolMavenCli.java
fix

@@ -33,7 +33,7 @@ public class TestevolMavenCli {
 			args.add(goal);
 		}
 
-		Process process = new ProcessBuilder(args).start();
+		Process process = new ProcessBuilder(args).directory(workingDir).start();
 		process.waitFor();
 
 		String line;

### 2012-11-01 tool/src/main/java/org/testevol/domain/Version.java
new cli for maven

@@ -339,16 +339,15 @@ public class Version {
 	}
 
 	public String getConfigurationType() {
+		if (isMavenProject()) {
+			return "Maven";
+		}
 		if (!getSourceDir().exists() || !getLibrariesDir().exists()) {
 			return "Invalid";
 		}
 		if (hasTestEvolConfig()) {
 			return "TestEvol";
 		}
-		if (isMavenProject()) {
-			return "Maven";
-		}
-		System.out.println(getLibrariesDir().getAbsolutePath());
 
 		return null;
 	}

### 2012-11-02 tool/src/main/java/org/testevol/controller/LoginController.java
pseudo-real login implemented

@@ -3,11 +3,20 @@ package org.testevol.controller;
 import org.springframework.stereotype.Controller;
 import org.springframework.web.bind.annotation.RequestMapping;
 import org.springframework.web.bind.annotation.RequestMethod;
+import org.springframework.web.servlet.ModelAndView;
 
 @Controller
 @RequestMapping("/login")
 public class LoginController {
 
+	@RequestMapping(method = RequestMethod.GET)
+	public ModelAndView showLoginPage() {
+		
+		ModelAndView modelAndView = new ModelAndView();
+		modelAndView.setViewName("login");
+		return modelAndView;
+	}
+	
 	@RequestMapping(method = RequestMethod.POST)
 	public String login() {
 		return "redirect:/projects/list";

### 2012-11-02 tool/src/main/java/org/testevol/controller/ProjectController.java

@@ -6,6 +6,7 @@ import java.io.IOException;
 import java.io.InputStream;
 import java.io.PrintWriter;
 import java.io.StringWriter;
+import java.security.Principal;
 import java.util.ArrayList;
 import java.util.Collections;
 import java.util.HashMap;
@@ -41,9 +42,10 @@ import org.testevol.versioncontrol.VersionControlSystem;
 @Controller
 @RequestMapping("/projects")
 public class ProjectController {
-	
-	@Value("#{testEvolProperties.config_dir}") String configDir;
-	
+
+	@Value("#{testEvolProperties.config_dir}")
+	String configDir;
+
 	@Autowired
 	private ProjectRepository projectRepo;
 
@@ -54,246 +56,290 @@ public class ProjectController {
 		return mav;
 	}
 
-	@RequestMapping(value="list",method = RequestMethod.GET)
-	public ModelAndView list() throws Exception {
-		List<Project> projects = projectRepo.getProjects();
-		
+	@RequestMapping(value = "list", method = RequestMethod.GET)
+	public ModelAndView list(Principal principal) throws Exception {
+		List<Project> projects = projectRepo.getProjects(principal.getName());
+
 		ModelAndView mav = new ModelAndView();
 		mav.addObject("projects", projects);
 		mav.setViewName("projectList");
 		return mav;
 	}
 
-	@RequestMapping(value="names",method = RequestMethod.GET, produces="application/json")
-	public @ResponseBody List<String> getProjectNames() throws Exception {
-		return projectRepo.getProjectsNames();
+	@RequestMapping(value = "names", method = RequestMethod.GET, produces = "application/json")
+	public @ResponseBody
+	List<String> getProjectNames(Principal principal) throws Exception {
+		return projectRepo.getProjectsNames(principal.getName());
 	}
 
-	
-	@RequestMapping(value="{project}",method = RequestMethod.GET)
-	public ModelAndView getProject(@PathVariable("project") String projectName) throws Exception {
-		Project project = projectRepo.getProject(projectName);
-		
+	@RequestMapping(value = "{project}", method = RequestMethod.GET)
+	public ModelAndView getProject(@PathVariable("project") String projectName,
+			Principal principal) throws Exception {
+		Project project = projectRepo.getProject(projectName, principal.getName());
+
 		ModelAndView mav = new ModelAndView();
 		mav.addObject("project", project);
 		mav.setViewName("project");
 		return mav;
 	}
-	
-	@RequestMapping(value="{project}/execute",method = RequestMethod.POST)
[…]

### 2012-11-02 tool/src/main/java/org/testevol/domain/Project.java

@@ -12,69 +12,68 @@ public class Project {
 	private List<String> versionsToExecute;
 	private List<String> branchesToCheckout;
 	private boolean includeCoverageAnalysis;
-	
-	public boolean isIncludeCoverageAnalysis() {
-		return includeCoverageAnalysis;
-	}
 
-	public void setIncludeCoverageAnalysis(boolean includeCoverageAnalysis) {
-		this.includeCoverageAnalysis = includeCoverageAnalysis;
-	}
+	public Project() {}
 
-	public Project() {
-	}
 	
 	public Project(String name) {
-		super();
 		this.name = name;
+	}
+
+	public List<String> getBranchesToCheckout() {
+		return branchesToCheckout;
 	}
 	
 	public String getName() {
 		return name;
 	}
-
-	public void setName(String name) {
-		this.name = name;
-	}
 	
+	public RepositoryInfo getRepositoryInfo() {
+		return repositoryInfo;
+	}
+
 	public String getUrl() {
 		return repositoryInfo.getUrl();
+	}
+	
+	public VersionControlSystem getVersionControlSystem(){
+		return VersionControlSystem.getInstance(repositoryInfo);
 	}
 	
 	public List<Version> getVersionsList() {
 		return versionsList;
 	}
 
-	public void setVersionsList(List<Version> versionsList) {
-		this.versionsList = versionsList;
+	public List<String> getVersionsToExecute() {
+		return versionsToExecute;
+	}
+	
+	public boolean isIncludeCoverageAnalysis() {
+		return includeCoverageAnalysis;
 	}
 	
 	public void setBranchesToCheckout(List<String> branchesToCheckout) {
 		this.branchesToCheckout = branchesToCheckout;
 	}
-	
-	public List<String> getBranchesToCheckout() {
-		return branchesToCheckout;
-	}
 
-	public VersionControlSystem getVersionControlSystem(){
-		return VersionControlSystem.getInstance(repositoryInfo);
+	public void setIncludeCoverageAnalysis(boolean includeCoverageAnalysis) {
+		this.includeCoverageAnalysis = includeCoverageAnalysis;
+	}
+	
+	public void setName(String name) {
+		this.name = name;
 	}
 	
 	public void setRepositoryInfo(RepositoryInfo repositoryInfo) {
 		this.repositoryInfo = repositoryInfo;
 	}
 	
-	public RepositoryInfo getRepositoryInfo() {
-		return repositoryInfo;
[…]

### 2012-11-02 tool/src/main/java/org/testevol/domain/ProjectRepository.java

@@ -9,19 +9,19 @@ import org.testevol.versioncontrol.UpdateResult;
 
 public interface ProjectRepository {
 
-	public void save(Project project) throws Exception;
-	public boolean exists(String projectName);
-	public Project getProject(String projectName) throws Exception;
-	public List<Project> getProjects();
-	public List<String> getProjectsNames();
-	public void deleteProject(String projectName) throws IOException;
-	public void deleteVersion(String projectName, String version) throws Exception;
-	public UpdateResult updateRepo(String projectName, String version) throws Exception;
-	public Execution createExecution(String projectName, List<String> versionsToExecute) throws Exception;
-	public Execution getExecution(String projectName, String id) throws Exception;
-	public void saveExecution(String projectName, String id, String name, ExecutionStatus status) throws Exception;
-	public List<Execution> getExecutions(Project project) throws Exception;
-	public void deleteExecution(String projectName, String id) throws IOException;
-	public void updateVersionSettings(VersionSettings versionSettings) throws Exception;
+	public void save(Project project, String user) throws Exception;
+	public boolean exists(String projectName, String user) throws Exception;
+	public Project getProject(String projectName, String user) throws Exception;
+	public List<Project> getProjects(String user) throws Exception;
+	public List<String> getProjectsNames(String user) throws Exception;
+	public void deleteProject(String projectName, String user) throws IOException;
+	public void deleteVersion(String projectName, String version, String user) throws Exception;
+	public UpdateResult updateRepo(String projectName, String version, String user) throws Exception;
+	public Execution createExecution(String projectName, List<String> versionsToExecute, String user) throws Exception;
+	public Execution getExecution(String projectName, String id, String user) throws Exception;
+	public void saveExecution(String projectName, String id, String name, ExecutionStatus status, String user) throws Exception;
+	public List<Execution> getExecutions(Project project, String user) throws Exception;
+	public void deleteExecution(String projectName, String id, String user) throws IOException;
+	public void updateVersionSettings(VersionSettings versionSettings, String user) throws Exception;
 	
 }

### 2012-11-02 tool/src/main/java/org/testevol/infra/ProjectRepoFileSystem.java

@@ -31,32 +31,38 @@ public class ProjectRepoFileSystem implements ProjectRepository {
 
 	private static final String EXECUTION_PROPERTIES = "execution.properties";
 	private static final String EXECUTIONS_DIR = "reports";
+	
 	private File projectsDir = null;
-
+	
 	@Autowired
-	public ProjectRepoFileSystem(
-			@Value("#{testEvolProperties.projects_dir}") String dir) {
+	public ProjectRepoFileSystem(@Value("#{testEvolProperties.projects_dir}") String dir) {
 		projectsDir = new File(dir);
 		if (!projectsDir.exists()) {
 			projectsDir.mkdirs();
 		}
 
 	}
+	
+	private File getProjectsDir(String user) throws IOException{
+		File userDir = new File(projectsDir, user);
+		if(!userDir.exists()){
+			userDir.createNewFile();
+		}
+		return userDir;
+	}
 
-	public void save(Project project) throws Exception {
+	public void save(Project project, String user) throws Exception {
 		if (!project.validate()) {
 			throw new RuntimeException("Missing requried fields");
 		}
-		if (exists(project.getName())) {
+		if (exists(project.getName(), user)) {
 			throw new RuntimeException("Project already exists");
 		}
 
-		
-		
 		//TODO: implement this inside version object
 		VersionControlSystem versionControlSystem = project
 				.getVersionControlSystem();
-		File projectDir = new File(projectsDir, project.getName());
+		File projectDir = new File(getProjectsDir(user), project.getName());
 		projectDir.mkdirs();		
 		try {
 			versionControlSystem.checkout(projectDir, project.getBranchesToCheckout());
@@ -66,13 +72,13 @@ public class ProjectRepoFileSystem implements ProjectRepository {
 		}
 	}
 
-	public boolean exists(String projectName) {
-		File projectDir = new File(projectsDir, projectName);
+	public boolean exists(String projectName, String user) throws Exception {
+		File projectDir = new File(getProjectsDir(user), projectName);
 		return projectDir.exists();
 	}
 
-	public Project getProject(String projectName) throws Exception{
-		File f = new File(projectsDir,projectName);
+	public Project getProject(String projectName, String user) throws Exception{
+		File f = new File(getProjectsDir(user),projectName);
 		Project project = new Project();
 		project.setName(projectName);
 		File[] files = f.listFiles();
[…]

### 2012-11-02 tool/src/test/java/org/testevol/versioncontrol/GitImplTest.java

@@ -29,7 +29,7 @@ public class GitImplTest {
 		repositoryInfo.setUrl("git://github.com/testevol/google-gson.git");
 		
 		GitImpl git = new GitImpl(repositoryInfo);
-		Assert.assertEquals(Arrays.asList("v.1.2","v.1.1","v.1.0"),
+		Assert.assertEquals(Arrays.asList("v.1.2.2","v.1.2.1","v.1.2","v.1.1","v.1.0"),
 				git.getBranches());
 	}
 

### 2012-11-02 tool/src/main/java/org/testevol/infra/ProjectRepoFileSystem.java
creation dir bug fixed

@@ -46,7 +46,7 @@ public class ProjectRepoFileSystem implements ProjectRepository {
 	private File getProjectsDir(String user) throws IOException{
 		File userDir = new File(projectsDir, user);
 		if(!userDir.exists()){
-			userDir.createNewFile();
+			userDir.mkdirs();
 		}
 		return userDir;
 	}

### 2012-11-02 tool/src/main/java/org/testevol/controller/Ping.java
ping

@@ -1,0 +1,18 @@
+package org.testevol.controller;
+
+import org.springframework.stereotype.Controller;
+import org.springframework.web.bind.annotation.RequestMapping;
+import org.springframework.web.bind.annotation.RequestMethod;
+import org.springframework.web.bind.annotation.ResponseBody;
+
+@Controller
+@RequestMapping("/ping")
+public class Ping {
+
+	@RequestMapping(method = RequestMethod.GET, produces = "text/xml")
+	public @ResponseBody
+	String ping() {
+		return "<pingdom_http_custom_check><status>OK</status><response_time>1</response_time></pingdom_http_custom_check>";
+	}
+
+}

### 2012-11-02 tool/src/main/java/org/testevol/controller/ProjectController.java
fixed problem with session

@@ -87,6 +87,8 @@ public class ProjectController {
 	public String execute(@PathVariable("project") final String projectName,
 			final @ModelAttribute Project projectModel, final Principal principal)
 			throws Exception {
+		
+		final String username = principal.getName();
 
 		final Execution execution = projectRepo.createExecution(projectName,
 				projectModel.getVersionsToExecute(), principal.getName());
@@ -109,16 +111,16 @@ public class ProjectController {
 						!projectModel.isIncludeCoverageAnalysis());
 				try {
 					projectRepo.saveExecution(projectName, execution.getId(),
-							execution.getName(), ExecutionStatus.RUNNING, principal.getName());
+							execution.getName(), ExecutionStatus.RUNNING, username);
 					dataAnalysis.start();
 					projectRepo.saveExecution(projectName, execution.getId(),
-							execution.getName(), ExecutionStatus.SUCCESS, principal.getName());
+							execution.getName(), ExecutionStatus.SUCCESS, username);
 				} catch (Exception e) {
 					e.printStackTrace();
 					try {
 						projectRepo.saveExecution(projectName,
 								execution.getId(), execution.getName(),
-								ExecutionStatus.ERROR, principal.getName());
+								ExecutionStatus.ERROR, username);
 					} catch (Exception e1) {
 					}
 				}

### 2012-11-02 tool/src/main/java/org/testevol/infra/ProjectRepoFileSystem.java
executions folder

@@ -30,7 +30,7 @@ import org.testevol.versioncontrol.VersionControlSystem;
 public class ProjectRepoFileSystem implements ProjectRepository {
 
 	private static final String EXECUTION_PROPERTIES = "execution.properties";
-	private static final String EXECUTIONS_DIR = "reports";
+	private static final String EXECUTIONS_DIR = "executions";
 	
 	private File projectsDir = null;
 	

### 2012-11-02 icse2013demo-testevol/code/OldTestRef.java
First draft

@@ -1,0 +1,7 @@
+public void testDistance() {
+  Vector3D v1 = new Vector3D(1, -2, 3);
+  Vector3D v2 = new Vector3D(-4, 2, 0);
+  assertEquals(0.0, Vector3D.distance(Vector3D.MINUS_I, Vector3D.MINUS_I), 0);
+  assertEquals(Math.sqrt(50), Vector3D.distance(v1, v2), 1.0e-12);
+  assertEquals(v1.subtract(v2).getNorm(), Vector3D.distance(v1, v2), 1.0e-12);
+}

### 2012-11-02 icse2013demo-testevol/code/OldTestRep.java

@@ -1,0 +1,6 @@
+public void testNullField() throws Exception {
+  try {
+    new FieldAttributes(Foo.class, null);
+    fail("Field parameter can not be null");
+  } catch (NullPointerException expected) { }
+}

### 2012-11-02 icse2013demo-testevol/code/TestAdd-AeRe.java

@@ -1,0 +1,5 @@
+public void testZeroVectors() {
+  assertEquals(0, new ArrayRealVector(new double[0]).getDimension());
+  assertEquals(0, new ArrayRealVector(new double[0], true).getDimension());
+  assertEquals(0, new ArrayRealVector(new double[0], false).getDimension());
+}

### 2012-11-02 icse2013demo-testevol/code/TestAdd-Ce.java

@@ -1,0 +1,10 @@
+public void testGetMinY() {
+  TimeSeries s1 = new TimeSeries("S1");
+  assertTrue(Double.isNaN(s1.getMinY()));
+  s1.add(new Year(2008), 1.1);
+  assertEquals(1.1, s1.getMinY(), EPSILON);
+  s1.add(new Year(2009), 2.2);
+  assertEquals(1.1, s1.getMinY(), EPSILON);
+  s1.add(new Year(2002), -1.1);
+  assertEquals(-1.1, s1.getMinY(), EPSILON);
+}

### 2012-11-02 icse2013demo-testevol/code/TestAdd-P.java

@@ -1,0 +1,4 @@
+public void testFindRangeBounds() {
+  XYErrorRenderer r = new XYErrorRenderer();
+  assertNull(r.findRangeBounds(null));
+}

### 2012-11-02 icse2013demo-testevol/code/TestDel-AeRe-II.java

@@ -1,0 +1,5 @@
+public void test1900Previous() {
+  Year current = new Year(1900);
+  Year previous = (Year) current.previous();
+  assertNull(previous);
+}

### 2012-11-02 icse2013demo-testevol/code/TestDel-AeRe.java

@@ -1,0 +1,6 @@
+public void testBigDecimal() {
+  BigDecimal o1 = new BigDecimal("2.0");
+  BigDecimal o2 = new BigDecimal("2.00");
+  assertTrue(new EqualsBuilder().append(o1, o1).isEquals());
+  assertTrue(new EqualsBuilder().append(o1, o2).isEquals());
+}

### 2012-11-02 icse2013demo-testevol/code/TestDel-Ce.java

@@ -1,0 +1,3 @@
+public void testGetBuddhist() {
+  assertEquals(BuddhistChronology.getInstance(), Chronology.getBuddhist());
+}

### 2012-11-02 icse2013demo-testevol/code/TestDel-P.java

@@ -1,0 +1,5 @@
+public void testConstructorMessage(){
+  String msg = "message";
+  MatrixIndexException ex = new MatrixIndexException(msg);
+  assertEquals(msg, ex.getMessage());
+}

### 2012-11-02 icse2013demo-testevol/code/TestDel-PII.java

@@ -1,0 +1,7 @@
+public void testParameter(){
+  MatrixIndexException ex = 
+	new MatrixIndexException(INDEX_OUT_OF_RANGE, 12, 0, 5);
+  assertEquals(12, ex.getArguments()[0]);
+  assertEquals(0,  ex.getArguments()[1]);
+  assertEquals(5,  ex.getArguments()[2]);
+}

### 2012-11-02 icse2013demo-testevol/code/TestDel-PIII.java

@@ -1,0 +1,4 @@
+public void testArrayOfStrings() {
+  String[] target = {"Hello", "World"};
+  assertEquals("[\"Hello\",\"World\"]", gson.toJson(target));
+}

### 2012-11-02 icse2013demo-testevol/code/TestRef.java

@@ -1,0 +1,7 @@
+public void testDistance() {
+  Vector3D v1 = new Vector3D(1, -2, 3);
+  Vector3D v2 = new Vector3D(-4, 2, 0);
+  assertEquals(0.0,Vector3D.distance(Vector3D.MINUS_I, Vector3D.MINUS_I), 0);
+  assertEquals(FastMath.sqrt(50), Vector3D.distance(v1, v2), 1.0e-12);
+  assertEquals(v1.subtract(v2).getNorm(), Vector3D.distance(v1, v2), 1.0e-12);
+}

### 2012-11-02 icse2013demo-testevol/code/TestRep.java

@@ -1,0 +1,6 @@
+public void testNullField() throws Exception {
+  try {
+    new FieldAttributes(null);
+    fail("Field parameter can not be null");
+  } catch (NullPointerException expected) { }
+}

### 2012-11-02 icse2013demo-testevol/code/a.java

@@ -1,0 +1,8 @@
+public void testDiscardSemicolons() throws Throwable {
+   Tokenizer t = new JavaTokenizer();
+   SourceCode sourceCode = new SourceCode("1");
+   String data = "public class Foo {private int x;}";
+   Tokens tokens = new Tokens();
+   t.tokenize(sourceCode, tokens, new StringReader(data));  // Broken statement
+   assertEquals(9, tokens.size());
+}

### 2012-11-02 icse2013demo-testevol/code/b.java

@@ -1,0 +1,9 @@
+public void testDiscardSemicolons() throws Throwable {
+   Tokenizer t = new JavaTokenizer();
+   SourceCode sourceCode = new SourceCode("1");
+   String data = "public class Foo {private int x;}";
+   Tokens tokens = new Tokens();
+   sourceCode.readSource(new StringReader(data));  // Added statement
+   t.tokenize(sourceCode, tokens);                 // Modified statement
+   assertEquals(9, tokens.size());
+}

### 2012-11-02 icse2013demo-testevol/paper.tex
Minor fix

@@
 
-\usepackage[linesnumbered,boxed,ruled,nofillcomment]{algorithm2e} % add vlined,
-\usepackage{amsmath}
-%\usepackage{amsthm}
+\usepackage{times}
+\usepackage{graphicx}
+\usepackage{epsfig}
+% \usepackage{url}
+% \usepackage{hyperref}
+\usepackage[bookmarks=false]{hyperref}
+\usepackage{xspace}
+\usepackage{float}
+\usepackage{latexsym}
+\usepackage{natbib}
 \usepackage[usenames]{color}
-\usepackage[light,first]{draftcopy}
-% \usepackage{draftwatermark}
-% \usepackage[firstpage]{draftwatermark}
-\usepackage{epsfig}
-%\usepackage{fullpage}
-%\usepackage[pdftex]{graphicx}
-\usepackage{graphicx}
-%\usepackage{latex8}
+\usepackage{multirow}
 \usepackage{listings}
-\lstloadlanguages{Java}
-\usepackage{multirow}
-%\usepackage{palatino}
-\usepackage{alltt}
-\usepackage{times}
-% \usepackage{url}
-\usepackage{hyperref}
-\usepackage{cite}
-\usepackage{xspace}
-\usepackage[linesnumbered,boxed,ruled,nofillcomment]{algorithm2e} % add vlined,
-% \usepackage[small,compact]{titlesec}
+\usepackage{textcomp}
 
-\newcommand{\subparagraph}{}
-%\usepackage[compact]{titlesec}
-%\titlespacing{\section}{0pt}{1ex}{1ex}
-%\titlespacing{\subsection}{0pt}{1ex}{0ex}
-%\titlespacing{\subsubsection}{0pt}{0.5ex}{0ex}
+\bibpunct{[}{]}{,}{n}{}{}
 
-% Use the following to make modification
-% \SetWatermarkAngle{45}
-% \SetWatermarkLightness{0.8}
-% \SetWatermarkFontSize{5cm}
-% \SetWatermarkScale{1}
-% \SetWatermarkText{DRAFT -- Do not redistribute}
-
-%\renewcommand{\topfraction}{0.85}
-%\renewcommand{\textfraction}{0.1}
-%\renewcommand{\floatpagefraction}{0.75}
-%\addtolength{\textfloatsep}{-0.3in}
+\def\denseitems{
+  \itemsep1pt plus1pt minus1pt
+  \parsep0pt plus0pt
+  \parskip0pt\topsep0pt}
 
 \input{mymacros}
-\newcommand{\tool}{\textsc{TestEvol}\xspace}
+
+\makeatletter
+\newcommand\tabcaption{\def\@captype{table}\caption}
+\makeatother
+
+\renewcommand\lstlistingname{\small{Listing}}
+
+\newcommand{\lang}[1]{\texttt{\small #1}}
+\newcommand{\subject}[1]{\texttt{\small #1}}
+\newcommand{\mt}{\mathit}
+\newcommand{\trex}{\textsc{TestEvol}}
+\newcommand{\pass}{\mt{Pass}}
+\newcommand{\fail}{\mt{Fail}}
+\newcommand{\failce}{\mt{Fail}_{CE}}
+\newcommand{\failre}{\mt{Fail}_{RE}}
+\newcommand{\failae}{\mt{Fail}_{AE}}
+\newcommand{\testfunc}[2]{\mt{Test(#1, #2)}}
+\newcommand{\covfunc}[2]{\mt{Cov(#1, #2)}}
+% \newcommand{\note}[1]{{\color{red}$\blacktriangleright$ \bf #1
+%     $\blacktriangleleft$}}
+
+\newcommand{\catrep}{\textsc{TestRep}}
+\newcommand{\catref}{\textsc{TestModNotRep}}
+\newcommand{\catdelaere}{\textsc{TestDel}$_\mt{(AE|RE)}$}
+\newcommand{\catdelce}{\textsc{TestDel}$_\mt{(CE)}$}
+\newcommand{\catdelp}{\textsc{TestDel}$_\mt{(P)}$}
+\newcommand{\cataddaere}{\textsc{TestAdd}$_\mt{(AE|RE)}$}
+\newcommand{\cataddce}{\textsc{TestAdd}$_\mt{(CE)}$}
+\newcommand{\cataddp}{\textsc{TestAdd}$_\mt{(P)}$}
+
+\newcommand{\smcatrep}{{\small \textsc{TestRep}}}
+\newcommand{\smcatref}{{\small \textsc{TestRef}}}
+\newcommand{\smcatdelaere}{{\small \textsc{TestDel}$_\mt{(AE|RE)}$}}
+\newcommand{\smcatdelce}{{\small \textsc{TestDel}$_\mt{(CE)}$}}
+\newcommand{\smcatdelp}{{\small \textsc{TestDel}$_\mt{(P)}$}}
+\newcommand{\smcataddaere}{{\small \textsc{TestAdd}$_\mt{(AE|RE)}$}}
+\newcommand{\smcataddce}{{\small \textsc{TestAdd}$_\mt{(CE)}$}}
+\newcommand{\smcataddp}{{\small \textsc{TestAdd}$_\mt{(P)}$}}
+
+\lstset{ %
+upquote=true,
+basicstyle=\tiny\sffamily,
+showspaces=false,               % show spaces adding particular underscores
+  showstringspaces=false,         % underline spaces within strings
+  showtabs=false
+}
 
@@
 \displaywidowpenalty = 10000
+
+\hyphenation{Test-Evol}
+
+\newcommand{\tool}{\textsc{TestEvol}\xspace}
 
@@
 
-\title{TestEvol: A Tool for Analyzing\\Test-Suite Evolution}
+\title{TestEvol: A Tool for Analyzing Test-Suite Evolution}
 
@@
 \IEEEauthorblockA{
-College of Computing\\
+% College of Computing\\
 Georgia Institute of Technology\\
-Atlanta, USA\\
+% Atlanta, USA\\
 \{orso\}@cc.gatech.edu}
@@
 \pagestyle{empty}
+
+\note{This is a VERY rough draft that I put together by copying and
+  pasting from the FSE paper. I left some specific TODOs in, but the
+  paper really needs a major pass.}
+
+\todo{Restructure the content to make sure we comply with what is
+  requested from a demo paper: Tool-based demonstrations describe
+  novel aspects of early prototypes or mature tools. The tool
+  demonstrations must communicate clearly the following information to
+  the audience:\\
+  - the envisioned users;\\
+  - the software engineering challenge it proposes to address;\\
+  - the methodology it implies for its users; and\\
+  - the results of validation studies already conducted for mature tools, or the design of planned studies for early prototypes.}
+
+\todo{Reduce the description of the approach and extend the
+  description of the implementation. Leandro, can you add some details
+  there?}
+
+\todo{Add snapshots.}
 
@@
   investigate how test suites evolve. To tackle this problem, in this
-  paper we present a technique for studying test-suite evolution, a
-  tool that implements the technique, and an extensive empirical study
-  in which we used our technique to study many versions of six
-  real-world programs and their unit test suites. This is the first
-  study of this kind, and our results reveal several interesting
-  aspects of test-suite evolution. In particular, our findings show
-  that test repair is just one possible reason for test-suite
-  evolution, whereas most changes involve refactorings, deletions, and
-  additions of test cases.  Our results also show that test
-  modifications tend to involve complex, and hard-to-automate, changes
-  to test cases, and that existing test-repair techniques that focus
-  exclusively on assertions may have limited practical applicability.
-  More generally, our findings provide initial insight on how test
-  cases are added, removed, and modified in practice, and can guide
-  future research efforts in the area of test-suite evolution.
+  demo we present \tool, a tool that enables the systematic study of
+  test-suite evolution for Java programs and JUnit test cases. We also
+  present examples of applications of \tool\ to real-world programs
+  and their unit test suites that show the usefulness and practical
+  applicability of the tool.
 \end{abstract}
@@
 \section{Introduction}
+\label{sec:intro}
 
+Test cases form the first line of defense against the introduction of
+software faults, especially when retesting modified software.  With
+the availability of convenient testing frameworks, such as JUnit, and
+the adoption of agile development methodologies, in particular,
+writing unit test cases is an increasingly common practice nowadays.
+Developers routinely create test suites that consist of unit tests and
+that they run periodically on their code.
+
+Test suites are not static entities: they constantly evolve along with
+the application they test.  In particular, changes in the application
+can break test cases---in some cases, even a small change in the
+application code can affect a large number of tests. In general, a
+test failure on a new version of the software can either expose
+application faults or result from a problem with the test itself.  On
+observing a failure, the first task for the developer is to determine
+which of these two is the cause of the failure and, once this
+distinction is made, either fix the problem in the code or fix the
+broken~test.
+
+A broken test, if it covers a valid functionality, should ideally be
+repaired. Alternatively, if the repair is unduly complex to perform or
+if the test was designed to cover a functionality that no longer
+exists in the application, the test should be removed from the test
+suite. To illustrate with an example,
+Figure~\ref{fig:pmd-javatokenizertest} shows two versions of a unit
+test case from the test suite of \subject{PMD}, one of the programs
+used in our demo. A change in \subject{PMD}'s API broke the original
+version of the test case, which had to be fixed by adding a call to
+method \lang{SourceCode.readSource} and removing one parameter from
+the call to method \lang{Tokenizer.tokenize} (lines 6 and 7 in
+Figure~\ref{fig:pmd-javatokenizertest}(b), respectively).
+
+\begin{figure}[t]
+\lstinputlisting[language=java,
+captionpos=t,frame=tb,stepnumber=1,numbers=left,numbersep=5pt]{code/a.java}
+\vspace*{-4pt}
+\centerline{(a)}
+\lstinputlisting[language=java,
+captionpos=t,frame=tb,stepnumber=1,numbers=left,numbersep=5pt]{code/b.java}
+\vspace*{-4pt}
+\centerline{(b)}
+\vspace*{-8pt}
+\caption{Two versions of a test case from \subject{PMD}'s unit test
+  suite: (a) version~1.4, broken, and (b) version~1.6, repaired.}
+\vspace*{-12pt}
+\label{fig:pmd-javatokenizertest}
+\end{figure}
+
+Because test repair can be an expensive activity, automating it---even
+if only partially---could save a considerable amount of resources
+during maintenance. This is the motivation behind the development of
+automated test-repair techniques, such as the ones targeted at unit
+test cases~\cite{Daniel:2009, Daniel:2010, Mirzaaghaei:2012} and those
+focused on GUI (or system) test cases~\cite{Choudhary:2011,
+  Grechanik:2009, Huang:2010, Memon:2008}.
+
+We believe that, to develop effective techniques for assisting manual
+test repair, we must first understand how test suites evolve in
+practice. That is, we must understand when and how tests are created,
+removed, and modified. This is a necessary, preliminary step because
+it can (1) provide evidence that test cases do get repaired, (2)
+support the hypothesis that test repairs can be (at least partially)
+automated, and (3) suitably direct research efforts.  Without such
+understanding, we risk to develop techniques that may not be generally
+applicable and may not perform the kind of repairs that are actually
+needed in real-world software systems.
+
+To the best of our knowledge, to date there are no studies in the
+literature that investigate how unit test suites evolve. To address
+this issue, we defined a technique~\cite{pinto12} that combines
+various static- and dynamic-analysis techniques to compute the
+differences between the test suites associated with two versions of a
+program and categorize such changes along two dimensions: the static
+differences between the tests in the two test suites and the
+behavioral differences between such tests.  We implemented our
+technique in a tool, \tool, which enables a systematic study of
+test-suite evolution. \tool\ targets Java programs and JUnit test
+suites, as Java is a widely used language and JUnit is the de-facto
+standard unit-testing framework for Java.  Given two versions of a
+program and its test suite, \tool\ automatically computes differences
+in the behavior of the test suites on the two program versions,
+classifies the actual repairs performed between the versions, and
+computes the coverage attained by the tests on the two program
+versions.
+
+In this demo, we present \tool, its features and technical details,
+and show how it can be used to study how test suites evolved over the
+years for a project.  To do so, we will show examples of application
+of the tool to a set of real-world open-source software systems.
+Specifically, we will show how to use \tool\ to investigate relevant
+questions on test evolution, such as: What types of test-suite changes
+occur in practice and with what frequency? How often do test repairs
+require complex modifications of the tests? Why are tests deleted and
+added? Overall, we will show how \tool\ is a useful tool not only for
+researchers in the area of test repair (and test evolution in
+general), but also to developers and testers who want to better
+understand their software systems.
+
+\todo{Discuss \tool's availability at
+  \url{http://cheetah.cc.gt.atl.ga.us:8081/testevol/}}.
+
+\section{Our Approach for Studying Test-Suite Evolution}
+\label{sec:test-evolution}
+\subsection{Definitions and Terminology}
+\label{sec:terminology}
+
+A \textit{system} $S = (P, T)$ consists of a program $P$ and a test
+suite $T$.  A \textit{test suite} $T = \{t_1, t_2, \ldots, t_n\}$
+consists of a set of unit test cases. 
+% A unit test case $t$ is a method (or function) and it is identified
+% by its name plus the name of the class it is associated with.
+$\testfunc{P}{t}$ is a function that executes test case $t$ on program
+$P$ and returns the outcome of the test execution.  A \textit{test
+  outcome} can be of one of four types:
+
+\begin{itemize}\denseitems
+
+\item $\pass$: The execution of $P$ against $t$ succeeds.
+
+\item $\failce$: The execution of $P$ against $t$ fails because a
+  class or method accessed in $t$ does not exist in
+  $P$.\footnote{\small These failures can obviously be detected at
+    compile-time. For the sake of consistency in the discussion,
+    however, we consider such cases to be detected at runtime via
+    ``class not found'' or ``no such method'' exceptions. In fact, our
+    \tool{} tool detects such failures at runtime by executing the
+    tests compiled using the previous version of $P$ on $P$.}
+
+\item $\failre$: The execution of $P$ against $t$ fails due to an
+  uncaught runtime exception (\eg a ``null pointer'' exception).
+
+\item $\failae$: The execution of $P$ against $t$ fails due to an
+  assertion violation.
+
+\end{itemize}
+
+We use the generic term $\fail$ to refer to failures for which the
+distinction among the above three types of failures is unnecessary.
+
+$\covfunc{P}{t}$ is a function that instruments program $P$, executes
+test case $t$ on $P$, and returns the set of all statements in $P$
+covered by $t$. $\covfunc{P}{T}$ returns the cumulative coverage
+achieved on $P$ by all the tests in test suite $T$.
+
+% $\covfunc{P}{t}$ is a function that instruments program $P$, executes
+% test case $t$ on $P$, and returns the number of branches in $P$
+% covered by $t$. $\covfunc{P}{T}$ returns the cumulative coverage
+% attained on $P$ by all the tests in test suite $T$.
+
+%% Unit tests are run very frequently---often from the IDE, soon after
+%% the code is changed, or even while the code is being changed. In a
+%% typical testing process, developers may run the test suite after
+%% editing the code. In the run, some tests may fail, whereas others
+%% would pass. The developer would want to fix the broken tests online to
+%% ensure that all tests pass.
+
+Given a system $S = (P, T)$, a modified version of $S$, $S'=(P', T')$,
+and a test case $t$ in $T \cup T'$, there are three possible scenarios
+to consider: (1) $t$ exists in $T$ and $T'$, (2) $t$ exists in $T$ but
+not $T'$ (\ie $t$ was removed from the test suite), and (3) $t$ exists
+in $T'$ but not in $T$ (\ie $t$ was added to the test suite). These
+scenarios can be further classified based on the behavior of $t$ in
+$S$ and $S'$, as summarized in Figure~\ref{fig:study-design} and
+discussed in the rest of this section.
+
+\subsection{Test Modifications}
+\label{sec:test-mod}
+
+Figure~\ref{fig:study-design}(a) illustrates the scenario in which $t$
+is present in the test suites for both the old and the new versions of
+the system. To study different cases, we consider whether $t$ is
+modified (to $t'$) and, if so, whether the behaviors of $t$ and $t'$
+differ. (We have not considered the cases in which $t$ is not modified
+because they are irrelevant for studying test evolution.)  For
+\textit{behavioral differences}, there are two cases, shown in the two
+rows of the table: either $t$ fails on $P'$ and $t'$ passes on $P'$ or
+both $t$ and $t'$ pass on $P'$.
+
+\begin{figure}[t]
+\centering
+\small
+\tabcolsep=3pt
+\textbf{(a) Test $t$ exists in $S$ and $S'$ and is modified}
+\\ [2pt]
+\begin{tabular}{|l||l|}
+\hline
+%\multicolumn{1}{|c||}{} & \multicolumn{1}{|c}{} &
+%\multicolumn{1}{|c|}{$t$ is not} \\
+%\multicolumn{1}{|c||}{} & \multicolumn{1}{|c|}{$t$ is modified}\\
+%\hline \hline
+$\testfunc{P'}{t} = \fail \; \wedge$ &
+$t$ is repaired \\
+$\testfunc{P'}{t'} = \pass$ &
+\multicolumn{1}{r|}{\scriptsize [\catrep{}]}\\
+\hline
+\multirow{3}{28mm}{$\testfunc{P'}{t} = \pass \; \wedge \testfunc{P'}{t'} = \pass$} &
+$t$ is refactored, updated to test a different \\
+& scenario, or is made more/less discriminating \\
+& \multicolumn{1}{r|}{\scriptsize [\catref{}]} \\
+\hline
+\end{tabular}
+\\ [8pt]
+%
+\textbf{(b) Test $t$ is removed in $S'$}
+\\ [2pt]
+\begin{tabular}{|l||l|}
+\hline
+\multirow{2}{*}{$\testfunc{P'}{t} = \failre \, | \, \failae$} &
+$t$ is too difficult to fix \\
+& \multicolumn{1}{r|}{\scriptsize [\catdelaere{}]} \\
+\hline
+\multirow{2}{*}{$\testfunc{P'}{t} = \failce$} & $t$ is obsolete or is
+too difficult to fix \\
+& \multicolumn{1}{r|}{\scriptsize [\catdelce{}]} \\
+\hline
+\multirow{2}{*}{$\testfunc{P'}{t} = \pass$} & $t$ is redundant \\
+& \multicolumn{1}{r|}{\scriptsize [\catdelp{}]} \\
+\hline 
+\end{tabular}
+\\ [8pt]
+%
+\textbf{(c) Test $t'$ is added in $S'$}
+\\ [2pt]
+\begin{tabular}{|l||l|}
+  \hline
+  \multirow{2}{*}{$\testfunc{P}{t'} = \failre \, | \, \failae$} &
+  $t'$ is added to validate a bug fix \\
+  & \multicolumn{1}{r|}{\scriptsize [\cataddaere{}]} \\
+  \hline
+  \multirow{3}{*}{$\testfunc{P}{t'} = \failce$} &
+  $t'$ is added to test a new functionality \\
+  & or a code refactoring \\
+  & \multicolumn{1}{r|}{\scriptsize [\cataddce{}]} \\
+  \hline
+  \multirow{3}{*}{$\testfunc{P}{t'} = \pass$} &
+  %% TODO: Check: $t'$ is added to test a new functionality \\
+  $t'$ is added to test an existing feature\\
+  & or for coverage-based augmentation \\
+  & \multicolumn{1}{r|}{\scriptsize [\cataddp{}]} \\
+  \hline
+\end{tabular}
+\caption{Scenarios considered in our investigation. Given two system
+  versions $S = (P, T)$ and $S' = (P', T')$, the three scenarios are:
+  (a) $t$ exists in $T$ and $T'$ and is modified, (b) $t$ exists in
+  $T$ but not in $T'$, (c) $t'$ exists in $T'$ but not in $T$.}
+\vspace*{-5pt}
+\label{fig:study-design}
+\end{figure}
+
+\subsubsection{Category \catrep{}: Repaired Tests}
+\label{sec:category-rep}
+
+The \catrep{} category corresponds to the case where $t$ is repaired
+so that, after the modifications, it passes on $P'.$ As discussed in
+the Introduction, Figure~\ref{fig:pmd-javatokenizertest} shows an
+example of such a test repair. The code fragments in
+Listings~\ref{c1-old} and~\ref{c1-new} present another example of
+repair that involves a simpler code modification than the one in
+Figure~\ref{fig:pmd-javatokenizertest}. The example is taken from
+\subject{Gson}, one of the programs used in our demo, and involves a
+test case from \subject{Gson} version~2.0 that was fixed in the
+subsequent version~2.1. Test \lang{testNullField} had to be fixed
+because constructor \lang{FieldAttributes(Class<?> declClazz, Field
+  f)} from version~2.0 was modified in version~2.1 to take only one
+parameter (of type \lang{Field}).
+%% was no longer available on version 2.1. In the new version of the
+%% \lang{FieldAttributes} class, the constructor receives only one
+%% parameter of type \lang{Field}.
+
+\vspace*{-10pt}
+\lstinputlisting[language=java,label=c1-old,caption=\small{Unit test
+  for class FieldAttributes} (Gson v2.0),
+captionpos=t,frame=tb]{code/OldTestRep.java}
+
+\vspace*{-5pt}
+\lstinputlisting[language=java,label=c1-new,caption=\small{Unit test
+  for class FieldAttributes} (Gson v2.1),
+captionpos=t,belowcaptionskip=4pt,frame=tb]{code/TestRep.java}
+
+For this category, we wish to study the types of modifications that
+are made to $t$. A test repair may involve changing the sequence of
+method calls, assertions, data values, or control flow. Based on our
+experience, for \textit{method-call sequence changes}, we consider
+five types of modifications:
+
+\begin{enumerate}
+\denseitems
+
+\item \textit{Method call added}: a new method call is added.
+
+\item \textit{Method call deleted}: an existing method call is
+  removed.
+
+\item \textit{Method parameter added}: a method call is modified such
+  that new parameters are added.
+
+\item \textit{Method parameter deleted}: a method call is modified
+  such that existing parameters are deleted.
+
+\item \textit{Method parameter modified}: a method call is modified
+  via changes in the values of its actual parameters.
+
+\end{enumerate}
+
+A test repair may involve multiple such changes. For example, the
+repair shown in Figure~\ref{fig:pmd-javatokenizertest} involves the
+addition of a method call~(in~line~6) and the deletion of a method
+parameter (in line~7). The repair illustrated in Listings~\ref{c1-old}
+and~\ref{c1-new} also involves the deletion of a method parameter.
+%
+For \textit{assertion changes}, we consider cases in which an
+assertion is added, an assertion is deleted, the expected value of an
+assertion is modified, or the assertion is modified but the expected
+value is unchanged.
+%
+Finally, we currently group together \textit{data-value changes} and
+\textit{control-flow changes}.
+
+The rationale underlying our classification scheme is that different
+classes of changes may require different types of repair analyses.
+Although this is not necessarily the case, at least the search
+strategy for candidate repairs would differ for the different
+categories of changes. Consider the case of method-parameter deletion,
+for instance, for which one could attempt a repair by simply deleting
+some of the actual parameters. Whether this repair would work depends
+on the situation. For the code in
+Figure~\ref{fig:pmd-javatokenizertest}, for example, it would not work
+because the deletion of one of the parameters in the call to
+\lang{tokenize()} is insufficient by itself to fix the test---a new
+method call (to \lang{readSource()}) has to be added as well for the
+test to work correctly.  Similarly, for the case of method-parameter
+addition, one could conceivably attempt straightforward fixes by
+constructing equivalence classes for the new parameters and selecting
+a value from each equivalence class (\eg positive, negative, and zero
+values for an integer parameter). In our study, we found cases where
+such an approach would in fact repair broken tests. In this case too,
+however, such a solution is in general not enough.
+
+\subsubsection{Category \catref{}: Refactored Tests}
+\label{sec:category-c2}
+
+The \catref{} category captures scenarios in which a test $t$ is
+modified in $S'$ even though $t$ passes on $P'$.
+Listings~\ref{c2-old} and~\ref{c2-new} show an example of one such
+change from \subject{Commons Math}. Unit test \lang{testDistance} was
+refactored to invoke method \lang{sqrt()} in class \lang{FastMath}, a
+newly added class in the new release, instead of the same method in
+\lang{java.lang.Math}.  There are different reasons why changes in
+this category might occur.
+
+\vspace{-8pt}
+\lstinputlisting[language=java,label=c2-old,caption=\small{Unit test
+  from class Vector3DTest} (Commons Math v2.1),
+captionpos=t,frame=tb]{code/OldTestRef.java}
+
+\vspace{-8pt}
+\lstinputlisting[language=java,label=c2-new,caption=\small{Unit test
+  from class Vector3DTest} (Commons Math v2.2),
+captionpos=t,frame=tb]{code/TestRef.java}
+
+\subsection{Test Deletions}
+\label{sec:test-ref}
+
+Figure~\ref{fig:study-design}(b) illustrates the scenario in which a
+test $t$ is deleted. To study the reasons for this, we examine the
+behavior of $t$ on the new program version $P'$ and consider three
+types of behaviors.
+
+\subsubsection{Category \catdelaere{}: Hard-To-Fix Tests}
+\label{sec:category-delaere}
+
+%%COMMENT PLEASE READ ME: I guess here we should focus more
+%%in the cases that tests are removed because they have become
+%%obsolete. Actually, in the examples I was not able to find one
+%%case in which it was removed because it was too difficult to
+%% be fixed. It was always obsolete tests.
+
+This category includes tests that fail on $P'$ with a runtime
+exception or an assertion violation. These may be instances where the
+tests should have been fixed, as the functionality that they test in
+$P$ still exists in $P'$, but the tests were discarded instead. One
+plausible hypothesis is that tests in this category involve repairs of
+undue complexity, for which the investigation of new repair techniques
+to aid the developer might be particularly useful.  We performed a
+preliminary investigation of this hypothesis by manually examining ten
+randomly selected tests in this category and found that all the
+examined tests were in fact obsolete.
+
+\subsubsection{Category \catdelce: Obsolete Tests}
+\label{sec:category-delce}
+
+A test that fails with a compilation error on the new program version
+is obsolete because of API changes. Listing~\ref{c4-example}
+illustrates a test in this category taken from \subject{JodaTime}.
+This test was deleted because the tested method
+\lang{Chronology.getBuddhist()} was removed in the subsequent version
+of \subject{JodaTime}.
+
+% \vspace{-4pt}
+\lstinputlisting[language=java,label=c4-example,caption=\small{Unit
+  test from class TestChronology} (JodaTime v2.0),frame=tb]
+{code/TestDel-Ce.java}
+%This method was
+%already marked as deprecated in the previous version.
+
+Although for this category of deletion too, one could postulate that
+the tests were removed because they were too difficult to fix, we
+believe this not to be the case in most practical occurrences.
+Instead, the more likely explanation is that the tests were removed
+simply because the tested methods were no longer present. Also in this
+case, we investigated our hypothesis by manually examining ten
+randomly selected cases. Indeed, our manual investigation confirmed
+that, for the cases we analyzed, the tested functionality was either
+removed or provided through alternative methods, which requires the
+development of new tests rather than fixes to the existing ones.
+
+\subsubsection{Category \catdelp: Redundant Tests}
+\label{sec:category-delp}
+
+This category includes tests that are removed even though they pass on
+$P'$.  Listing~\ref{c5-example} illustrates an example of one such
+test, taken from \subject{Commons Lang}. In the new version, this test
+was replaced by a more sophisticated one, shown in
+Listing~\ref{c5.2-example}.
+
+\begin{figure}[h]
+\lstinputlisting[language=java,label=c5-example,caption=\small{Unit
+  test from class MatrixIndexExceptionTest} (Commons Lang
+v2.1),frame=tb] {code/TestDel-P.java}
 \vspace{4pt}
-The rest of the paper is organized as follows.
+\end{figure}
 
-\section{Conclusion and future work}
-\label{sec:concl-future-work}
+\lstinputlisting[language=java,label=c5.2-example,caption=\small{Unit
+  test implemented to replace the removed one} (Commons Lang
+v2.2),frame=tb] {code/TestDel-PII.java}
 
-\section*{Acknowledgments}
+\subsection{Test Additions}
+\label{sec:test-add}
 
-This work was supported in part by NSF awards CCF-0916605 and
-CCF-0964647 to Georgia Tech, and by funding from IBM Research and
-Microsoft Research.
+Figure~\ref{fig:study-design}(c) illustrates the cases of test-suite
+augmentation, where a new test $t'$ is added to the test suite. The
+behavior of $t'$ on the old program can indicate the reason why it may
+have been added.
+
+\subsubsection{Category \cataddaere: Bug-Fix Tests}
+\label{sec:category-addaere}
+
+This category includes added tests that fail on $P$ with a runtime
+exception or an assertion violation. In this case, the functionality
+that the added test $t'$ was designed to test exists in $P$ but is not
+working as expected (most likely because of a fault). The program
+modifications between $P$ and $P'$ would ostensibly have been made to
+fix the fault, which causes $t'$ to pass on $P'$. Thus, $t'$ is added
+to the test suite to validate the bug fix. Listing~\ref{c6-example}
+illustrates a test that fits this profile, as it was added to
+\subject{Commons Math} version 2.1 to validate a bug fix ({\small
+  \url{https://issues.apache.org/jira/browse/MATH-391}}). In the
+previous version of \lang{ArrayRealVector}, the creation of a
+zero-length vector results in a runtime exception.
+
+% \begin{figure}[h]
+\lstinputlisting[language=java,label=c6-example,caption=\small{\mbox{Unit
+  test from class ArrayRealVectorTest (Commons Math v2.2)}},
+captionpos=t,frame=tb]{code/TestAdd-AeRe.java}
+% \end{figure}
+
+\subsubsection{Category \cataddce: New-Features Tests}
+\label{sec:category-addce}
+
+The added tests in this category fail on $P$ with a compilation error,
+which indicates that the API accessed by the tests does not exist in
+$P$. Thus, the added test $t'$ is created to test new code in $P'$,
+where the code could have been added as part of a refactoring or, more
+likely, to add new functionality.  Listing~\ref{c7-example}
+illustrates a test from \subject{JFreeChart} that covers a new
+functionality: method \lang{getMinY()} did not exist in previous
+versions of class \lang{TimeSeries}.
+
+\lstinputlisting[language=java,label=c7-example,caption=\small{Unit
+  test from class TimeSeriesTests} (JFreeChart v1.0.14),
+captionpos=t,frame=tb]{code/TestAdd-Ce.java}
+
+\subsubsection{Category \cataddp: Coverage-Augmentation Tests}
+\label{sec:category-addp}
+
+This category considers cases where the added test $t'$ passes on
+$P$. Clearly, $t'$ would have been a valid test in the old system as
+well. One would expect that the addition of $t'$ increases program
+coverage (\ie $\covfunc{P'}{T'} \supset \covfunc{P'}{T' -
+  \{t'\}}$). Moreover, if $t'$ covers different statements in $P$ and
+$P'$ (assuming that there is a way of matching statements between $P$
+and $P'$), the plausible explanation is that $t'$ was added to test
+the changes made between $P$ and $P'$. However, if $t'$ covers the
+same statements in both program versions, it would have been added
+purely to increase code coverage (and not to test any added or
+modified code).  Listing~\ref{c8-example} illustrates an added test
+case that increases code coverage: the new test method
+\lang{testFindRangeBounds} covers the case where the parameter of
+method \lang{findRangeBounds()} is null.
+
+\lstinputlisting[language=java,label=c8-example,caption=\small{Unit test
+from class XYErrorRendererTests} (JFreeChart v1.0.14),frame=tb]
+{code/TestAdd-P.java}
+
+\section{Implementation of \tool}
+\label{sec:implementation}
+
+\todo{Add the discussion of clone analysis.}
+
+\todo{In general, add more details.}
+
+\todo{Discuss the availability of the tool.}
+
+We implemented our approach for studying test suite evolution in a
+tool, called \tool, which facilitates a systematic study of test-suite
+evolution for Java programs and JUnit test suites.  \tool\ analyzes a
+sequence of versions of a software system, where each version consists
+of application code and test code. The versions can be actual releases
+or internal builds.  \tool\ consists of five components, as
+illustrated in the architecture diagram shown in
+Figure~\ref{fig:trex}.
+
+The \emph{compiler} component builds each system version and creates
+two jar files, one containing the application classes and the other
+containing the test classes.
+%
+The \emph{test-execution engine} analyzes each pair of system versions
+$(S, S')$, where $S = (P, T)$ and $S' = (P', T')$.  First, it executes
+$T$ on program $P$ and $T'$ on program $P'$ (\ie it runs the tests on
+the respective program versions).  Then, it executes $T'$ on $P$ and
+$T$ on $P'$. For each execution, it records the test outcome: $\pass,
+\failce, \failae, or \failre$.
+%
+The \emph{differencing component} compares $T$ and $T'$ to identify
+modified, deleted, and added tests. This component is implemented
+using the \textsc{wala} analysis infrastructure for Java ({\small
+  \url{wala.sourceforge.net}}).
+
+The test outcomes, collected by the test-execution engine, and the
+test-suite changes, computed by the differencing component, are then
+passed to the \emph{test classifier}, which analyzes the information
+about test outcomes and test updates to classify each update into one
+of the eight test-evolution categories presented in
+Section~\ref{sec:test-evolution}.  For each pair of broken test case
+and its repaired version, the test classifier also compares the test
+cases to identify the types of repair changes---different types of
+method-sequence changes and assertion changes---as discussed in
+Section~\ref{sec:category-rep}; this analysis is also implemented
+using \textsc{wala}.
+
+\tool\ performs a further step for the test cases in categories
+\catdelp{}and \cataddp{}. For these tests, the test classifier
+leverages the \emph{coverage analyzer} to compute the branch coverage
+achieved by each test; this facilitates the investigation of whether
+the deleted or added tests cause any variations in the coverage
+attained by the new test suite.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\columnwidth]{architecture.png}
+        \vspace*{-16pt}
+	\caption{High-level architecture of \tool.}
+        \vspace*{-8pt}
+	\label{fig:trex}
+\end{figure}
+
+\vspace*{-8pt}
+\section{Conclusion}
+\label{sec:summary}
+
+Test suites evolve throughout their lifetime and change together with
+the applications they are testing. Modifying existing test cases
+manually to adapt them to an evolving system, however, can be
+extremely time consuming, especially for large test suites, which has
+motivated the recent development of automated test-repair techniques.
+To support the development of more effective repair techniques, we
+developed \tool, a tool for systematic investigation of test-suite
+evolution that can provide its users with a thorough understanding of
+how test cases evolve in practice. In this demo we present \tool, its
+main features, and its technical characteristics. We also demonstrate
+how \tool\ can be run on real-world software systems and produce a
+wealth of useful information, such as the types of test-suite changes
+that occur in practice and their frequency and why tests are deleted
+and added.  Overall, we show how \tool\ is a useful tool not only for
+researchers in the area of test repair, and test evolution in general,
+but also to developers and testers who want to better understand their
+software systems.
+
+% \section*{Acknowledgments}
+
+% This work was supported in part by NSF awards CCF-0916605 and
+% CCF-0964647 to Georgia Tech, and by funding from IBM Research and
+% Microsoft Research.
 

### 2012-11-02 icse2013demo-testevol/paper.tex
Revised abstract

@@
 \documentclass[conference]{IEEEtran}
-\synctex=1
+%\synctex=1
 
@@
 \usepackage[bookmarks=false]{hyperref}
-\usepackage{xspace}
-\usepackage{float}
+\usepackage{xspace}\usepackage{float}
 \usepackage{latexsym}
@@
 
-\author{\IEEEauthorblockN{XXX}
+\author{
+\IEEEauthorblockN{Leandro Sales Pinto}
 \IEEEauthorblockA{
-% College of Computing\\
-Georgia Institute of Technology\\
-% Atlanta, USA\\
-\{orso\}@cc.gatech.edu}
+Politecnico di Milano \\
+pinto@elet.polimi.it}
+\and
+\IEEEauthorblockN{Saurabh Sinha}
+\IEEEauthorblockA{
+IBM Research -- India \\
+saurabhsinha@in.ibm.com}
+\and
+\IEEEauthorblockN{Alessandro Orso}
+\IEEEauthorblockA{
+Georgia Institute of Technology \\
+orso@cc.gatech.edu}
 }
@@
 
-\note{This is a VERY rough draft that I put together by copying and
-  pasting from the FSE paper. I left some specific TODOs in, but the
-  paper really needs a major pass.}
-
-\todo{Restructure the content to make sure we comply with what is
-  requested from a demo paper: Tool-based demonstrations describe
-  novel aspects of early prototypes or mature tools. The tool
-  demonstrations must communicate clearly the following information to
-  the audience:\\
-  - the envisioned users;\\
-  - the software engineering challenge it proposes to address;\\
-  - the methodology it implies for its users; and\\
-  - the results of validation studies already conducted for mature tools, or the design of planned studies for early prototypes.}
-
-\todo{Reduce the description of the approach and extend the
-  description of the implementation. Leandro, can you add some details
-  there?}
-
-\todo{Add snapshots.}
+% \note{This is a VERY rough draft that I put together by copying and
+%   pasting from the FSE paper. I left some specific TODOs in, but the
+%   paper really needs a major pass.}
+% \todo{Restructure the content to make sure we comply with what is
+%   requested from a demo paper: Tool-based demonstrations describe
+%   novel aspects of early prototypes or mature tools. The tool
+%   demonstrations must communicate clearly the following information to
+%   the audience:\\
+%   - the envisioned users;\\
+%   - the software engineering challenge it proposes to address;\\
+%   - the methodology it implies for its users; and\\
+%   - the results of validation studies already conducted for mature tools, or the design of planned studies for early prototypes.}
+% \todo{Reduce the description of the approach and extend the
+%   description of the implementation. Leandro, can you add some details
+%   there?}
+% \todo{Add snapshots.}
 
@@
   evolution---test cases cease to work because of changes in the code
-  and must be suitably repaired. Repairing existing test cases
-  manually, however, can be extremely time consuming, especially for
-  large test suites, which has motivated the recent development of
-  automated test-repair techniques. We believe that, for developing
-  effective repair techniques that are applicable in real-world
-  scenarios, a fundamental prerequisite is a thorough understanding of
-  how test cases evolve in practice. Without such knowledge, we risk
-  to develop techniques that may work well for only a small number of
-  tests or, worse, that may not work at all in most realistic cases.
-  Unfortunately, to date there are no studies in the literature that
-  investigate how test suites evolve. To tackle this problem, in this
-  demo we present \tool, a tool that enables the systematic study of
-  test-suite evolution for Java programs and JUnit test cases. We also
-  present examples of applications of \tool\ to real-world programs
-  and their unit test suites that show the usefulness and practical
-  applicability of the tool.
+  and must be suitably repaired. There are several reasons why it is
+  important to achieve a thorough understanding of how test cases
+  evolve in practice. In particular, researchers who develop automated
+  test-repair techniques---an increasingly active research area---can
+  use such understanding to develop more effective repair techniques
+  that are applicable in real-world scenarios. More generally,
+  analyzing test-suite evolution can help testers better understand
+  how test cases are modified during maintenance and improve the test
+  evolution process, an extremely time consuming activity for any non
+  trivial test suite.  Unfortunately, there are no existing tools that
+  facilitate investigation of test-suite evolution. To tackle this
+  problem, we developed \tool, a tool that enables the systematic
+  study of test-suite evolution for Java programs and JUnit test
+  cases.  This demo presents \tool and demonstrates its usefulness and
+  practical applicability by showing how \tool\ can be used on
+  real-world software and unit test suites.
 \end{abstract}
@@
 
-Test cases form the first line of defense against the introduction of
-software faults, especially when retesting modified software.  With
-the availability of convenient testing frameworks, such as JUnit, and
-the adoption of agile development methodologies, in particular,
-writing unit test cases is an increasingly common practice nowadays.
-Developers routinely create test suites that consist of unit tests and
-that they run periodically on their code.
-
 Test suites are not static entities: they constantly evolve along with
-the application they test.  In particular, changes in the application
-can break test cases---in some cases, even a small change in the
-application code can affect a large number of tests. In general, a
-test failure on a new version of the software can either expose
-application faults or result from a problem with the test itself.  On
-observing a failure, the first task for the developer is to determine
-which of these two is the cause of the failure and, once this
-distinction is made, either fix the problem in the code or fix the
-broken~test.
+the application they test. For instance, new tests can be added to
+test new functionality and existing tests can be refactored, repaired,
+or deleted.  In particular, changes in the application can break test
+cases---in some cases, even a small change in the application code can
+affect a large number of tests.
 
@@
 Figure~\ref{fig:pmd-javatokenizertest} shows two versions of a unit
-test case from the test suite of \subject{PMD}, one of the programs
-used in our demo. A change in \subject{PMD}'s API broke the original
-version of the test case, which had to be fixed by adding a call to
-method \lang{SourceCode.readSource} and removing one parameter from
-the call to method \lang{Tokenizer.tokenize} (lines 6 and 7 in
+test case from the test suite of \subject{PMD}, one of the programs we
+analyzed in our previous work~\cite{pinto12}. A change in
+\subject{PMD}'s API broke the original version of the test case, which
+had to be fixed by adding a call to method
+\lang{SourceCode.readSource} and removing one parameter from the call
+to method \lang{Tokenizer.tokenize} (lines 6 and 7 in
 Figure~\ref{fig:pmd-javatokenizertest}(b), respectively).
@@
 differences between the tests in the two test suites and the
-behavioral differences between such tests.  We implemented our
-technique in a tool, \tool, which enables a systematic study of
-test-suite evolution. \tool\ targets Java programs and JUnit test
-suites, as Java is a widely used language and JUnit is the de-facto
-standard unit-testing framework for Java.  Given two versions of a
-program and its test suite, \tool\ automatically computes differences
-in the behavior of the test suites on the two program versions,
-classifies the actual repairs performed between the versions, and
-computes the coverage attained by the tests on the two program
-versions.
+behavioral differences between such tests.
+
+We implemented our technique in a tool, \tool, which enables a
+systematic study of test-suite evolution. \tool\ targets Java programs
+and JUnit test suites, as Java is a widely used language and JUnit is
+the de-facto standard unit-testing framework for Java.  Given two
+versions of a program and its test suite, \tool\ automatically
+computes differences in the behavior of the test suites on the two
+program versions, classifies the actual repairs performed between the
+versions, and computes the coverage attained by the tests on the two
+program versions.
 
@@
 
-\section{Our Approach for Studying Test-Suite Evolution}
+\section{Studying Test-Suite Evolution}
 \label{sec:test-evolution}
+
 \subsection{Definitions and Terminology}
@@
 \centering
-\small
+\footnotesize
 \tabcolsep=3pt
@@
 
-\subsubsection{Category \catrep{}: Repaired Tests}
+\subsubsection{Category \catrep{} (Repaired Tests)}
 \label{sec:category-rep}
@@
 the Introduction, Figure~\ref{fig:pmd-javatokenizertest} shows an
-example of such a test repair. The code fragments in
-Listings~\ref{c1-old} and~\ref{c1-new} present another example of
-repair that involves a simpler code modification than the one in
-Figure~\ref{fig:pmd-javatokenizertest}. The example is taken from
-\subject{Gson}, one of the programs used in our demo, and involves a
-test case from \subject{Gson} version~2.0 that was fixed in the
-subsequent version~2.1. Test \lang{testNullField} had to be fixed
-because constructor \lang{FieldAttributes(Class<?> declClazz, Field
-  f)} from version~2.0 was modified in version~2.1 to take only one
-parameter (of type \lang{Field}).
-%% was no longer available on version 2.1. In the new version of the
-%% \lang{FieldAttributes} class, the constructor receives only one
-%% parameter of type \lang{Field}.
+example of such a test repair.
 
-\vspace*{-10pt}
-\lstinputlisting[language=java,label=c1-old,caption=\small{Unit test
-  for class FieldAttributes} (Gson v2.0),
-captionpos=t,frame=tb]{code/OldTestRep.java}
+%% The code fragments in Listings~\ref{c1-old} and~\ref{c1-new} present
+%% another example of repair that involves a simpler code modification
+%% than the one in Figure~\ref{fig:pmd-javatokenizertest}. The example is
+%% taken from \subject{Gson}, one of the programs used in our demo, and
+%% involves a test case from \subject{Gson} version~2.0 that was fixed in
+%% the subsequent version~2.1. Test \lang{testNullField} had to be fixed
+%% because constructor \lang{FieldAttributes(Class<?> declClazz, Field
+%%   f)} from version~2.0 was modified in version~2.1 to take only one
+%% parameter (of type \lang{Field}).
+%% %% was no longer available on version 2.1. In the new version of the
+%% %% \lang{FieldAttributes} class, the constructor receives only one
+%% %% parameter of type \lang{Field}.
 
-\vspace*{-5pt}
-\lstinputlisting[language=java,label=c1-new,caption=\small{Unit test
-  for class FieldAttributes} (Gson v2.1),
-captionpos=t,belowcaptionskip=4pt,frame=tb]{code/TestRep.java}
+%% \vspace*{-10pt}
+%% \lstinputlisting[language=java,label=c1-old,caption=\small{Unit test
+%%   for class FieldAttributes} (Gson v2.0),
+%% captionpos=t,frame=tb]{code/OldTestRep.java}
+
+%% \vspace*{-5pt}
+%% \lstinputlisting[language=java,label=c1-new,caption=\small{Unit test
+%%   for class FieldAttributes} (Gson v2.1),
+%% captionpos=t,belowcaptionskip=4pt,frame=tb]{code/TestRep.java}
 
@@
 repair shown in Figure~\ref{fig:pmd-javatokenizertest} involves the
-addition of a method call~(in~line~6) and the deletion of a method
-parameter (in line~7). The repair illustrated in Listings~\ref{c1-old}
-and~\ref{c1-new} also involves the deletion of a method parameter.
+addition of a method call (line~6) and the deletion of a method
+parameter (line~7).
+%% The repair illustrated in Listings~\ref{c1-old} and~\ref{c1-new} also
+%% involves the deletion of a method parameter.
 %
@@
 method call (to \lang{readSource()}) has to be added as well for the
-test to work correctly.  Similarly, for the case of method-parameter
-addition, one could conceivably attempt straightforward fixes by
-constructing equivalence classes for the new parameters and selecting
-a value from each equivalence class (\eg positive, negative, and zero
-values for an integer parameter). In our study, we found cases where
-such an approach would in fact repair broken tests. In this case too,
-however, such a solution is in general not enough.
+test to work correctly.
+%% Similarly, for the case of method-parameter addition, one could
+%% conceivably attempt straightforward fixes by constructing equivalence
+%% classes for the new parameters and selecting a value from each
+%% equivalence class (\eg positive, negative, and zero values for an
+%% integer parameter).  In our study, we found cases where such an
+%% approach would in fact repair broken tests. In this case too, however,
+%% such a solution is in general not enough.
 
-\subsubsection{Category \catref{}: Refactored Tests}
+\subsubsection{Category \catref{} (Refactored Tests)}
 \label{sec:category-c2}
@@
 modified in $S'$ even though $t$ passes on $P'$.
-Listings~\ref{c2-old} and~\ref{c2-new} show an example of one such
-change from \subject{Commons Math}. Unit test \lang{testDistance} was
-refactored to invoke method \lang{sqrt()} in class \lang{FastMath}, a
-newly added class in the new release, instead of the same method in
-\lang{java.lang.Math}.  There are different reasons why changes in
-this category might occur.
+%% Listings~\ref{c2-old} and~\ref{c2-new} show an example of one such
+%% change from \subject{Commons Math}. Unit test \lang{testDistance} was
+%% refactored to invoke method \lang{sqrt()} in class \lang{FastMath}, a
+%% newly added class in the new release, instead of the same method in
+%% \lang{java.lang.Math}.
 
-\vspace{-8pt}
-\lstinputlisting[language=java,label=c2-old,caption=\small{Unit test
-  from class Vector3DTest} (Commons Math v2.1),
-captionpos=t,frame=tb]{code/OldTestRef.java}
+%% \vspace{-5pt}
+%% \lstinputlisting[language=java,label=c2-old,caption=\small{Unit test
+%%   from class Vector3DTest} (Commons Math v2.1),
+%% captionpos=t,frame=tb]{code/OldTestRef.java}
 
-\vspace{-8pt}
-\lstinputlisting[language=java,label=c2-new,caption=\small{Unit test
-  from class Vector3DTest} (Commons Math v2.2),
-captionpos=t,frame=tb]{code/TestRef.java}
+%% \vspace{-5pt}
+%% \lstinputlisting[language=java,label=c2-new,caption=\small{Unit test
+%%   from class Vector3DTest} (Commons Math v2.2),
+%% captionpos=t,frame=tb]{code/TestRef.java}
 
@@
 
-\subsubsection{Category \catdelaere{}: Hard-To-Fix Tests}
+\subsubsection{Category \catdelaere{} (Hard-To-Fix Tests)}
 \label{sec:category-delaere}
@@
 undue complexity, for which the investigation of new repair techniques
-to aid the developer might be particularly useful.  We performed a
-preliminary investigation of this hypothesis by manually examining ten
-randomly selected tests in this category and found that all the
-examined tests were in fact obsolete.
+to aid the developer might be particularly useful.
+%% We performed a preliminary investigation of this hypothesis by
+%% manually examining ten randomly selected tests in this category and
+%% found that all the examined tests were in fact obsolete.
 
-\subsubsection{Category \catdelce: Obsolete Tests}
+\subsubsection{Category \catdelce (Obsolete Tests)}
 \label{sec:category-delce}
@@
 A test that fails with a compilation error on the new program version
-is obsolete because of API changes. Listing~\ref{c4-example}
-illustrates a test in this category taken from \subject{JodaTime}.
-This test was deleted because the tested method
-\lang{Chronology.getBuddhist()} was removed in the subsequent version
-of \subject{JodaTime}.
-
-% \vspace{-4pt}
-\lstinputlisting[language=java,label=c4-example,caption=\small{Unit
-  test from class TestChronology} (JodaTime v2.0),frame=tb]
-{code/TestDel-Ce.java}
-%This method was
-%already marked as deprecated in the previous version.
-
+is obsolete because of API changes.
+%
+%% Listing~\ref{c4-example} illustrates a test in this category taken
+%% from \subject{JodaTime}.  This test was deleted because the tested
+%% method \lang{Chronology.getBuddhist()} was removed in the subsequent
+%% version of \subject{JodaTime}.
+%
+%% % \vspace{-4pt}
+%% \lstinputlisting[language=java,label=c4-example,caption=\small{Unit
+%%   test from class TestChronology} (JodaTime v2.0),frame=tb]
+%% {code/TestDel-Ce.java}
+%% %This method was
+%% %already marked as deprecated in the previous version.
+%
 Although for this category of deletion too, one could postulate that
@@
 Instead, the more likely explanation is that the tests were removed
-simply because the tested methods were no longer present. Also in this
-case, we investigated our hypothesis by manually examining ten
-randomly selected cases. Indeed, our manual investigation confirmed
-that, for the cases we analyzed, the tested functionality was either
-removed or provided through alternative methods, which requires the
-development of new tests rather than fixes to the existing ones.
+simply because the tested methods were no longer present.
+%% Also in this case, we investigated our hypothesis by manually
+%% examining ten randomly selected cases. Indeed, our manual
+%% investigation confirmed that, for the cases we analyzed, the tested
+%% functionality was either removed or provided through alternative
+%% methods, which requires the development of new tests rather than fixes
+%% to the existing ones.
 
-\subsubsection{Category \catdelp: Redundant Tests}
+\subsubsection{Category \catdelp: (Redundant Tests)}
 \label{sec:category-delp}
@@
 This category includes tests that are removed even though they pass on
-$P'$.  Listing~\ref{c5-example} illustrates an example of one such
-test, taken from \subject{Commons Lang}. In the new version, this test
-was replaced by a more sophisticated one, shown in
-Listing~\ref{c5.2-example}.
+$P'$. These tests would typically be redundant, by some measure of
+redundancy (\eg code-coverage based). In some cases, a test may be
+replaced with a different one.
 
-\begin{figure}[h]
-\lstinputlisting[language=java,label=c5-example,caption=\small{Unit
-  test from class MatrixIndexExceptionTest} (Commons Lang
-v2.1),frame=tb] {code/TestDel-P.java}
-\vspace{4pt}
-\end{figure}
+%% Listing~\ref{c5-example} illustrates an example of one such test,
+%% taken from \subject{Commons Lang}. In the new version, this test was
+%% replaced by a more sophisticated one, shown in
+%% Listing~\ref{c5.2-example}.
 
-\lstinputlisting[language=java,label=c5.2-example,caption=\small{Unit
-  test implemented to replace the removed one} (Commons Lang
-v2.2),frame=tb] {code/TestDel-PII.java}
+%% \begin{figure}[h]
+%% \lstinputlisting[language=java,label=c5-example,caption=\small{Unit
+%%   test from class MatrixIndexExceptionTest} (Commons Lang
+%% v2.1),frame=tb] {code/TestDel-P.java}
+%% \vspace{4pt}
+%% \end{figure}
+
+%% \lstinputlisting[language=java,label=c5.2-example,caption=\small{Unit
+%%   test implemented to replace the removed one} (Commons Lang
+%% v2.2),frame=tb] {code/TestDel-PII.java}
 
@@
 
-\subsubsection{Category \cataddaere: Bug-Fix Tests}
+\subsubsection{Category \cataddaere: (Bug-Fix Tests)}
 \label{sec:category-addaere}
@@
 fix the fault, which causes $t'$ to pass on $P'$. Thus, $t'$ is added
-to the test suite to validate the bug fix. Listing~\ref{c6-example}
-illustrates a test that fits this profile, as it was added to
-\subject{Commons Math} version 2.1 to validate a bug fix ({\small
-  \url{https://issues.apache.org/jira/browse/MATH-391}}). In the
-previous version of \lang{ArrayRealVector}, the creation of a
-zero-length vector results in a runtime exception.
+to the test suite to validate the bug fix.
 
-% \begin{figure}[h]
-\lstinputlisting[language=java,label=c6-example,caption=\small{\mbox{Unit
-  test from class ArrayRealVectorTest (Commons Math v2.2)}},
-captionpos=t,frame=tb]{code/TestAdd-AeRe.java}
-% \end{figure}
+%% Listing~\ref{c6-example} illustrates a test that fits this profile, as
+%% it was added to \subject{Commons Math} version 2.1 to validate a bug
+%% fix ({\small
+%%   \url{https://issues.apache.org/jira/browse/MATH-391}}). In the
+%% previous version of \lang{ArrayRealVector}, the creation of a
+%% zero-length vector results in a runtime exception.
 
-\subsubsection{Category \cataddce: New-Features Tests}
+%% % \begin{figure}[h]
+%% \lstinputlisting[language=java,label=c6-example,caption=\small{\mbox{Unit
+%%   test from class ArrayRealVectorTest (Commons Math v2.2)}},
+%% captionpos=t,frame=tb]{code/TestAdd-AeRe.java}
+%% % \end{figure}
+
+\subsubsection{Category \cataddce (New-Features Tests)}
 \label{sec:category-addce}
@@
 where the code could have been added as part of a refactoring or, more
-likely, to add new functionality.  Listing~\ref{c7-example}
-illustrates a test from \subject{JFreeChart} that covers a new
-functionality: method \lang{getMinY()} did not exist in previous
-versions of class \lang{TimeSeries}.
+likely, to add new functionality.
 
-\lstinputlisting[language=java,label=c7-example,caption=\small{Unit
-  test from class TimeSeriesTests} (JFreeChart v1.0.14),
-captionpos=t,frame=tb]{code/TestAdd-Ce.java}
+%% Listing~\ref{c7-example} illustrates a test from \subject{JFreeChart}
+%% that covers a new functionality: method \lang{getMinY()} did not exist
+%% in previous versions of class \lang{TimeSeries}.
 
-\subsubsection{Category \cataddp: Coverage-Augmentation Tests}
+%% \lstinputlisting[language=java,label=c7-example,caption=\small{Unit
+%%   test from class TimeSeriesTests} (JFreeChart v1.0.14),
+%% captionpos=t,frame=tb]{code/TestAdd-Ce.java}
+
+\subsubsection{Category \cataddp (Coverage-Augmentation Tests)}
 \label{sec:category-addp}
@@
 purely to increase code coverage (and not to test any added or
-modified code).  Listing~\ref{c8-example} illustrates an added test
-case that increases code coverage: the new test method
-\lang{testFindRangeBounds} covers the case where the parameter of
-method \lang{findRangeBounds()} is null.
+modified code).
 
-\lstinputlisting[language=java,label=c8-example,caption=\small{Unit test
-from class XYErrorRendererTests} (JFreeChart v1.0.14),frame=tb]
-{code/TestAdd-P.java}
+%% Listing~\ref{c8-example} illustrates an added test case that increases
+%% code coverage: the new test method \lang{testFindRangeBounds} covers
+%% the case where the parameter of method \lang{findRangeBounds()} is
+%% null.
+
+%% \lstinputlisting[language=java,label=c8-example,caption=\small{Unit test
+%% from class XYErrorRendererTests} (JFreeChart v1.0.14),frame=tb]
+%% {code/TestAdd-P.java}
 
@@
 
-Test suites evolve throughout their lifetime and change together with
-the applications they are testing. Modifying existing test cases
-manually to adapt them to an evolving system, however, can be
-extremely time consuming, especially for large test suites, which has
-motivated the recent development of automated test-repair techniques.
+Test suites evolve throughout their lifetime and change with the
+applications under test. Adapting existing test cases manually,
+however, can be extremely tedious, especially for large test suites,
+which has motivated the recent development of automated test-repair
+techniques (\eg \cite{Daniel:2009, Daniel:2010, Mirzaaghaei:2012}).
 To support the development of more effective repair techniques, we
 developed \tool, a tool for systematic investigation of test-suite
-evolution that can provide its users with a thorough understanding of
-how test cases evolve in practice. In this demo we present \tool, its
-main features, and its technical characteristics. We also demonstrate
-how \tool\ can be run on real-world software systems and produce a
-wealth of useful information, such as the types of test-suite changes
-that occur in practice and their frequency and why tests are deleted
-and added.  Overall, we show how \tool\ is a useful tool not only for
-researchers in the area of test repair, and test evolution in general,
-but also to developers and testers who want to better understand their
-software systems.
+evolution that can provide its users with a comprehensive
+understanding of how test cases evolve. In this demo, we present
+\tool, its main features, and its technical characteristics. We also
+demonstrate how \tool\ can be run on real-world software systems and
+produce a wealth of useful information, such as the types of
+test-suite changes that occur, the frequency of the changes, and why
+tests are deleted and added.  Overall, we show how \tool\ is a useful
+tool not only for researchers working in the area of test repair, and
+test evolution in general, but also for developers and testers who
+wish to understand their software systems better.
 
@@
 \bibliographystyle{abbrv}
+{\footnotesize
 \bibliography{paper}
+}
 

### 2012-11-02 icse2013demo-testevol/paper.tex
Revised intro

@@
 
-To the best of our knowledge, to date there are no studies in the
-literature that investigate how unit test suites evolve. To address
-this issue, we defined a technique~\cite{pinto12} that combines
-various static- and dynamic-analysis techniques to compute the
-differences between the test suites associated with two versions of a
-program and categorize such changes along two dimensions: the static
-differences between the tests in the two test suites and the
-behavioral differences between such tests.
+More generally, the ability to analyze how test suites evolve can be
+beneficial for developers, as it can help them better understand the
+cost and tradeoffs of test evolution. Similarly, project managers can
+use information about test-suite evolution to get insight into the
+test maintenance process (\eg how often tests are deleted and cause
+oss of coverage, how often tests must be adapted because of changes in
+the system's API) and ultimately improve it.
 
-We implemented our technique in a tool, \tool, which enables a
-systematic study of test-suite evolution. \tool\ targets Java programs
-and JUnit test suites, as Java is a widely used language and JUnit is
-the de-facto standard unit-testing framework for Java.  Given two
-versions of a program and its test suite, \tool\ automatically
-computes differences in the behavior of the test suites on the two
-program versions, classifies the actual repairs performed between the
-versions, and computes the coverage attained by the tests on the two
-program versions.
+Until recently there were no empirical studies in the literature that
+investigated how unit test suites evolve and tools that could support
+such studies. To address this issue, we defined a technique that
+combines various static- and dynamic-analysis techniques to compute
+the differences between the test suites associated with two versions
+of a program and categorize such changes along two dimensions: the
+static differences between the tests in the two test suites and the
+behavioral differences between such tests~\cite{pinto12}. Applying our
+technique to a number of real-world programs, we were able to discover
+several important aspects of test evolution. For example, we found
+evidence that, although test repairs are a relatively small fraction
+of the activities performed during test evolution, they are indeed
+relevant.  We also found that repair techniques that just focus on
+oracles (\ie assertions) are likely to be inapplicable in many cases,
+that test cases are rarely removed because they are difficult to fix,
+but rather because they have become obsolete, and that test cases are
+not only added to check bug fixes and test new functionality, as
+expected, but also to validate changes in the code.
 
-In this demo, we present \tool, its features and technical details,
-and show how it can be used to study how test suites evolved over the
-years for a project.  To do so, we will show examples of application
-of the tool to a set of real-world open-source software systems.
-Specifically, we will show how to use \tool\ to investigate relevant
-questions on test evolution, such as: What types of test-suite changes
-occur in practice and with what frequency? How often do test repairs
-require complex modifications of the tests? Why are tests deleted and
-added? Overall, we will show how \tool\ is a useful tool not only for
-researchers in the area of test repair (and test evolution in
-general), but also to developers and testers who want to better
-understand their software systems.
+This demo presents a tool that implements our technique and that we
+developed to allow other researchers and practitioners to perform
+studies such as we the ones we just summarized. The tool, which is
+called \tool, enables a systematic study of test-suite evolution.
+Given two versions of a program and corresponding test suites, \tool\
+automatically computes differences in the behavior of the test suites
+on the two program versions, classifies the actual repairs performed
+between the two versions, and computes the coverage attained by the
+tests on the versions.
 
-\todo{Discuss \tool's availability at
-  \url{http://cheetah.cc.gt.atl.ga.us:8081/testevol/}}.
+After presenting \tool's features and technical details, the demo
+shows how the tool can be used to study how test suites evolved over
+the years for a software project.  To do so, we show examples of
+application of \tool\ to a set of real-world open-source software
+systems.  Specifically, we show how to use \tool\ to investigate
+relevant questions on test evolution, such as the following ones: What
+types of test-suite changes occur in practice and with what frequency?
+How often do test repairs require complex modifications of the tests?
+Why are tests deleted and added? Overall, we show how \tool\ is a
+useful and practically applicable tool for researchers in the area of
+test repair (and test evolution in general), developers and testers
+who want to better understand their software maintenance process.
 

### 2012-11-02 icse2013demo-testevol/paper.tex
Revised paper

@@
   study of test-suite evolution for Java programs and JUnit test
-  cases.  This demo presents \tool and demonstrates its usefulness and
-  practical applicability by showing how \tool\ can be used on
-  real-world software and unit test suites.
+  cases.  This demonstration presents \tool and demonstrates its
+  usefulness and practical applicability by showing how \tool\ can be
+  used on real-world software and unit test suites.
 \end{abstract}
@@
 
-\section{Introduction}
+\section{Motivation and Overview}
 \label{sec:intro}
@@
 
-This demo presents a tool that implements our technique and that we
-developed to allow other researchers and practitioners to perform
-studies such as we the ones we just summarized. The tool, which is
-called \tool, enables a systematic study of test-suite evolution.
-Given two versions of a program and corresponding test suites, \tool\
-automatically computes differences in the behavior of the test suites
-on the two program versions, classifies the actual repairs performed
-between the two versions, and computes the coverage attained by the
-tests on the versions.
+This demonstration presents a tool that implements our technique and
+that we developed to allow other researchers and practitioners to
+perform studies such as we the ones we just summarized. The tool,
+which is called \tool, enables a systematic study of test-suite
+evolution.  Given two versions of a program and corresponding test
+suites, \tool\ automatically computes differences in the behavior of
+the test suites on the two program versions, classifies the actual
+repairs performed between the two versions, and computes the coverage
+attained by the tests on the versions.
 
-After presenting \tool's features and technical details, the demo
-shows how the tool can be used to study how test suites evolved over
-the years for a software project.  To do so, we show examples of
-application of \tool\ to a set of real-world open-source software
-systems.  Specifically, we show how to use \tool\ to investigate
-relevant questions on test evolution, such as the following ones: What
-types of test-suite changes occur in practice and with what frequency?
-How often do test repairs require complex modifications of the tests?
-Why are tests deleted and added? Overall, we show how \tool\ is a
-useful and practically applicable tool for researchers in the area of
-test repair (and test evolution in general), developers and testers
-who want to better understand their software maintenance process.
+After presenting \tool's features and technical details, the
+demonstration shows how the tool can be used to study how test suites
+evolved over the years for a software project.  To do so, we show
+examples of application of \tool\ to a set of real-world open-source
+software systems.  Specifically, we show how to use \tool\ to
+investigate relevant questions on test evolution, such as the
+following ones: What types of test-suite changes occur in practice and
+with what frequency?  How often do test repairs require complex
+modifications of the tests?  Why are tests deleted and added? Overall,
+we show how \tool\ is a useful and practically applicable tool for
+researchers in the area of test repair (and test evolution in
+general), developers and testers who want to better understand their
+software maintenance process.
 
-\section{Studying Test-Suite Evolution}
+\section{The \tool\ Tool}
 \label{sec:test-evolution}
 
-\subsection{Definitions and Terminology}
-\label{sec:terminology}
+In this section we firs summarize our technique, implemented in the
+\tool\ tool, and then discuss the main characteristics of the tool
+implementation. A detailed description of the approach can be found
+in~\cite{pinto12}.
 
-A \textit{system} $S = (P, T)$ consists of a program $P$ and a test
-suite $T$.  A \textit{test suite} $T = \{t_1, t_2, \ldots, t_n\}$
-consists of a set of unit test cases.
+\subsection{Underlying Technique}
+
+Before describing the characteristics of our technique, we introduce
+some necessary terminology.  A \textit{system} $S = (P, T)$ consists
+of a program $P$ and a test suite $T$.  A \textit{test suite} $T =
+\{t_1, t_2, \ldots, t_n\}$ consists of a set of unit test cases.
 % A unit test case $t$ is a method (or function) and it is identified
@@
 
-\subsection{Test Modifications}
+\paragraph*{\textbf{Test Modifications}}
 \label{sec:test-mod}
@@
 
-\subsubsection{Category \catrep{} (Repaired Tests)}
+\paragraph{Category \catrep{} (Repaired Tests)}
 \label{sec:category-rep}
@@
 
-\subsubsection{Category \catref{} (Refactored Tests)}
+\paragraph{Category \catref{} (Refactored Tests)}
 \label{sec:category-c2}
@@
 
-\subsection{Test Deletions}
+\paragraph*{\textbf{Test Deletions}}
 \label{sec:test-ref}
@@
 
-\subsubsection{Category \catdelaere{} (Hard-To-Fix Tests)}
+\paragraph{Category \catdelaere{} (Hard-To-Fix Tests)}
 \label{sec:category-delaere}
@@
 
-\subsubsection{Category \catdelce (Obsolete Tests)}
+\paragraph{Category \catdelce (Obsolete Tests)}
 \label{sec:category-delce}
@@
 
-\subsubsection{Category \catdelp: (Redundant Tests)}
+\paragraph{Category \catdelp: (Redundant Tests)}
 \label{sec:category-delp}
@@
 
-\subsection{Test Additions}
+\paragraph*{\textbf{Test Additions}}
 \label{sec:test-add}
@@
 
-\subsubsection{Category \cataddaere: (Bug-Fix Tests)}
+\paragraph{Category \cataddaere: (Bug-Fix Tests)}
 \label{sec:category-addaere}
@@
 
-\subsubsection{Category \cataddce (New-Features Tests)}
+\paragraph{Category \cataddce (New-Features Tests)}
 \label{sec:category-addce}
@@
 
-\subsubsection{Category \cataddp (Coverage-Augmentation Tests)}
+\paragraph{Category \cataddp (Coverage-Augmentation Tests)}
 \label{sec:category-addp}
@@
 
-\section{Implementation of \tool}
+\section{Implementation}
 \label{sec:implementation}
 
-\todo{Add the discussion of clone analysis.}
+% \todo{Add the discussion of clone analysis.}
+% \todo{In general, add more details.}
+% \todo{Discuss the availability of the tool.}
 
-\todo{In general, add more details.}
+In our demonstration, we show an implementation of our technique,
+\tool, that works for Java programs and JUnit test suites ({\small
+  \url{http://www.junit.org/}}). We chose Java and JUnit because the
+former is a widely used language, and the latter is the de-facto
+standard unit-testing framework for Java.  \tool\ analyzes a sequence
+of versions of a software system, where each version consists of
+application code and test code and can be an actual release or an
+internal build.
 
-\todo{Discuss the availability of the tool.}
+\tool\ is implemented as a Java based web application that runs on
+Apache Tomcat ({\small \url{http://tomcat.apache.org/}}). Although the
+tool can be installed locally, using a local server, users who want to
+get familiar with \tool\ without having to install it can access it
+remotely on our servers. The tool is currently available at {\small
+  \url{http://cheetah.cc.gt.atl.ga.us:8081/testevol/}}, and
+unregistered users can access the tool using account ``icse'', with
+password ``icse2013''.
 
-We implemented our approach for studying test suite evolution in a
-tool, called \tool, which facilitates a systematic study of test-suite
-evolution for Java programs and JUnit test suites.  \tool\ analyzes a
-sequence of versions of a software system, where each version consists
-of application code and test code. The versions can be actual releases
-or internal builds.  \tool\ consists of five components, as
-illustrated in the architecture diagram shown in
-Figure~\ref{fig:trex}.
+Due to space limitations, we can only provide a few examples of
+\tool's graphical interface. The companion video demonstration for
+this paper illustrates the tool interface in full detail. Figure...
 
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=\columnwidth]{1-summary}
+        \vspace*{-16pt}
+	\caption{TBD.}
+        \vspace*{-8pt}
+	\label{fig:summary}
+\end{figure}
+
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=\columnwidth]{2-versiondetails}
+        \vspace*{-16pt}
+	\caption{TBD.}
+        \vspace*{-8pt}
+	\label{fig:versiondetails}
+\end{figure}
+
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=\columnwidth]{3-testdetails}
+        \vspace*{-16pt}
+	\caption{TBD.}
+        \vspace*{-8pt}
+	\label{fig:testdetails}
+\end{figure}
+
+\tool\ consists of five components, as illustrated in the architecture
+diagram shown in Figure~\ref{fig:trex}. 
+%
 The \emph{compiler} component builds each system version and creates
@@
 	\centering
-	\includegraphics[width=\columnwidth]{architecture.png}
+	\includegraphics[width=\columnwidth]{architecture}
         \vspace*{-16pt}
@@
 evolution that can provide its users with a comprehensive
-understanding of how test cases evolve. In this demo, we present
-\tool, its main features, and its technical characteristics. We also
-demonstrate how \tool\ can be run on real-world software systems and
-produce a wealth of useful information, such as the types of
-test-suite changes that occur, the frequency of the changes, and why
-tests are deleted and added.  Overall, we show how \tool\ is a useful
-tool not only for researchers working in the area of test repair, and
-test evolution in general, but also for developers and testers who
-wish to understand their software systems better.
+understanding of how test cases evolve. In this demonstration, we
+present \tool, its main features, and its technical
+characteristics. We also demonstrate how \tool\ can be run on
+real-world software systems and produce a wealth of useful
+information, such as the types of test-suite changes that occur, the
+frequency of the changes, and why tests are deleted and added.
+Overall, we show how \tool\ is a useful tool not only for researchers
+working in the area of test repair, and test evolution in general, but
+also for developers and testers who wish to understand their software
+systems better.
 

### 2012-11-02 tool/src/main/java/org/testevol/infra/ProjectRepoFileSystem.java
Executions -> Analysis

@@ -174,7 +174,7 @@ public class ProjectRepoFileSystem implements ProjectRepository {
 				}
 			}
 			
-			Execution execution = new Execution(project, "Untitled execution", reportDir, Calendar.getInstance().getTimeInMillis(), versions, ExecutionStatus.INITIALIZED);
+			Execution execution = new Execution(project, "New Analysis", reportDir, Calendar.getInstance().getTimeInMillis(), versions, ExecutionStatus.INITIALIZED);
 			execution.saveProperties(new File(reportDir, EXECUTION_PROPERTIES));
 			
 			return execution;

### 2012-11-03 icse2013demo-testevol/paper.tex
Added description about figures and new snapshots

@@
 \tool's graphical interface. The companion video demonstration for
-this paper illustrates the tool interface in full detail. Figure...
+this paper illustrates the tool interface in full detail. Figure~\ref{fig:summary}
+shows the summary report generated by TestEvol. Such summary report
+contains the total number of tests included in each one of the eight
+categories we have defined in our approach, and previously described.
+Note that beside the totals for all versions together, the summary also 
+shows the results for each pair of versions. Figure~\ref{fig:versiondetails}
+shows an example of the detailed report which shows details of all the tests
+included in each one of the categories. In this figure is shown the list of
+tests in the \catrep category. When tests in this category, and also those in
+category \catref, are clicked, TestEvol opens a dialog which lets
+the user compare two versions of the same test case. This is exemplified in Figure~\ref{fig:summary}.
 
@@
         \vspace*{-16pt}
-	\caption{TBD.}
+	\caption{Summary report generated from a \tool Analysis}
         \vspace*{-8pt}
@@
         \vspace*{-16pt}
-	\caption{TBD.}
+	\caption{Detailed report for a pair of versions.}
         \vspace*{-8pt}
@@
         \vspace*{-16pt}
-	\caption{TBD.}
+	\caption{Comparison between two different versions of a test case}
         \vspace*{-8pt}

### 2012-11-03 tool/src/main/java/org/testevol/controller/RequestAccountController.java
request access. Bug fix for paralell executions

@@ -1,0 +1,64 @@
+package org.testevol.controller;
+
+import java.util.Properties;
+
+import javax.mail.Message;
+import javax.mail.MessagingException;
+import javax.mail.PasswordAuthentication;
+import javax.mail.Session;
+import javax.mail.Transport;
+import javax.mail.internet.InternetAddress;
+import javax.mail.internet.MimeMessage;
+
+import org.springframework.beans.factory.annotation.Value;
+import org.springframework.stereotype.Controller;
+import org.springframework.web.bind.annotation.RequestMapping;
+import org.springframework.web.bind.annotation.RequestMethod;
+import org.springframework.web.bind.annotation.RequestParam;
+
+@Controller
+@RequestMapping("/account")
+public class RequestAccountController {
+
+	@Value("#{testEvolProperties.email}")
+	String email;
+	@Value("#{testEvolProperties.passwd}")
+	String password;
+
+	@RequestMapping(method = RequestMethod.GET)
+	public 	String getBranches(@RequestParam("username") String username) {
+		if(username == null || username.trim().length() == 0){
+			return "redirect:/login";
+		}
+
+		Properties props = new Properties();
+		props.put("mail.smtp.auth", "true");
+		props.put("mail.smtp.starttls.enable", "true");
+		props.put("mail.smtp.host", "smtp.gmail.com");
+		props.put("mail.smtp.port", "587");
+ 
+		Session session = Session.getInstance(props,
+		  new javax.mail.Authenticator() {
+			protected PasswordAuthentication getPasswordAuthentication() {
+				return new PasswordAuthentication(email, password);
+			}
+		  });
+ 
+		try {
+ 
+			Message message = new MimeMessage(session);
+			message.setFrom(new InternetAddress(email));
+			message.setRecipients(Message.RecipientType.TO,
+				InternetAddress.parse("leandro.shp@gmail.com"));
+			message.setSubject("Testevol Access Request");
+			message.setText(username+" is requesting access to Testevol.");
+ 
+			Transport.send(message);
+		} catch (MessagingException e) {
+			throw new RuntimeException(e);
+		}
+		
+		return "redirect:/login?accessRequested=true";
+	}
+
+}

### 2012-11-03 tool/src/main/java/org/testevol/domain/Version.java

@@ -188,6 +188,11 @@ public class Version {
 	public File getDirectory() {
 		return versionDir;
 	}
+	
+	public void setDirectory(File versionDir) {
+		this.versionDir = versionDir;
+	}
+
 
 	public int getIndex() {
 		return Integer.parseInt(properties.getProperty("index"));

### 2012-11-03 icse2013demo-testevol/paper.tex

--- 2012-11-02 icse2013demo-testevol/paper.tex
@@
 % \usepackage{hyperref}
-\usepackage[bookmarks=false]{hyperref}
+\usepackage{hyperref}
 \usepackage{xspace}\usepackage{float}
@@
 \displaywidowpenalty = 10000
+
+\hypersetup{
+colorlinks=true,
+bookmarksnumbered=true,
+pdftitle={Isolating Failure Causes through Test Case Generation},
+pdfauthor={Jeremias R\"o\ss{}ler and Gordon Fraser and Andreas Zeller and Alessandro Orso},
+pdfsubject={Automated Testing},
+pdfkeywords={Automated Debugging, Diagnostics, Testing tools}
+}
 
@@
   used on real-world software and unit test suites.
+
+  \noindent
+  Demo video at {\small \url{http://www.cc.gatech.edu/~orso/software/testevol/}}
+
 \end{abstract}
@@
 In our demonstration, we show an implementation of our technique,
-\tool, that works for Java programs and JUnit test suites ({\small
+\tool, that works on Java programs and JUnit test suites ({\small
   \url{http://www.junit.org/}}). We chose Java and JUnit because the
@@
 standard unit-testing framework for Java.  \tool\ analyzes a sequence
-of versions of a software system, where each version consists of
-application code and test code and can be an actual release or an
-internal build.
+of versions of a software system, where each version can be an actual
+release or an internal build and consists of application code and test
+code.
 
@@
 Apache Tomcat ({\small \url{http://tomcat.apache.org/}}). Although the
-tool can be installed locally, using a local server, users who want to
-get familiar with \tool\ without having to install it can access it
-remotely on our servers. The tool is currently available at {\small
-  \url{http://cheetah.cc.gt.atl.ga.us:8081/testevol/}}, and
-unregistered users can access the tool using account ``icse'', with
-password ``icse2013''.
+tool can be installed locally, users who want to get familiar with
+\tool\ without having to install it can also access it remotely at
+{\small \url{http://cheetah.cc.gt.atl.ga.us:8081/testevol/}},
+specifying user ``icse'' and password ``icse2013''.
 
 Due to space limitations, we can only provide a few examples of
-\tool's graphical interface. The companion video demonstration for
-this paper illustrates the tool interface in full detail. Figure...
+\tool's graphical interface. (The companion demo video illustrates the
+tool interface in full detail.) Figure~\ref{fig:summary} shows the
+summary report generated by \tool\ for two pairs of versions of
+project \subject{google-gson}. The report shows the number of tests,
+both total and per version, that fall in each of the eight categories
+defined in our approach.  By clicking on a pair of versions, the user
+can obtain detailed report for a specific pair of versions. To
+illustrate, Figure~\ref{fig:versiondetails} shows the detailed report
+for versions $v.1.1$--$v.1.2$ and a specific category of differences
+(\catrep). By further clicking on a test case in the list, users can
+also inspect, in the case of modified tests, the actual differences
+between the two versions of that test, as shown in
+Figure~\ref{fig:summary} for test case \subject{TypeInfoTest}.
 
@@
 	\includegraphics[width=\columnwidth]{1-summary}
-        \vspace*{-16pt}
-	\caption{TBD.}
+        \vspace*{-20pt}
+	\caption{Summary report for two pairs of versions of a
+          project.}
         \vspace*{-8pt}
@@
 	\includegraphics[width=\columnwidth]{2-versiondetails}
-        \vspace*{-16pt}
-	\caption{TBD.}
+        \vspace*{-20pt}
+	\caption{Detailed report for a pair of versions.}
         \vspace*{-8pt}
@@
 	\includegraphics[width=\columnwidth]{3-testdetails}
-        \vspace*{-16pt}
-	\caption{TBD.}
+        \vspace*{-20pt}
+	\caption{Differences between two versions of a test case.}
         \vspace*{-8pt}
@@
 
-\tool\ consists of five components, as illustrated in the architecture
-diagram shown in Figure~\ref{fig:trex}. 
+In terms of design, \tool\ consists of five components, as illustrated
+in Figure~\ref{fig:trex}.
 %
@@
 of the eight test-evolution categories presented in
-Section~\ref{sec:test-evolution}.  For each pair of broken test case
-and its repaired version, the test classifier also compares the test
-cases to identify the types of repair changes---different types of
-method-sequence changes and assertion changes---as discussed in
-Section~\ref{sec:category-rep}; this analysis is also implemented
+Section~\ref{sec:test-evolution}. For each pair consisting of a broken
+test case and its repaired version, the test classifier also compares
+the test cases to identify the types of repair changes---different
+types of method-sequence changes and assertion changes---as discussed
+in Section~\ref{sec:category-rep}; this analysis is also implemented
 using \textsc{wala}.
@@
 	\includegraphics[width=\columnwidth]{architecture}
-        \vspace*{-16pt}
-	\caption{High-level architecture of \tool.}
+        \vspace*{-20pt}
+	\caption{High-level design of \tool.}
         \vspace*{-8pt}
@@
 understanding of how test cases evolve. In this demonstration, we
-present \tool, its main features, and its technical
-characteristics. We also demonstrate how \tool\ can be run on
-real-world software systems and produce a wealth of useful
-information, such as the types of test-suite changes that occur, the
-frequency of the changes, and why tests are deleted and added.
-Overall, we show how \tool\ is a useful tool not only for researchers
-working in the area of test repair, and test evolution in general, but
-also for developers and testers who wish to understand their software
-systems better.
+present \tool, its main features, and its technical characteristics.
+We also demonstrate how \tool\ can be run on real-world software
+systems and produce a wealth of useful information, such as the types
+of test-suite changes that occur, the frequency of the changes, and
+why tests are deleted and added.  Overall, we show how \tool\ is a
+useful tool not only for researchers working in the area of test
+repair, and test evolution in general, but also for developers and
+testers who wish to understand their software systems better.
 

### 2012-11-03 webpage/js/site.js
added webpage to repository

@@ -1,0 +1,35 @@
+function add_menu(){
+	var menu_code = '';
+	menu_code += '<ul>';
+	menu_code += '<li><a id="menu_index" href="index.html"><span>Home</span></a></li>';
+	menu_code += '<li><a id="menu_documentation" href="documentation.html"><span>Documentation</span></a></li>';
+	menu_code += '<li><a id="menu_publication" href="publications.html"><span>Publications</span></a></li>';
+	menu_code += '<li><a id="menu_download" href="download.html"><span>Download</span></a></li>';
+	menu_code += '<li><a id="menu_authors" href="authors.html"><span>Authors</span></a></li>';
+	menu_code += '</ul>';
+	$("#topmenu").html(menu_code);
+	if(activeTab != ""){
+		$(activeTab).addClass("active");		
+	}
+}
+
+function getting_started(){
+	var code ='';
+	code += '<h3>Getting Started</h3>';
+	code += '<ul>';
+	code += '<li><a href="documentation.html">Documentation</a></li>';
+	code += '<li><a href="help.html">Getting help</a></li>';
+	code += '</ul>';
+	$("#getting_started").html(code);
+}
+
+function show_smscom_box(){
+	var code = '<div style="text-align: center;"><a href="http://www.erc-smscom.org/" target="_blank"><img id="smscom" src="images/smscom_logo.png" alt="SMSCom" /></a><br /><br />DSOL is developed as part of the SMSCom project</div>';
+	$("#smscom_box").html(code);
+}
+
+function init(){
+	add_menu();
+	getting_started();
+	show_smscom_box();
+}

### 2012-11-03 tool/src/main/java/org/testevol/controller/RequestAccountController.java
request tool

@@ -26,11 +26,28 @@ public class RequestAccountController {
 	String password;
 
 	@RequestMapping(method = RequestMethod.GET)
-	public 	String getBranches(@RequestParam("username") String username) {
+	public 	String requestAccount(@RequestParam("username") String username) {
 		if(username == null || username.trim().length() == 0){
 			return "redirect:/login";
 		}
 
+		request("Testevol Access Request", username);
+		
+		return "redirect:/login?accessRequested=true";
+	}
+
+	@RequestMapping(value="tool", method = RequestMethod.GET)
+	public 	String requestTool(@RequestParam("username") String username) {
+		if(username == null || username.trim().length() == 0){
+			return "redirect:/login";
+		}
+
+		request("Testevol Tool Request", username);
+		
+		return "redirect:/login?toolRequested=true";
+	}
+	
+	private void request(String messageBody, String username){
 		Properties props = new Properties();
 		props.put("mail.smtp.auth", "true");
 		props.put("mail.smtp.starttls.enable", "true");
@@ -50,15 +67,13 @@ public class RequestAccountController {
 			message.setFrom(new InternetAddress(email));
 			message.setRecipients(Message.RecipientType.TO,
 				InternetAddress.parse("leandro.shp@gmail.com"));
-			message.setSubject("Testevol Access Request");
+			message.setSubject(messageBody);
 			message.setText(username+" is requesting access to Testevol.");
  
 			Transport.send(message);
 		} catch (MessagingException e) {
 			throw new RuntimeException(e);
 		}
-		
-		return "redirect:/login?accessRequested=true";
 	}
 
 }

### 2012-11-03 icse2013demo-testevol/paper.tex
Complete pass

@@
 bookmarksnumbered=true,
-pdftitle={Isolating Failure Causes through Test Case Generation},
-pdfauthor={Jeremias R\"o\ss{}ler and Gordon Fraser and Andreas Zeller and Alessandro Orso},
-pdfsubject={Automated Testing},
-pdfkeywords={Automated Debugging, Diagnostics, Testing tools}
+pdftitle={TestEvol: A Tool for Analyzing Test-Suite Evolution},
+pdfauthor={Leandro Sales Pinto and Saurabh Sinha and Alessandro Orso},
+pdfsubject={Test Evolution},
+pdfkeywords={Test Repair, Test-Suite Evolution, Test Maintenance}
 }
@@
 
-% \note{This is a VERY rough draft that I put together by copying and
-%   pasting from the FSE paper. I left some specific TODOs in, but the
-%   paper really needs a major pass.}
-% \todo{Restructure the content to make sure we comply with what is
-%   requested from a demo paper: Tool-based demonstrations describe
-%   novel aspects of early prototypes or mature tools. The tool
-%   demonstrations must communicate clearly the following information to
-%   the audience:\\
+% Tool-based demonstrations describe novel aspects of early prototypes
+% or mature tools. The tool demonstrations must communicate clearly
+% the following information to the audience:\\
 % - the envisioned users;\\
@@
 % - the methodology it implies for its users; and\\
-%   - the results of validation studies already conducted for mature tools, or the design of planned studies for early prototypes.}
-% \todo{Reduce the description of the approach and extend the
-%   description of the implementation. Leandro, can you add some details
-%   there?}
-% \todo{Add snapshots.}
+% - the results of validation studies already conducted for mature
+% tools, or the design of planned studies for early prototypes.}
 
 \begin{abstract}
-  Test suites, once created, rarely remain static. Just like the
-  application they are testing, they evolve throughout their lifetime.
-  Test obsolescence is probably the most known reason for test-suite
-  evolution---test cases cease to work because of changes in the code
-  and must be suitably repaired. There are several reasons why it is
-  important to achieve a thorough understanding of how test cases
-  evolve in practice. In particular, researchers who develop automated
-  test-repair techniques---an increasingly active research area---can
-  use such understanding to develop more effective repair techniques
-  that are applicable in real-world scenarios. More generally,
-  analyzing test-suite evolution can help testers better understand
-  how test cases are modified during maintenance and improve the test
-  evolution process, an extremely time consuming activity for any non
-  trivial test suite.  Unfortunately, there are no existing tools that
-  facilitate investigation of test-suite evolution. To tackle this
-  problem, we developed \tool, a tool that enables the systematic
-  study of test-suite evolution for Java programs and JUnit test
-  cases.  This demonstration presents \tool and demonstrates its
+  Test suites, just like the applications they are testing, evolve
+  throughout their lifetime.  One of the main reasons for test-suite
+  evolution is test obsolescence: test cases cease to work because of
+  changes in the code and must be suitably repaired. There are several
+  reasons why it is important to achieve a thorough understanding of
+  how test cases evolve in practice. In particular, researchers who
+  develop automated test-repair techniques---an increasingly active
+  research area---can use such understanding to develop more effective
+  repair techniques that are applicable in real-world scenarios. More
+  generally, analyzing test-suite evolution can help testers better
+  understand how test cases are modified during maintenance and
+  improve the test evolution process, an extremely time consuming
+  activity for any non-trivial test suite.  Unfortunately, there are
+  no existing tools that facilitate investigation of test evolution.
+  To tackle this problem, we developed \tool, a tool that enables the
+  systematic study of test-suite evolution for Java programs and JUnit
+  test cases. This demonstration presents \tool\ and illustrates its
   usefulness and practical applicability by showing how \tool\ can be
-  used on real-world software and unit test suites.
+  successfully used on real-world software and test suites.
 
@@
 Test suites are not static entities: they constantly evolve along with
-the application they test. For instance, new tests can be added to
-test new functionality and existing tests can be refactored, repaired,
-or deleted.  In particular, changes in the application can break test
-cases---in some cases, even a small change in the application code can
-affect a large number of tests.
-
-A broken test, if it covers a valid functionality, should ideally be
-repaired. Alternatively, if the repair is unduly complex to perform or
-if the test was designed to cover a functionality that no longer
-exists in the application, the test should be removed from the test
-suite. To illustrate with an example,
-Figure~\ref{fig:pmd-javatokenizertest} shows two versions of a unit
-test case from the test suite of \subject{PMD}, one of the programs we
-analyzed in our previous work~\cite{pinto12}. A change in
-\subject{PMD}'s API broke the original version of the test case, which
-had to be fixed by adding a call to method
-\lang{SourceCode.readSource} and removing one parameter from the call
-to method \lang{Tokenizer.tokenize} (lines 6 and 7 in
+the applications they test. For instance, new tests can be added to
+test new functionality, and existing tests can be refactored,
+repaired, or deleted. Often, test cases have to be modified because
+changes in the application break them. In these cases, if the broken
+test covers a valid functionality, it should ideally be repaired.
+Alternatively, if the repair is unduly complex to perform, or if the
+test was designed to cover a functionality that no longer exists in
+the application, the test should be removed from the test suite. To
+illustrate with an example, Figure~\ref{fig:pmd-javatokenizertest}
+shows two versions of a unit test case from the test suite of
+\subject{PMD}, one of the programs we analyzed in previous
+work~\cite{pinto12}.  A change in \subject{PMD}'s API broke the
+original version of the test case, which had to be fixed by adding a
+call to method \lang{SourceCode.readSource} and removing one parameter
+from the call to method \lang{Tokenizer.tokenize} (lines 6 and 7 in
 Figure~\ref{fig:pmd-javatokenizertest}(b), respectively).
@@
 practice.  That is, we must understand when and how tests are created,
-removed, and modified. This is a necessary, preliminary step because
-it can (1) provide evidence that test cases do get repaired, (2)
-support the hypothesis that test repairs can be (at least partially)
-automated, and (3) suitably direct research efforts.  Without such
-understanding, we risk to develop techniques that may not be generally
-applicable and may not perform the kind of repairs that are actually
-needed in real-world software systems.
+removed, and modified. Such understanding can (1) provide evidence
+that test cases do get repaired, (2) support the hypothesis that test
+repairs can be (at least partially) automated, and (3) suitably guide
+research efforts.  Otherwise, we risk to develop techniques that may
+not be generally applicable and may not perform the kind of repairs
+that are actually needed in real-world software systems.
 
@@
 test maintenance process (\eg how often tests are deleted and cause
-oss of coverage, how often tests must be adapted because of changes in
-the system's API) and ultimately improve it.
+loss of coverage or how often tests must be adapted because of changes
+in the system's API) and ultimately improve it.
 
-Until recently there were no empirical studies in the literature that
-investigated how unit test suites evolve and tools that could support
-such studies. To address this issue, we defined a technique that
-combines various static- and dynamic-analysis techniques to compute
-the differences between the test suites associated with two versions
-of a program and categorize such changes along two dimensions: the
-static differences between the tests in the two test suites and the
-behavioral differences between such tests~\cite{pinto12}. Applying our
-technique to a number of real-world programs, we were able to discover
-several important aspects of test evolution. For example, we found
-evidence that, although test repairs are a relatively small fraction
-of the activities performed during test evolution, they are indeed
-relevant.  We also found that repair techniques that just focus on
-oracles (\ie assertions) are likely to be inapplicable in many cases,
-that test cases are rarely removed because they are difficult to fix,
-but rather because they have become obsolete, and that test cases are
-not only added to check bug fixes and test new functionality, as
-expected, but also to validate changes in the code.
+Until recently, there were no empirical studies in the literature that
+investigated how unit test suites evolve, and no tools that could
+support such studies existed. To address this issue, we defined a
+technique that combines various static- and dynamic-analysis
+techniques to (1) compute the differences between the test suites
+associated with two versions of a program and (2) categorize such
+changes along two dimensions: the static differences between the tests
+in the two test suites and the behavioral differences between such
+tests~\cite{pinto12}. Applying our technique to a number of real-world
+programs, we were able to discover several important aspects of test
+evolution. For example, we found evidence that, although test repairs
+are a relatively small fraction of the activities performed during
+test evolution, they are indeed relevant.  We also found that repair
+techniques that just focus on oracles (\ie assertions) are likely to
+be inapplicable in many cases, that test cases are rarely removed
+because they are difficult to fix, but rather because they have become
+obsolete, and that test cases are not only added to check bug fixes
+and test new functionality, as expected, but also to validate modified
+code.
 
-This demonstration presents a tool that implements our technique and
-that we developed to allow other researchers and practitioners to
-perform studies such as we the ones we just summarized. The tool,
-which is called \tool, enables a systematic study of test-suite
-evolution.  Given two versions of a program and corresponding test
-suites, \tool\ automatically computes differences in the behavior of
-the test suites on the two program versions, classifies the actual
-repairs performed between the two versions, and computes the coverage
-attained by the tests on the versions.
+This demonstration presents a tool, \tool, that implements our
+technique and that we developed to allow other researchers and
+practitioners to perform additional studies on test evolution. Given
+two versions of a program and corresponding test suites, \tool\
+automatically computes and classifies both static and behavioral
+differences between the test suites for the two program versions.
+\tool\ can identify deleted, added, and repaired test cases, together
+with the effect that such deletions, additions, and repairs have on
+code coverage.
 
 After presenting \tool's features and technical details, the
-demonstration shows how the tool can be used to study how test suites
-evolved over the years for a software project.  To do so, we show
-examples of application of \tool\ to a set of real-world open-source
-software systems.  Specifically, we show how to use \tool\ to
-investigate relevant questions on test evolution, such as the
-following ones: What types of test-suite changes occur in practice and
-with what frequency?  How often do test repairs require complex
-modifications of the tests?  Why are tests deleted and added? Overall,
-we show how \tool\ is a useful and practically applicable tool for
-researchers in the area of test repair (and test evolution in
-general), developers and testers who want to better understand their
-software maintenance process.
+demonstration shows how the tool can be used to study the evolution,
+over the years, of a software project's test suite.  To do so, we show
+examples of application of \tool\ to several real-world open-source
+software systems. In particular, we show how to use \tool\ to
+investigate relevant questions on test evolution, such as what types
+of test-suite changes occur in practice and with what frequency, how
+often test repairs require complex modifications of the tests, and why
+tests are deleted and added. We demonstrate how \tool\ is a useful and
+practically applicable tool for researchers and practitioners
+interested in test repair (and test evolution in general), and for
+developers and testers who want to better understand their test
+maintenance process.
 
@@
 
-In this section we firs summarize our technique, implemented in the
+In this section we first summarize our technique, implemented in the
 \tool\ tool, and then discuss the main characteristics of the tool
@@
 
-\begin{itemize}\denseitems
+\noindent
+1) $\pass$: The execution of $P$ against $t$ succeeds.
 
-\item $\pass$: The execution of $P$ against $t$ succeeds.
+\noindent
+2) $\failce$: The execution of $P$ against $t$ fails because a class
+or method accessed in $t$ does not exist in $P$.\footnote{\small These
+  failures can obviously be detected at compile-time. For consistency
+  in the discussion, however, we consider such cases to be detected at
+  runtime via ``class not found'' or ``no such method'' exceptions. In
+  fact, \tool\ detects such failures at runtime by executing the tests
+  compiled using the previous version of $P$ on $P$.}
 
-\item $\failce$: The execution of $P$ against $t$ fails because a
-  class or method accessed in $t$ does not exist in
-  $P$.\footnote{\small These failures can obviously be detected at
-    compile-time. For the sake of consistency in the discussion,
-    however, we consider such cases to be detected at runtime via
-    ``class not found'' or ``no such method'' exceptions. In fact, our
-    \tool{} tool detects such failures at runtime by executing the
-    tests compiled using the previous version of $P$ on $P$.}
-
-\item $\failre$: The execution of $P$ against $t$ fails due to an
+\noindent
+3) $\failre$: The execution of $P$ against $t$ fails due to an
 uncaught runtime exception (\eg a ``null pointer'' exception).
 
-\item $\failae$: The execution of $P$ against $t$ fails due to an
+\noindent
+4) $\failae$: The execution of $P$ against $t$ fails due to an
 assertion violation.
 
-\end{itemize}
+We use the generic term $\fail$ to refer to failures for which the
+distinction among different types of failures is unnecessary.
 
-We use the generic term $\fail$ to refer to failures for which the
-distinction among the above three types of failures is unnecessary.
-
-$\covfunc{P}{t}$ is a function that instruments program $P$, executes
-test case $t$ on $P$, and returns the set of all statements in $P$
-covered by $t$. $\covfunc{P}{T}$ returns the cumulative coverage
-achieved on $P$ by all the tests in test suite $T$.
+% $\covfunc{P}{t}$ is a function that instruments program $P$, executes
+% test case $t$ on $P$, and returns the set of all statements in $P$
+% covered by $t$. $\covfunc{P}{T}$ returns the cumulative coverage
+% achieved on $P$ by all the tests in test suite $T$.
 
@@
 modified (to $t'$) and, if so, whether the behaviors of $t$ and $t'$
-differ. (We have not considered the cases in which $t$ is not modified
-because they are irrelevant for studying test evolution.)  For
-\textit{behavioral differences}, there are two cases, shown in the two
-rows of the table: either $t$ fails on $P'$ and $t'$ passes on $P'$ or
-both $t$ and $t'$ pass on $P'$.
+differ. For \textit{behavioral differences} there are two cases, shown
+in the two rows of the table: either $t$ fails on $P'$ and $t'$ passes
+on $P'$ or both $t$ and $t'$ pass on $P'$.
 
@@
 \end{tabular}
-\caption{Scenarios considered in our investigation. Given two system
-  versions $S = (P, T)$ and $S' = (P', T')$, the three scenarios are:
-  (a) $t$ exists in $T$ and $T'$ and is modified, (b) $t$ exists in
-  $T$ but not in $T'$, (c) $t'$ exists in $T'$ but not in $T$.}
-\vspace*{-5pt}
+\caption{Scenarios considered in our approach, given two system
+  versions $S = (P, T)$ and $S' = (P', T')$: (a) $t$ exists in $T$ and
+  $T'$ and is modified, (b) $t$ exists in $T$ but not in $T'$, (c)
+  $t'$ exists in $T'$ but not in $T$.}
+\vspace*{-12pt}
 \label{fig:study-design}
@@
 
-\paragraph{Category \catrep{} (Repaired Tests)}
-\label{sec:category-rep}
-
-The \catrep{} category corresponds to the case where $t$ is repaired
-so that, after the modifications, it passes on $P'.$ As discussed in
-the Introduction, Figure~\ref{fig:pmd-javatokenizertest} shows an
-example of such a test repair.
+\textit{a) Category \catrep{} (Repaired Tests)} corresponds to cases
+where $t$ is repaired so that, after the modifications, it passes on
+$P'.$ (See Figure~\ref{fig:pmd-javatokenizertest} and discussion in
+Section~\ref{sec:intro}.)
 
@@
 
-\paragraph{Category \catref{} (Refactored Tests)}
-\label{sec:category-c2}
-
-The \catref{} category captures scenarios in which a test $t$ is
-modified in $S'$ even though $t$ passes on $P'$.
+\textit{b) Category \catref{} (Refactored Tests)} captures
+scenarios in which a test $t$ is modified in $S'$ even though $t$
+passes on $P'$.
 %% Listings~\ref{c2-old} and~\ref{c2-new} show an example of one such
@@
 
-\paragraph{Category \catdelaere{} (Hard-To-Fix Tests)}
-\label{sec:category-delaere}
-
-%%COMMENT PLEASE READ ME: I guess here we should focus more
-%%in the cases that tests are removed because they have become
-%%obsolete. Actually, in the examples I was not able to find one
-%%case in which it was removed because it was too difficult to
-%% be fixed. It was always obsolete tests.
-
-This category includes tests that fail on $P'$ with a runtime
-exception or an assertion violation. These may be instances where the
-tests should have been fixed, as the functionality that they test in
-$P$ still exists in $P'$, but the tests were discarded instead. One
-plausible hypothesis is that tests in this category involve repairs of
-undue complexity, for which the investigation of new repair techniques
-to aid the developer might be particularly useful.
+\textit{a) Category \catdelaere{} (Hard-To-Fix Tests)} includes tests
+that fail on $P'$ with a runtime exception or an assertion
+violation. These may be instances where the tests should have been
+fixed, as the functionality that they test in $P$ still exists in
+$P'$, but the tests were discarded instead. One plausible hypothesis
+is that tests in this category involve repairs of undue complexity,
+for which the investigation of new repair techniques to aid the
+developer might be particularly useful.
 %% We performed a preliminary investigation of this hypothesis by
@@
 
-\paragraph{Category \catdelce (Obsolete Tests)}
-\label{sec:category-delce}
-
-A test that fails with a compilation error on the new program version
-is obsolete because of API changes.
+\textit{b) Category \catdelce (Obsolete Tests)} includes tests that
+are obsolete because of API changes, and thus fail with a compilation
+error on the new program version.
 %
@@
 
-\paragraph{Category \catdelp: (Redundant Tests)}
-\label{sec:category-delp}
-
-This category includes tests that are removed even though they pass on
-$P'$. These tests would typically be redundant, by some measure of
-redundancy (\eg code-coverage based). In some cases, a test may be
-replaced with a different one.
-
-%% Listing~\ref{c5-example} illustrates an example of one such test,
-%% taken from \subject{Commons Lang}. In the new version, this test was
-%% replaced by a more sophisticated one, shown in
-%% Listing~\ref{c5.2-example}.
-
-%% \begin{figure}[h]
-%% \lstinputlisting[language=java,label=c5-example,caption=\small{Unit
-%%   test from class MatrixIndexExceptionTest} (Commons Lang
-%% v2.1),frame=tb] {code/TestDel-P.java}
-%% \vspace{4pt}
-%% \end{figure}
-
-%% \lstinputlisting[language=java,label=c5.2-example,caption=\small{Unit
-%%   test implemented to replace the removed one} (Commons Lang
-%% v2.2),frame=tb] {code/TestDel-PII.java}
+\textit{c) Category \catdelp (Redundant Tests)} includes tests that
+are removed even though they pass on $P'$. These tests would typically
+be redundant according to some criterion, such as code coverage.
 
@@
 
-\paragraph{Category \cataddaere: (Bug-Fix Tests)}
-\label{sec:category-addaere}
-
-This category includes added tests that fail on $P$ with a runtime
-exception or an assertion violation. In this case, the functionality
-that the added test $t'$ was designed to test exists in $P$ but is not
-working as expected (most likely because of a fault). The program
-modifications between $P$ and $P'$ would ostensibly have been made to
-fix the fault, which causes $t'$ to pass on $P'$. Thus, $t'$ is added
-to the test suite to validate the bug fix.
+\textit{a) Category \cataddaere (Bug-Fix Tests)} includes added tests
+that fail on $P$ with a runtime exception or an assertion
+violation. In this case, the functionality that the added test $t'$
+was designed to test exists in $P$ but is not working as expected
+(most likely because of a fault). The program modifications between
+$P$ and $P'$ would ostensibly have been made to fix the fault, which
+causes $t'$ to pass on $P'$. Thus, $t'$ is added to the test suite to
+validate the bug fix.
 
@@
 
-\paragraph{Category \cataddce (New-Features Tests)}
-\label{sec:category-addce}
+\textit{b) Category \cataddce (New-Features Tests)} includes tests
+that fail on $P$ with a compilation error, which indicates that the
+API accessed by the tests does not exist in $P$. Thus, the added test
+$t'$ is created to test new code in $P'$.
 
-The added tests in this category fail on $P$ with a compilation error,
-which indicates that the API accessed by the tests does not exist in
-$P$. Thus, the added test $t'$ is created to test new code in $P'$,
-where the code could have been added as part of a refactoring or, more
-likely, to add new functionality.
-
-%% Listing~\ref{c7-example} illustrates a test from \subject{JFreeChart}
-%% that covers a new functionality: method \lang{getMinY()} did not exist
-%% in previous versions of class \lang{TimeSeries}.
-
-%% \lstinputlisting[language=java,label=c7-example,caption=\small{Unit
-%%   test from class TimeSeriesTests} (JFreeChart v1.0.14),
-%% captionpos=t,frame=tb]{code/TestAdd-Ce.java}
-
-\paragraph{Category \cataddp (Coverage-Augmentation Tests)}
-\label{sec:category-addp}
-
-This category considers cases where the added test $t'$ passes on
-$P$. Clearly, $t'$ would have been a valid test in the old system as
-well. One would expect that the addition of $t'$ increases program
-coverage (\ie $\covfunc{P'}{T'} \supset \covfunc{P'}{T' -
-  \{t'\}}$). Moreover, if $t'$ covers different statements in $P$ and
-$P'$ (assuming that there is a way of matching statements between $P$
-and $P'$), the plausible explanation is that $t'$ was added to test
-the changes made between $P$ and $P'$. However, if $t'$ covers the
-same statements in both program versions, it would have been added
-purely to increase code coverage (and not to test any added or
-modified code).
-
-%% Listing~\ref{c8-example} illustrates an added test case that increases
-%% code coverage: the new test method \lang{testFindRangeBounds} covers
-%% the case where the parameter of method \lang{findRangeBounds()} is
-%% null.
-
-%% \lstinputlisting[language=java,label=c8-example,caption=\small{Unit test
-%% from class XYErrorRendererTests} (JFreeChart v1.0.14),frame=tb]
-%% {code/TestAdd-P.java}
+\textit{c) Category \cataddp (Coverage-Augmentation Tests)} considers
+cases where the added test $t'$ passes on $P$. Clearly, $t'$ would
+have been a valid test in the old system as well. One would expect
+that the addition of $t'$ increases program coverage. Moreover, if
+$t'$ covers different statements in $P$ and $P'$, the plausible
+explanation is that $t'$ was added to test the changes made between
+$P$ and $P'$. However, if $t'$ covers the same statements in both
+program versions, it would have been added purely to increase code
+coverage, and not to test any added or modified code.
 
@@
 
-In our demonstration, we show an implementation of our technique,
-\tool, that works on Java programs and JUnit test suites ({\small
+\tool works on Java programs and JUnit test suites ({\small
   \url{http://www.junit.org/}}). We chose Java and JUnit because the
@@
 Apache Tomcat ({\small \url{http://tomcat.apache.org/}}). Although the
-tool can be installed locally, users who want to get familiar with
-\tool\ without having to install it can also access it remotely at
-{\small \url{http://cheetah.cc.gt.atl.ga.us:8081/testevol/}},
-specifying user ``icse'' and password ``icse2013''.
+tool can be installed locally, users can also run it without any
+install by accessing it remotely at {\small
+  \url{http://cheetah.cc.gt.atl.ga.us:8081/testevol/}} and specifying
+user ``icse'' and password ``icse2013'' (or requesting an account).
 
@@
 project \subject{google-gson}. The report shows the number of tests,
-both total and per version, that fall in each of the eight categories
-defined in our approach.  By clicking on a pair of versions, the user
-can obtain detailed report for a specific pair of versions. To
-illustrate, Figure~\ref{fig:versiondetails} shows the detailed report
-for versions $v.1.1$--$v.1.2$ and a specific category of differences
-(\catrep). By further clicking on a test case in the list, users can
-also inspect, in the case of modified tests, the actual differences
-between the two versions of that test, as shown in
-Figure~\ref{fig:summary} for test case \subject{TypeInfoTest}.
+both total and per version, that fall in each of the test-evolution
+categories considered in our approach.  By clicking on a pair of
+versions, the user can obtain a detailed report for a specific pair of
+versions.  To illustrate, Figure~\ref{fig:versiondetails} shows the
+detailed report for versions $v.1.1$--$v.1.2$ and for a specific
+category of differences (\catrep). By further clicking on a test case
+in the list, users can also inspect, if it is a modified test, the
+actual differences between the two versions of that test, as shown in
+Figure~\ref{fig:testdetails} for test case \subject{TypeInfoTest}.
 
@@
 of the eight test-evolution categories presented in
-Section~\ref{sec:test-evolution}. For each pair consisting of a broken
-test case and its repaired version, the test classifier also compares
-the test cases to identify the types of repair changes---different
-types of method-sequence changes and assertion changes---as discussed
-in Section~\ref{sec:category-rep}; this analysis is also implemented
-using \textsc{wala}.
+Section~\ref{sec:test-evolution}.  For each pair consisting of a
+broken test case and its repaired version, the test classifier also
+compares the test cases to identify the types of repair changes (\eg
+different types of method-sequence changes and assertion changes), as
+discussed in Section~\ref{sec:test-mod}. This analysis is also
+implemented using \textsc{wala}.
 
@@
 the deleted or added tests cause any variations in the coverage
-attained by the new test suite.
+achieved by the new test suite.
 
@@
 
-Test suites evolve throughout their lifetime and change with the
-applications under test. Adapting existing test cases manually,
+Test suites evolve throughout their lifetime and change together with
+the applications under test. Adapting existing test cases manually,
 however, can be extremely tedious, especially for large test suites,
 which has motivated the recent development of automated test-repair
-techniques (\eg \cite{Daniel:2009, Daniel:2010, Mirzaaghaei:2012}).
-To support the development of more effective repair techniques, we
-developed \tool, a tool for systematic investigation of test-suite
-evolution that can provide its users with a comprehensive
-understanding of how test cases evolve. In this demonstration, we
-present \tool, its main features, and its technical characteristics.
-We also demonstrate how \tool\ can be run on real-world software
-systems and produce a wealth of useful information, such as the types
-of test-suite changes that occur, the frequency of the changes, and
-why tests are deleted and added.  Overall, we show how \tool\ is a
-useful tool not only for researchers working in the area of test
-repair, and test evolution in general, but also for developers and
-testers who wish to understand their software systems better.
+techniques. To support the development of more effective repair
+techniques, and to help developers and testers better understand test
+maintenance in general, we developed \tool. \tool is a tool for
+systematic investigation of test-suite evolution that can provide its
+users with a comprehensive understanding of how test cases evolve
+throughout the lifetime of a software system. This demonstration
+presents \tool, its main features, and its technical characteristics.
+It also shows how \tool\ can be run on real-world software systems and
+produce a wealth of useful information on how test-suite changes.
+
+Complete information on \tool\ can be found on the tool's web page, at
+{\small \url{http://www.cc.gatech.edu/~orso/software/testevol/}}.
 
@@
 {\footnotesize
-\bibliography{paper}
+% \bibliography{paper}
+\begin{thebibliography}{1}
+
+\bibitem{Choudhary:2011}
+S.~R. Choudhary, D.~Zhao, H.~Versee, and A.~Orso.
+\newblock {WATER: Web Application TEst Repair}.
+\newblock In {\em Proceedings of the First International Workshop on End-to-End
+  Test Script Engineering}, pages 24--29, 2011.
+
+\bibitem{Daniel:2010}
+B.~Daniel, T.~Gvero, and D.~Marinov.
+\newblock On test repair using symbolic execution.
+\newblock In {\em Proceedings of the 19th International Symposium on Software
+  Testing and Analysis}, pages 207--218, 2010.
+
+\bibitem{Daniel:2009}
+B.~Daniel, V.~Jagannath, D.~Dig, and D.~Marinov.
+\newblock {ReAssert: Suggesting repairs for broken unit tests}.
+\newblock In {\em Proceedings of the International Conference on Automated
+  Software Engineering}, pages 433--444, 2009.
+
+\bibitem{Grechanik:2009}
+M.~Grechanik, Q.~Xie, and C.~Fu.
+\newblock Maintaining and evolving gui-directed test scripts.
+\newblock In {\em Proceedings of the 31st International Conference on Software
+  Engineering}, pages 408--418, 2009.
+
+\bibitem{Huang:2010}
+S.~Huang, M.~B. Cohen, and A.~M. Memon.
+\newblock Repairing {GUI} test suites using a genetic algorithm.
+\newblock In {\em Proceedings of the 3rd International Conference on Software
+  Testing, Verification and Validation}, pages 245--254, 2010.
+
+\bibitem{Memon:2008}
+A.~M. Memon.
+\newblock {Automatically repairing event sequence-based GUI test suites for
+  regression testing}.
+\newblock {\em ACM Trans. Softw. Eng. Methodol.}, 18:1--36, November 2008.
+
+\bibitem{Mirzaaghaei:2012}
+M.~Mirzaaghaei, F.~Pastore, and M.~Pezz{\'e}.
+\newblock Supporting test suite evolution through test case adaptation.
+\newblock In {\em Proceedings of the 5th IEEE International Conference on
+  Software Testing, Verification and Validation}, pages 231--240, 2012.
+
+\bibitem{pinto12}
+L.~S. Pinto, S.~Sinha, and A.~Orso.
+\newblock Understanding myths and realities of test-suite evolution.
+\newblock In {\em Proceedings of the 20th ACM SIGSOFT International Symposium
+  on the Foundations of Software Engineering (FSE 2012), to appear}.
+
+\end{thebibliography}
+
 }
